### 2024-08-13 manuscript.Rmd
post-meeting

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
bibliography: references.bib
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Introduction

[@dplyr]

[@rosseel2012]

# Methods

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis

We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

### 2024-08-13 manuscript.tex
post-meeting

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

\makeatletter
\usepackage{etoolbox}
\patchcmd{\maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={The title},
  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{The title}
\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
\date{}

\shorttitle{Title}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing, Supervision.

Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}

\abstract{%
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
One or two sentences to put the results into a more \textbf{general context}.
Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

Introduction

(Wickham, François, Henry, Müller, \& Vaughan, 2023)

(Rosseel, 2012)

\section{Methods}\label{methods}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.

\subsection{Participants}\label{participants}

\subsection{Material}\label{material}

\subsection{Procedure}\label{procedure}

\subsection{Data analysis}\label{data-analysis}

We used R (Version 4.4.1; \textbf{R-base?}) and the R-packages \emph{papaja} (Version 0.1.2; \textbf{R-papaja?}), and \emph{tinylabels} (Version 0.2.4; \textbf{R-tinylabels?}) for all our analyses.

\section{Results}\label{results}

\section{Discussion}\label{discussion}

\newpage

\section{References}\label{references}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-rosseel2012}
Rosseel, Y. (2012). Lavaan: An r package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(1), 1--36. \url{https://doi.org/10.18637/jss.v048.i02}

\bibitem[\citeproctext]{ref-dplyr}
Wickham, H., François, R., Henry, L., Müller, K., \& Vaughan, D. (2023). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}

\end{CSLReferences}

\end{document}

### 2024-08-23 manuscript.Rmd
working on intro - kind of a mess lol

@@
 
-[@dplyr]
+Example citation: [@dplyr]
 
 [@rosseel2012]
+
+Preliminary Outline
+
+Intro - awareness of death, especially in light of COVID.
+
+Various existential philosophers and psychologists have proposed ways in which we deal with the awareness of death and the anxiety this awareness often causes.
+Psychoanalyst Erik Erikson proposed that during mid-life one becomes acutely aware of their oncoming death and is motivated to care for things which will outlast themselves.
+He called this act of caring generativity (CITATION).
+In *The Denial of Death* (1973), philosopher Ernest Becker posits that humans undertake immortality projects to curb their sense of vulnerability to death.
+Similarly, psychiatrist Robert Jay Lifton (1979), a mentee of Erikson, described the awareness of death as being ever present and motivating us to create symbols thereby allowing ourselves to imagine us as symbolically immortalized.
+Existential psychiatrist, Irvin Yalom notes that many of his clients experiencing anxiety about their death take comfort in “rippling”, the idea that one’s lasting effects on the world will ripple out and influence the world after they have died (CITATION).
+
+Although these thinkers use different terminology, there are several common themes among their ideas.
+(1) Our physical death is an inevitability, and we often find our awareness of its inevitability to be aversive: that is, it can cause angst, death-anxiety, despair, being-towards-death, terror, and so on.
+However, (2) we take comfort in the idea that other, non-physical parts of us continue to exist indefinitely after our biological death, through mechanisms such as the heroic archetype and symbolic self.
+(3) Finally, we can take action to promote these non-physical aspects of the self, such as through search for meaning, immortality project, care, generativity, rippling.
+
+Sense of immortality.
+Originally theorized by Lifton 1979.
+Awareness of death drives a fundamental human need to "develop a sense of continuity and lastingness" beyond the lifespan.
+Some denial of death is thought to be universal, according to Lifton.
+But acceptance of the reality of death can drive "personal and collective creativity" (aka generativity?).
+Humans as meaning-seeking creatures.
+(The above was taken from Drolet 1990).
+
+Lifton's five modes of symbolic immortality: (1) biological or biosocial mode (ancestors and progeny, but can be extended to one's culture, values, and social identity), (2) creative mode (one's work or social contribution, influence), (3) natural mode (being a part of the broader world transcending oneself), (4) spiritual mode (spiritual attainment, possibly a literal sense of an afterlife but not always, search for ultimate meaning), (5) mode of experiential transcendence (ability to lose oneself in what might be called a "flow" experience).
+The fifth mode must occur in the context of one of the other four to really be considered transcendent, but it has a great capacity to bring about personal change.
+
+Erikson's theory and generativity.
+
+Current measures of generativity are more about domains of generativity, actions, trait. Loyola Generativity Scale
+
+Lacking measure of the underlying motivation, thought to be related to a motive to expand the sense of self beyond the lifetime (Kotre 1984).
+This is related to sense of symbolic immortality.
+McAdams and de St.
+Aubin (1992) found symbolic immortality to be one of five themes across content analysis of autobiographical episodes.
+
+Terror Management Theory and generativity/symbolic immortality.
+Claims of how we suppress death-anxiety have been investigated experimentally, primarily through the paradigm of Terror Management Theory (TMT).
+Based on the theories of Ernest Becker, TMT posits that human awareness of death is always present to some degree.
+This awareness of our inevitable death, coupled with a strong aversion to thoughts of death, causes terror and is pushed out of our consciousness by our creation of meaning systems (CITATION).
+TMT refers to a person's awareness of death as mortality salience (MS).
+The MS hypothesis of TMT posits than an increase in one's awareness of death causes an increase in compensatory behaviors to lower their death anxiety, either by distracting from the awareness of death or by the promotion of meaningful cultural worldviews.
+A meta-analysis of 277 experiments has found mortality salience to have moderate effects (*r* = 0.35; Burke, Martens & Faucher, 2010).
+TMT literature has found three consistent buffers of our awareness of death: self-esteem, interpersonal relationships, and cultural worldview (CITATION, unless it's the same as above, in which case make that clear).
+
+TMT research is conducted in two paradigms.
+In the MS paradigm, a participant’s increased awareness of death causes an increase in compensatory buffers.
+In the death-thought accessibility paradigm, experimentally decreasing participants’ buffers, such as lowering self-esteem or challenging their worldview beliefs, causes (CHECK THIS AND CITE ACTUAL STUDIES) an increase in their awareness of death.
+Together, these experiments provide convincing evidence of these of suppressing awareness of death and death anxiety.
+It is assumed that such changes in attitude and behavior suppress thoughts of death by giving a sense of existential immortality; however, to our knowledge no researchers have attempted to assess subjective feelings of immortality.
+This missing literature may in part be because of a lack of a viable measure of existential immortality.
+We view this dearth as a large gap in the literature and methodology.
+
+Sense of psychological death?
+
+Somewhat loss of religiosity in the West that may have been a way of coping/finding a sense of immortality in the past. A sense of collective/social immortality may be a way to address this?
+
+Two attempts have been made to develop such a measurement.
+Drolet (1990) developed the Sense of Symbolic Immortality Scale.
+This scale was based on Robert J.
+Lifton’s theory of symbolic immortality in which a sense of symbolic immortality can be achieved through five different modes: the biological mode in which one lives on through their genetic progeny, the creative mode in which one’s accomplishments outlast oneself, the natural mode in which one feels they are a part of the universe, the spiritual mode in which one transcends the biological and physical realm to a higher spiritual realm to transcend death, and the mode of experiential transcendence in which one experiences a phenomenological state of flow.
+The Sense of Symbolic Immortality Scale contains five subscales corresponding to each proposed mode.
+
+[Is Matthews and Kling a thing???]
+
+Drolet studied 136 adults, 18-30 and 30-40 year olds, and hypothesized that those in their 30's (established adults) would have a greater sense of symbolic immortality than the young adults (18-30).
+The measure is inherently subjective, not only by the nature of self-report, but in that what we are interested in is what a person *believes* and how they *feel* about these subjects.
+The scale as a whole had a high internal consistency (alpha = .91) and test-retest reliability was r = .97.
+Internal consistency of subscales for the five theoretical modes of immortality was mixed.
+Of the five, spiritual immortality was the most distinct from the scale as a whole and the other subscales.
+(Note that this seems relevant to what we found in our own scale development.
+For more in the Discussion later on.) Factor analysis showed three factors, mapping onto biosocial, creative, and spiritual.
+The transcendent and natural items may be related to biosocial.
+
+Moving beyond the scale development itself (still Drolet 1990), SSI correlated negatively with death anxiety (Templer's Death Anxiety Scale) and had a strong (r = .84) positive relationship with purpose in life (Maholick's Purpose in Life Test).
+In interpreting the very strong correlation, the author suggests that SSI is a broader construct than Purpose in Life and the scale itself may be less prone to social desirability effects than the PIL, although this had not been directly tested.
+Age group was also related, with established adults having a higher SSI, particularly in the biosocial and creative domains.
+
+We see multiple issues with using the Symbolic Immortality Scale.
+First, the study was underpowered, conducting exploratory factor analysis of 67 items using a sample of 136.
+Second, the scale was developed in French, and we do not take for granted the psychometric properties of a translated version.
+Third and most fundamentally, the scale has poor face validity and appears to measure the constructs theorized to symbolically immortalize rather than a sense of symbolic immortality directly.
+For example, the scale includes items such as “My sex life contributes greatly to my well-being”, “Intimate relationships scare me”, and “I am sure of who I am." Although related to the constructs (such as interpersonal relationships and self-esteem) which theoretically help cope with death, it is unclear how these items represent the construct of symbolic immortality itself.
+
+Mathews and Mister (1988) also developed a scale involving symbolic immortality, sensation seeking, and psychic numbness.
+Study of 400 adults.
+Experiential transcendence was operationalized as something like Zuckerman's (1979) sensation seeking, which may not fully capture the original intent (the experience of losing oneself).
+Items were forced into five factors, and the five factors largely aligned with Lifton's constructs.
+Although internal consistency was at least acceptable for each factor, goodness of fit statistics are not reported.
+The items themselves seem to have more face validity than the scale by Drolet, but some factors seem more behavioral and specific: pertaining to one's religiosity or biological children.
+The Nature and Creative factors seems most useful and theoretically aligned with Lifton.
+
+The goal of the present research is to develop a scale that more directly measures one’s sense of existential immortality using a larger sample and current best practices for scale development.
 

### 2024-08-27 05_Manuscript/manuscript.Rmd
updating structure and data

--- 2024-08-23 manuscript.Rmd
@@
 
-# Methods
-
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+# Method
 
@@
 
-We used `r cite_r("r-references.bib")` for all our analyses.
+# Results
 
-# Results
+```{r libraries}
+library(rio)
+library(dplyr)
+set.seed(8943)
+```
+
+```{r load-data}
+sona <- import("../03_Data/sona_data.csv")
+mturk <- import("../03_Data/mturk_data.csv")
+```
 

### 2024-08-27 05_Manuscript/manuscript.tex
updating structure and data

--- 2024-08-13 manuscript.tex
@@
 
-Introduction
+\#Introduction
 
-(Wickham, François, Henry, Müller, \& Vaughan, 2023)
+Example citation: (Wickham, François, Henry, Müller, \& Vaughan, 2023)
 
 (Rosseel, 2012)
+
+Preliminary Outline
+
+Erikson's theory and generativity.
+
+Current measures of generativity are more about domains of generativity, actions, trait. Loyola Generativity Scale
+
+Lacking measure of the underlying motivation, thought to be related to a motive to expand the sense of self beyond the lifetime (Kotre 1984).
+This is related to sense of symbolic immortality (Lifton 1979).
+
+Terror Management Theory and generativity.
+
+Only current scale to measure sense of immortality is Drolet's (1990) Sense of Symbolic Immortality scale. This has not been tested in translation.
 

### 2024-08-27 manuscript.Rmd
intro stuff

@@
 
-Preliminary Outline
-
 Intro - awareness of death, especially in light of COVID.
@@
 Various existential philosophers and psychologists have proposed ways in which we deal with the awareness of death and the anxiety this awareness often causes.
-Psychoanalyst Erik Erikson proposed that during mid-life one becomes acutely aware of their oncoming death and is motivated to care for things which will outlast themselves.
-He called this act of caring generativity (CITATION).
+Psychoanalyst Erik Erikson (1950) proposed that during mid-life one becomes acutely aware of their oncoming death and is motivated to care for things which will outlast themselves.
+He called this act of caring generativity.
 In *The Denial of Death* (1973), philosopher Ernest Becker posits that humans undertake immortality projects to curb their sense of vulnerability to death.
 Similarly, psychiatrist Robert Jay Lifton (1979), a mentee of Erikson, described the awareness of death as being ever present and motivating us to create symbols thereby allowing ourselves to imagine us as symbolically immortalized.
-Existential psychiatrist, Irvin Yalom notes that many of his clients experiencing anxiety about their death take comfort in “rippling”, the idea that one’s lasting effects on the world will ripple out and influence the world after they have died (CITATION).
+Existential psychiatrist, Irvin Yalom (2008) notes that many of his clients experiencing anxiety about their death take comfort in “rippling”, the idea that one’s lasting effects on the world will ripple out and influence the world after they have died.
 
@@
 
-Sense of immortality.
-Originally theorized by Lifton 1979.
-Awareness of death drives a fundamental human need to "develop a sense of continuity and lastingness" beyond the lifespan.
-Some denial of death is thought to be universal, according to Lifton.
-But acceptance of the reality of death can drive "personal and collective creativity" (aka generativity?).
+Sense of symbolic immortality was originally theorized by Lifton (1979), who thought that awareness of death drives a fundamental human need to "develop a sense of continuity and lastingness" beyond the lifespan (quote from Drolet 1990).
 Humans as meaning-seeking creatures.
-(The above was taken from Drolet 1990).
 
-Lifton's five modes of symbolic immortality: (1) biological or biosocial mode (ancestors and progeny, but can be extended to one's culture, values, and social identity), (2) creative mode (one's work or social contribution, influence), (3) natural mode (being a part of the broader world transcending oneself), (4) spiritual mode (spiritual attainment, possibly a literal sense of an afterlife but not always, search for ultimate meaning), (5) mode of experiential transcendence (ability to lose oneself in what might be called a "flow" experience).
-The fifth mode must occur in the context of one of the other four to really be considered transcendent, but it has a great capacity to bring about personal change.
+Lifton (1979) proposed five modes of experience or ways of achieving symbolic immortality: The biological (or biosocial) mode in which one lives on through their genetic and socio-cultural progeny, the creative mode in which one’s accomplishments and contribution outlast oneself, the natural mode in which one feels they are a part of the broader universe, the spiritual mode in which one seeks to transcend the physical realm to a higher spiritual realm beyond death, and the mode of experiential transcendence in which one experiences a phenomenological state of flow.
+The latter (experiential transcendence) must occur in the context of one of the other four to really be considered transcendent, but it is thought to have a great capacity to bring about personal change.
 
+Sense of psychological death?
+
+Though some denial of death is thought to be universal, acceptance of the reality of death can drive what Drolet (1990) refers to as personal and collective creativity, or what Erikson referred to as generativity.
 Erikson's theory and generativity.
 
-Current measures of generativity are more about domains of generativity, actions, trait. Loyola Generativity Scale
+Current measures of generativity are more about domains of generativity, actions, trait rather than underlying motives.
+Loyola Generativity Scale and the authors' understanding of the dimensions of generativity.
+Underlying motivation of generativity thought to be related to a motive to expand the sense of self beyond the lifetime (Kotre 1984), especially in light of the fear of death.
+McAdams and de St.
+Aubin (1992) indeed found symbolic immortality to be one of five themes across content analysis of autobiographical episodes.
 
-Lacking measure of the underlying motivation, thought to be related to a motive to expand the sense of self beyond the lifetime (Kotre 1984).
-This is related to sense of symbolic immortality.
-McAdams and de St.
-Aubin (1992) found symbolic immortality to be one of five themes across content analysis of autobiographical episodes.
+Somewhat loss of religiosity in the West that may have been a way of coping/finding a sense of immortality in the past.
+Likely this may have fallen under the umbrella of the spiritual mode of immortality, and for many a literal belief in life after death.
+Perhaps many now would benefit more from a sense of collective, social, or creative immortality.
+(some citations here if I keep this paragraph)
 
-Terror Management Theory and generativity/symbolic immortality.
 Claims of how we suppress death-anxiety have been investigated experimentally, primarily through the paradigm of Terror Management Theory (TMT).
@@
 Together, these experiments provide convincing evidence of these of suppressing awareness of death and death anxiety.
+
 It is assumed that such changes in attitude and behavior suppress thoughts of death by giving a sense of existential immortality; however, to our knowledge no researchers have attempted to assess subjective feelings of immortality.
@@
 We view this dearth as a large gap in the literature and methodology.
+Two attempts have been made to develop such a measurement: Drolet's (1990) Sense of Symbolic Immortality Scale and Mathews and Kling (1988) measure of symbolic immortality, based on an original questionnaire by Mathews and Mister (1987).
 
-Sense of psychological death?
+NOTE\*\*\* can't get access to the Mathews and Kling article but it seems mostly related to prosocial behavior for nonprofit stuff - should we just focus on the original Mathews and Mister article?
+Some other articles I found use the Mathews and Kling version though.
+<https://journals.sagepub.com/doi/abs/10.1177/089976408801700202?download=true&journalCode=nvsa>
 
-Somewhat loss of religiosity in the West that may have been a way of coping/finding a sense of immortality in the past. A sense of collective/social immortality may be a way to address this?
-
-Two attempts have been made to develop such a measurement.
-Drolet (1990) developed the Sense of Symbolic Immortality Scale.
-This scale was based on Robert J.
-Lifton’s theory of symbolic immortality in which a sense of symbolic immortality can be achieved through five different modes: the biological mode in which one lives on through their genetic progeny, the creative mode in which one’s accomplishments outlast oneself, the natural mode in which one feels they are a part of the universe, the spiritual mode in which one transcends the biological and physical realm to a higher spiritual realm to transcend death, and the mode of experiential transcendence in which one experiences a phenomenological state of flow.
-The Sense of Symbolic Immortality Scale contains five subscales corresponding to each proposed mode.
-
-[Is Matthews and Kling a thing???]
-
-Drolet studied 136 adults, 18-30 and 30-40 year olds, and hypothesized that those in their 30's (established adults) would have a greater sense of symbolic immortality than the young adults (18-30).
-The measure is inherently subjective, not only by the nature of self-report, but in that what we are interested in is what a person *believes* and how they *feel* about these subjects.
+Drolet (1990) developed the Sense of Symbolic Immortality Scale based on Robert J.
+Lifton’s theory of symbolic immortality and its five modes of experience.
+Drolet studied 136 adults, ages 18-30 and 30-40, and hypothesized that those in their 30's (established adults) would have a greater sense of symbolic immortality than the young adults (18-30).
+The measure is inherently subjective, not only by the nature of self-report, but in that the scale seeks to measure what a person *believes* and how they *feel* about these subjects.
 The scale as a whole had a high internal consistency (alpha = .91) and test-retest reliability was r = .97.
@@
 
-Mathews and Mister (1988) also developed a scale involving symbolic immortality, sensation seeking, and psychic numbness.
-Study of 400 adults.
+Mathews and Mister (1987) also developed a scale involving symbolic immortality, sensation seeking, and psychic numbness.
+Some studies have used a revised version of the scale by Mathews and Kling (1988), who adapted it for a study on prosocial behavior in the context of nonprofit volunteer motivation.
+Mathews and Mister's study included 400 adults.
 Experiential transcendence was operationalized as something like Zuckerman's (1979) sensation seeking, which may not fully capture the original intent (the experience of losing oneself).
@@
 Although internal consistency was at least acceptable for each factor, goodness of fit statistics are not reported.
-The items themselves seem to have more face validity than the scale by Drolet, but some factors seem more behavioral and specific: pertaining to one's religiosity or biological children.
+The items themselves seem to have more face validity than the scale by Drolet, but some factors seem more behavioral and specific: pertaining to one's religiosity or biological children, whereas Lifton's theory allows for a broader interpretation of these dimensions.
 The Nature and Creative factors seems most useful and theoretically aligned with Lifton.
 
-The goal of the present research is to develop a scale that more directly measures one’s sense of existential immortality using a larger sample and current best practices for scale development.
+The goal of the present research is to develop a scale that more directly measures one’s sense of existential immortality in a way more generally applicable regardless of a person's religious beliefs and parental status.
+We have attempted to use current best practices for scale development.
 

### 2024-08-27 05_Manuscript/manuscript.Rmd
here's stuff

@@
 set.seed(8943)
+library(mice)
+
+## args: dat: Dataframe of scale values, with each row being a participant and each column being a scale question
+## args: rt: vector of response time/page time for each participant
+## args: min: minimum value of scale
+## args: max: maximum value of scale
+## args: partno: vector of corresponding participant numbers
+## args: clicks: click count column, outputted by qualtrics
+## args: manvec: vector of manipulation check question responses
+## args: mancor: correct answer of manipulation check
+## args: char: number of characters on the page
+
+SAD <- function(dat, #data frame of only scale values
+               rt = NULL, #column name for page timing
+               min = 1, #lower end of scale points
+               max = 7, #upper end of scale points
+               partno, #participant number so you can merge and identify outliers
+               click = NULL, #column of click counts
+               manvec = NULL, #column of manipulation check
+               mancor = NULL, #answer to the manipulation check
+               char = NULL){ #number of characters on the page
+
+  ##make sure the data provided is a data frame
+  dat = as.data.frame(dat)
+
+  ####number of scale options used####
+  OptUse = function(x){
+    length(table(as.vector(as.matrix(unname(x)))))
+  }
+  numOpt = apply(dat,1,OptUse)
+  numOpt = as.numeric(numOpt)
+  nsim = length(numOpt)
+  badScaleCheck = rep(NA, length(numOpt))
+  for(i in 1:nsim){
+    ##more than half of the options
+    optionhalf = length(min:max)/2+1
+    if(numOpt[i] >= optionhalf){
+      badScaleCheck[i] = 1
+    } else { badScaleCheck[i] = 0 }
+  }
+  badScaleCheck = as.numeric(badScaleCheck)
+
+  ####response/page time####
+  if (!is.null(rt)){
+    rt = as.numeric(unlist(rt))
+
+    ourchar = char
+    meanchar = 987
+    sdchar = 118
+    upperchar = meanchar + 2*sdchar
+    cutoffChar = ourchar / upperchar * 60
+    badChar = rep(NA, length(rt))
+    nsim = length(badChar)
+    for(i in 1:nsim){
+      if(!is.na(rt[i])){
+        if(rt[i] < cutoffChar){
+          badChar[i] = 1
+        } else{
+          badChar[i] = 0
+        }
+      } else { badChar[i] = NA}
+    }
+    badChar = as.numeric(badChar)
+  } else { badChar = rep(NA, nrow(dat))}
+
+  ####click count check####
+  if(!is.null(click)){
+    click = as.numeric(unlist(click))
+    totalexp = apply(dat,1, function(x){sum(!is.na(x))})
+    nsim = length(click)
+    badClick = rep(NA, length(click))
+    for(i in 1:nsim){
+      if(!is.na(click[i])){
+        if(click[i] >= totalexp[i]){
+          badClick[i] = 0
+        } else{
+          badClick[i] = 1
+        }
+      } else{ badClick[i] = NA}
+    }
+    badClick = as.numeric(badClick)
+  } else { badClick = rep(NA, nrow(dat))}
+
+  ####manipulation check question manip####
+  if(!is.null(manvec)){
+    manvec = as.numeric(unlist(manvec))
+    nsim = length(manvec)
+    badMC = rep(NA, nrow(dat))
+    for(i in 1:nsim){
+      if(!is.na(manvec[i])){ 
+        if(manvec[i] == mancor) { badMC[i] = 0 } else { badMC[i] = 1}} else { badMC[i] = 1}
+    }
+    badMC = as.numeric(badMC)
+  } else { badMC = rep(NA, nrow(dat))}
+
+  ####Distribution Testing####
+  uniform = rep(NA,nrow(dat))
+  normal = rep(NA, nrow(dat))
+  dist = rep(NA, nrow(dat))
+  nsim = nrow(dat)
+  for(i in 1:nsim){
+    temprow = as.numeric(unname(dat[i,])) 
+    utable = matrix(0, nrow = 1, ncol = length(min:max))
+    for(x in min:max) {
+      utable[x] = length(temprow[ temprow == x])
+    }
+    uniformest = chisq.test(utable,
+                            rescale.p = T,
+                            simulate.p.value = T)
+    ##test normal distribution
+    ##first convert to z score
+    ztest = scale(temprow)
+    ##then figure out how much of the data is binned for SDs
+    ztable = matrix(0, nrow = 1, ncol = 6)
+    ztable[1] = length(ztest[ ztest <= -2 ])  
+    ztable[2] = length(ztest[ ztest > -2 & ztest <= -1  ])
+    ztable[3] = length(ztest[ ztest > -1 & ztest <= 0 ])
+    ztable[4] = length(ztest[ ztest > 0 & ztest <= 1 ])
+    ztable[5] = length(ztest[ ztest > 1 & ztest <= 2 ])
+    ztable[6] = length(ztest[ ztest > 2 ])
+    znormal = c(0.0228, 0.1359, 0.3413, 0.3413, 0.1359, 0.0228)
+    normalest = chisq.test(ztable,
+                           p = znormal*sum(ztable),
+                           rescale.p = T,
+                           simulate.p.value = T)
+    ##output return chi square values
+    uniform[i] = uniformest$statistic
+    normal[i] = normalest$statistic
+    ##if uniform < normal
+    if(uniformest$statistic < normalest$statistic)
+    {
+      ##if more than 1 option
+      if (numOpt[i]>1)
+      {
+        dist[i] = 0 ##uniform is better
+      } else { ##handles when people only pick one thing
+        dist[i] = 2
+      }
+    }
+    ##if uniform >= normal
+    if(uniformest$statistic >= normalest$statistic)
+    {
+      ##if more than 1 option
+      if (numOpt[i]>1)
+      {
+        dist[i] = 1 ##normal is better
+      } else { ##handles when people only pick one thing
+        dist[i] = 2
+      }
+
+    }
+    #0 means uniform fits better
+    #1 means normal fits better
+    #2 means only chose one scale option
+  }## end of for loop
+
+  ####distribution coding####
+  badDist = rep(NA, nsim)
+  for(i in 1:nsim){
+    if(dist[i] == 0){
+      badDist[i] = 1
+    } 
+    if (dist[i] == 1){
+      badDist[i] = 0
+    } 
+    if (dist[i] == 2) {
+      badDist[i] = 0
+    }
+  }
+  badDist = as.numeric(badDist)
+
+  ####total up####
+  badDF = cbind.data.frame(badChar, badClick, badDist, badScaleCheck, badMC)
+  badDF$badTotal = apply(badDF, 1, sum, na.rm = T)
+  badDF$participant = partno
+
+  return(badDF)
+
+} #end function
+
+percentmiss <- function(x){ sum(is.na(x))/length(x) *100 }
 ```
 
-```{r load-data}
-sona <- import("../03_Data/sona_data.csv")
-mturk <- import("../03_Data/mturk_data.csv")
+```{r load-data, eval = T}
+sona <- import("../03_Data/sona_data_deidentify.csv") %>% 
+  mutate(where = "sona")
+mturk <- import("../03_Data/mturk_data_deidentify.csv") %>% 
+  mutate(where = "mturk")
+```
+
+## Data Screening
+
+```{r screen-sona-accuracy-out, eval = F}
+# Accuracy ----
+summary(sona %>% 
+          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20))
+# everything is within the expected range
+
+apply(sona %>% 
+          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
+      2, mean, na.rm = TRUE)
+apply(sona %>% 
+          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
+      2, sd, na.rm = TRUE)
+# check reverse items? Q2_21?
+
+# Missing ----
+
+# rows
+missing <- apply(sona %>% 
+          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
+          1, 
+          percentmiss) 
+table(missing)
+replacepeople <- subset(sona, missing <= 5)
+dontpeople <- subset(sona, missing > 5)
+
+# columns
+missingcol <- apply(replacepeople %>% 
+                      select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
+                    2, 
+                    percentmiss)
+table(missingcol) # all replaceable
+
+replacecolumn <- replacepeople %>% 
+  select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20)
+dontcolumn <- replacepeople %>% 
+  select(-c(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20))
+
+# replacing those with <= 5% missing by multiple imputation
+tempnomiss <- mice(replacecolumn)
+nomiss <- complete(tempnomiss, 1)
+summary(nomiss)
+
+# putting data back together
+# excluding participants with > 5% missing (7 total)
+allcolumns <- cbind(dontcolumn, nomiss)
+summary(allcolumns)
+write.csv(allcolumns, "../03_Data/sona_data_replaced.csv", row.names = F)
+```
+
+```{r screen-sona-SAD}
+# SAD 
+nomissing <- import("../03_Data/sona_data_replaced.csv")
+
+# Block 1
+page1 <- SAD(dat = nomissing %>% 
+               select(Q2_1:Q2_21),
+    rt = nomissing$`Q10_Page Submit`,
+    min = 1, 
+    max = 5, 
+    partno = nomissing$ResponseId, 
+    click = nomissing$`Q10_Click Count`, 
+    manvec = nomissing$Q2_21, 
+    mancor = 1, 
+    char = 1626)
+write.csv(page1, "../03_Data/sona_page1_sad.csv", row.names = F)
+
+# Block 2
+page2 <- SAD(dat = nomissing %>% 
+               select(Q4_1:Q4_20), 
+            rt = nomissing$`Q11_Page Submit`,
+            min = 1, 
+            max = 5, 
+            partno = nomissing$ResponseId, 
+            click = nomissing$`Q11_Click Count`, 
+            manvec = nomissing$Q4_20, 
+            mancor = 4, 
+            char = 1491)
+write.csv(page2, "../03_Data/sona_page2_sad.csv", row.names = F)
+
+# Block 3
+page3 <- SAD(dat = nomissing %>% 
+               select(Q5_1:Q5_20), 
+            rt = nomissing$`Q12_Page Submit`,
+            min = 1, 
+            max = 5, 
+            partno = nomissing$ResponseId, 
+            click = nomissing$`Q12_Click Count`, 
+            manvec = nomissing$Q5_16, 
+            mancor = 3, 
+            char = 1496)
+write.csv(page3, "../03_Data/sona_page3_sad.csv", row.names = F)
+
+# Total
+nomissing$totalbad <- page1$badTotal + page2$badTotal + page3$badTotal
+
+nomissing$totalbadUP = 
+  page1$badChar + page1$badClick + page1$badMC + 
+  page2$badChar + page2$badClick + page2$badMC + 
+  page3$badChar + page3$badClick + page3$badMC
+table(nomissing$totalbadUP)
+nolowqual = subset(nomissing, totalbadUP < 4)
+##B&S say 2/5 which is 40%, so 40% of the 9 total is 3.6 or 4 or more
+
+# Outliers ----------------------------------------------------------------
+
+mahal = mahalanobis(nolowqual[ , 37:97], 
+                    colMeans(nolowqual[ , 37:97], na.rm = TRUE),
+                    cov(nolowqual[ , 37:97], use="pairwise.complete.obs"))
+
+cutoff = qchisq(1 - .001,ncol(nolowqual[ , 37:97]))
+ncol(nolowqual[ , 37:97]) #df 61
+cutoff #cutoff 100.8879
+
+summary(mahal < cutoff)
+mahal[mahal > cutoff]
+
+noout = subset(nolowqual, mahal < cutoff)
+#42 participants excluded as outliers
+
+# Assumptions -------------------------------------------------------------
+
+# Linearity #
+random = rchisq(nrow(noout[ , 37:97]), 7) 
+fake = lm(random~., data=noout[ , 37:97])
+
+standardized = rstudent(fake)
+{qqnorm(standardized)
+  abline(0,1)}
+#seems okay
+
+# Normality #
+hist(standardized, breaks=15)
+#a little skewed but mostly centered on 0 and between -2 and 2 so okay
+
+# Homog/s #
+fitvalues = scale(fake$fitted.values)
+{plot(fitvalues, standardized) 
+  abline(0,0)
+  abline(v = 0)}
+#some homogeneity issues but we'll accept it
+
+write.csv(noout, file = "sona_data_screened.csv", row.names = F)
+library(beepr)
+beep(sound = 5)
+
+# > nrow(master)
+# [1] 564
+# > nrow(nomissing)
+# [1] 557
+# > nrow(nolowqual)
+# [1] 507
+# > nrow(noout)
+# [1] 464
+
+sona_screen_1 <- SAD(
+  dat = sona %>% 
+    select(Q2_1:Q2_21, `Q10_Page Submit`, `Q10_Click Count`),
+  rt = "Q10_Page Submit",
+  min = 1,
+  max = 5, 
+  partno = "ResponseId",
+  clicks = "Q10_Click Count",
+
+)
+
+## args: dat: Dataframe of scale values, with each row being a participant and each column being a scale question
+## args: rt: vector of response time/page time for each participant
+## args: min: minimum value of scale
+## args: max: maximum value of scale
+## args: partno: vector of corresponding participant numbers
+## args: clicks: click count column, outputted by qualtrics
+## args: manvec: vector of manipulation check question responses
+## args: mancor: correct answer of manipulation check
+## args: char: number of characters on the page
 ```

### 2024-08-27 05_Manuscript/manuscript.Rmd
a bit of updates

@@
       2, sd, na.rm = TRUE)
-# check reverse items? Q2_21?
+#
 
@@
 
-```{r screen-sona-SAD}
+```{r screen-sona-SAD, eval = F}
 # SAD 
@@
 nomissing$totalbad <- page1$badTotal + page2$badTotal + page3$badTotal
+table(nomissing$totalbad) 
+sum(nomissing$totalbad < 15*.4) 
+nrow(nomissing)
 
-nomissing$totalbadUP = 
+nomissing$totalbadUP <- 
   page1$badChar + page1$badClick + page1$badMC + 
@@
 table(nomissing$totalbadUP)
-nolowqual = subset(nomissing, totalbadUP < 4)
-##B&S say 2/5 which is 40%, so 40% of the 9 total is 3.6 or 4 or more
+sum(nomissing$totalbadUP < 9*.4) 
+# B&S say 2/5 which is 40%, so 40% of the 9 total is 3.6 or 4 or more
+
+nolowqual <- subset(nomissing, totalbadUP < 4)
+write.csv(nolowqual, "../03_Data/sona_data_goodqual.csv", row.names = F)
+```
+
+```{r}
 
@@
 
-# > nrow(master)
-# [1] 564
-# > nrow(nomissing)
-# [1] 557
-# > nrow(nolowqual)
-# [1] 507
-# > nrow(noout)
-# [1] 464
-
-sona_screen_1 <- SAD(
-  dat = sona %>% 
-    select(Q2_1:Q2_21, `Q10_Page Submit`, `Q10_Click Count`),
-  rt = "Q10_Page Submit",
-  min = 1,
-  max = 5, 
-  partno = "ResponseId",
-  clicks = "Q10_Click Count",
-
-)
-
-## args: dat: Dataframe of scale values, with each row being a participant and each column being a scale question
-## args: rt: vector of response time/page time for each participant
-## args: min: minimum value of scale
-## args: max: maximum value of scale
-## args: partno: vector of corresponding participant numbers
-## args: clicks: click count column, outputted by qualtrics
-## args: manvec: vector of manipulation check question responses
-## args: mancor: correct answer of manipulation check
-## args: char: number of characters on the page
 ```

### 2024-09-01 05_Manuscript/manuscript.Rmd
work on intro

@@
 
-Introduction
-
-Example citation: [@dplyr]
-
-[@rosseel2012]
-
-Intro - awareness of death, especially in light of COVID.
+Intro paragraph - awareness of death, especially in light of COVID.
 
@@
 He called this act of caring generativity.
-In *The Denial of Death* (1973), philosopher Ernest Becker posits that humans undertake immortality projects to curb their sense of vulnerability to death.
-Similarly, psychiatrist Robert Jay Lifton (1979), a mentee of Erikson, described the awareness of death as being ever present and motivating us to create symbols thereby allowing ourselves to imagine us as symbolically immortalized.
-Existential psychiatrist, Irvin Yalom (2008) notes that many of his clients experiencing anxiety about their death take comfort in “rippling”, the idea that one’s lasting effects on the world will ripple out and influence the world after they have died.
+In *The Denial of Death*, philosopher Ernest Becker (1973) posits that humans undertake immortality projects to curb their sense of vulnerability to death.
+Similarly, psychiatrist Robert Jay Lifton (1979), a mentee of Erikson, described the awareness of death as being ever present and motivating us to create symbols, thereby allowing us to imagine ourselves as symbolically immortalized.
+Existential psychiatrist Irvin Yalom (2008) notes that many of his clients experiencing anxiety about their death take comfort in “rippling,” the idea that one’s lasting effects on the world will ripple out and influence the world after they have died.
 
 Although these thinkers use different terminology, there are several common themes among their ideas.
-(1) Our physical death is an inevitability, and we often find our awareness of its inevitability to be aversive: that is, it can cause angst, death-anxiety, despair, being-towards-death, terror, and so on.
+(1) Our physical death is an inevitability, and we often find our awareness of its inevitability to be aversive.
+This aversion may be referred to varyingly as angst, death-anxiety, despair, being-towards-death, terror, and so on.
 However, (2) we take comfort in the idea that other, non-physical parts of us continue to exist indefinitely after our biological death, through mechanisms such as the heroic archetype and symbolic self.
-(3) Finally, we can take action to promote these non-physical aspects of the self, such as through search for meaning, immortality project, care, generativity, rippling.
+(3) Finally, we can take action to promote these non-physical aspects of the self, such as through search for meaning, immortality project, care, generativity, and rippling.
 
-Sense of symbolic immortality was originally theorized by Lifton (1979), who thought that awareness of death drives a fundamental human need to "develop a sense of continuity and lastingness" beyond the lifespan (quote from Drolet 1990).
-Humans as meaning-seeking creatures.
+One of these bodies of thought, called symbolic immortality, was originally theorized by Lifton (1979), who thought that awareness of death drives a fundamental human desire for a sense of continuity lasting beyond the lifespan.
+Essentially, humans are meaning-seeking creatures, and throughout our lives, this search for meaning involves an evolving psychological imagery of life and death.
+Death, or the transient nature of life, threatens our search of meaning.
+He thought that if we could achieve what we believe to be some form of immortality, we could overcome this loss of meaning, and the awareness of death could instead drive an inner vitality (imagery associated with connection, integrity, and movement).
+If this drive toward vitality is lost, we are vulnerable to what Lifton called a psychic numbness (imagery associated with separation, disintegration, and stasis).
+In Lifton's own words, "Death does indeed bring about biological and psychic annihilation.
+But life includes symbolic perceptions of connections that precede and outlast that annihilation" (1979, p.
+18).
 
@@
 
-Sense of psychological death?
-
-Though some denial of death is thought to be universal, acceptance of the reality of death can drive what Drolet (1990) refers to as personal and collective creativity, or what Erikson referred to as generativity.
-Erikson's theory and generativity.
-
-Current measures of generativity are more about domains of generativity, actions, trait rather than underlying motives.
-Loyola Generativity Scale and the authors' understanding of the dimensions of generativity.
-Underlying motivation of generativity thought to be related to a motive to expand the sense of self beyond the lifetime (Kotre 1984), especially in light of the fear of death.
-McAdams and de St.
-Aubin (1992) indeed found symbolic immortality to be one of five themes across content analysis of autobiographical episodes.
-
-Somewhat loss of religiosity in the West that may have been a way of coping/finding a sense of immortality in the past.
-Likely this may have fallen under the umbrella of the spiritual mode of immortality, and for many a literal belief in life after death.
-Perhaps many now would benefit more from a sense of collective, social, or creative immortality.
-(some citations here if I keep this paragraph)
-
 Claims of how we suppress death-anxiety have been investigated experimentally, primarily through the paradigm of Terror Management Theory (TMT).
 Based on the theories of Ernest Becker, TMT posits that human awareness of death is always present to some degree.
-This awareness of our inevitable death, coupled with a strong aversion to thoughts of death, causes terror and is pushed out of our consciousness by our creation of meaning systems (CITATION).
+This awareness of our inevitable death, coupled with a strong aversion to thoughts of death, causes terror and is pushed out of our consciousness by our creation of meaning systems [@greenberg1986].
+TMT proposes that self-esteem, interpersonal relationships, and cultural worldview work together to buffer against our anxiety about death.
+It is assumed that these buffers suppress thoughts of death by providing a sense of symbolic immortality, though little systematic research has been conducted on this construct.
+The results of this buffering process are not always positive.
+For example, experimentally priming mortality salience can lead to more positive attitudes toward in-group members but harsher negative attitudes toward out-group members [@greenberg1990].
+
 TMT refers to a person's awareness of death as mortality salience (MS).
 The MS hypothesis of TMT posits than an increase in one's awareness of death causes an increase in compensatory behaviors to lower their death anxiety, either by distracting from the awareness of death or by the promotion of meaningful cultural worldviews.
-A meta-analysis of 277 experiments has found mortality salience to have moderate effects (*r* = 0.35; Burke, Martens & Faucher, 2010).
-TMT literature has found three consistent buffers of our awareness of death: self-esteem, interpersonal relationships, and cultural worldview (CITATION, unless it's the same as above, in which case make that clear).
+In the MS paradigm, experimentally priming a participant’s awareness of death (for example, by having participants write about death and then complete a distraction task) is thought to cause an increase in compensatory buffers.
+A meta-analysis of 277 experiments found mortality salience to have a robust, moderate overal effect size: *r*(276) = 0.35, *p* = .00 [@burke2010].
+Altogether, these experiments provide convincing evidence for TMT and the MS hypothesis in particular.
 
-TMT research is conducted in two paradigms.
-In the MS paradigm, a participant’s increased awareness of death causes an increase in compensatory buffers.
-In the death-thought accessibility paradigm, experimentally decreasing participants’ buffers, such as lowering self-esteem or challenging their worldview beliefs, causes (CHECK THIS AND CITE ACTUAL STUDIES) an increase in their awareness of death.
-Together, these experiments provide convincing evidence of these of suppressing awareness of death and death anxiety.
+Though some avoidance of (or buffering against) death anxiety is thought to be universal and has the potential to increase interpersonal conflict, awareness of death through symbolic immortality may also have potential as a positive force.
+In particular, it is thought to be an underlying motive for what Erikson referred to as generativity.
+Generativity is the seventh of eight proposed stages in Erikson's (1950) theory of psychosocial development, which he associated with midlife and described as "the concern in establishing and guiding the next generation" (Erikson, 1963, p.
+267).
+Little systematic research was conducted on this subject until the 1980's.
+Kotre (1984) expanded on the theory and proposed that the drive for generativity was related to a motive to expand the sense of self beyond the lifetime, especially in light of the fear of death.
 
-It is assumed that such changes in attitude and behavior suppress thoughts of death by giving a sense of existential immortality; however, to our knowledge no researchers have attempted to assess subjective feelings of immortality.
-This missing literature may in part be because of a lack of a viable measure of existential immortality.
-We view this dearth as a large gap in the literature and methodology.
+McAdams and de St.
+Aubin (1992) sought to formalize the study of generativity as a multidimensional construct.
+Their seven components of generativity include cultural demand, inner desire (for symbolic immortality and community), concern (for the next generation), belief (in the human species), commitment, action, and narration (of generativity within one's life story).
+In addition to a quantitative measure of generative concern (the Loyola Generativity Scale), they developed a system for content analysis of autobiographical episodes pertaining to generativity, and symbolic immortality is one of the five themes they found.
+Here they define symbolic immortality as "any reference to leaving a legacy, having an enduring influence, or leaving behind products that will outlive one's physical existence," a theme clearly related to both Lifton's and Erikson's theories (McAdams & de St.
+Aubin, 1992, p.
+1011).
+
+These research areas depend on the construct of symbolic immortality for their theoretical frameworks, but few researchers have attempted to systematically and quantitatively assess this construct.
 Two attempts have been made to develop such a measurement: Drolet's (1990) Sense of Symbolic Immortality Scale and Mathews and Kling (1988) measure of symbolic immortality, based on an original questionnaire by Mathews and Mister (1987).
-
-NOTE\*\*\* can't get access to the Mathews and Kling article but it seems mostly related to prosocial behavior for nonprofit stuff - should we just focus on the original Mathews and Mister article?
-Some other articles I found use the Mathews and Kling version though.
-<https://journals.sagepub.com/doi/abs/10.1177/089976408801700202?download=true&journalCode=nvsa>
 
@@
 Although internal consistency was at least acceptable for each factor, goodness of fit statistics are not reported.
-The items themselves seem to have more face validity than the scale by Drolet, but some factors seem more behavioral and specific: pertaining to one's religiosity or biological children, whereas Lifton's theory allows for a broader interpretation of these dimensions.
-The Nature and Creative factors seems most useful and theoretically aligned with Lifton.
+Mathews and Kling's (1988) study reported similar results for their revised scale.
+The items themselves seem to have more face validity than the scale by Drolet, but some factors seem more behavioral and unnecessarily specific: pertaining to one's religiosity or biological children, whereas Lifton's theory allows for a broader interpretation of these dimensions.
+The Nature and Creative factors seem most useful and theoretically aligned with Lifton.
 
-The goal of the present research is to develop a scale that more directly measures one’s sense of existential immortality in a way more generally applicable regardless of a person's religious beliefs and parental status.
-We have attempted to use current best practices for scale development.
+Much more advanced factor analysis methods have been developed since the 1980s, but to our knowledge, these scales have not been tested with more robust tools.
+The goal of the present research is to develop an up-to-date symbolic immortality scale that more directly measures one’s sense of symbolic immortality and which contains items more generally applicable to broad groups of participants (e.g., regardless of a person's religious beliefs and parental status).
+We have attempted to use current best practices for scale development and analysis.
 

### 2024-09-17 05_Manuscript/manuscript.Rmd
intro work

@@
 
-Intro paragraph - awareness of death, especially in light of COVID.
-
+Death is something each of us must learn to cope with, whether in healthy ways or less so.
+These issues may be at front of mind for many in light of the COVID-19 pandemic.
 Various existential philosophers and psychologists have proposed ways in which we deal with the awareness of death and the anxiety this awareness often causes.
@@
 (1) Our physical death is an inevitability, and we often find our awareness of its inevitability to be aversive.
-This aversion may be referred to varyingly as angst, death-anxiety, despair, being-towards-death, terror, and so on.
+This aversion may be referred to variously as angst, death-anxiety, despair, being-towards-death, terror, and so on.
 However, (2) we take comfort in the idea that other, non-physical parts of us continue to exist indefinitely after our biological death, through mechanisms such as the heroic archetype and symbolic self.
-(3) Finally, we can take action to promote these non-physical aspects of the self, such as through search for meaning, immortality project, care, generativity, and rippling.
+(3) Finally, we can take action to promote these non-physical aspects of the self, such as through search for meaning, sense of immortality, care, generativity, and rippling.
 
@@
 Essentially, humans are meaning-seeking creatures, and throughout our lives, this search for meaning involves an evolving psychological imagery of life and death.
-Death, or the transient nature of life, threatens our search of meaning.
-He thought that if we could achieve what we believe to be some form of immortality, we could overcome this loss of meaning, and the awareness of death could instead drive an inner vitality (imagery associated with connection, integrity, and movement).
-If this drive toward vitality is lost, we are vulnerable to what Lifton called a psychic numbness (imagery associated with separation, disintegration, and stasis).
+Death, or the transient nature of life, threatens our search for meaning.
+Lifton thought that if we could achieve what we believe to be some form of immortality, we could overcome this loss of meaning, and the awareness of death could instead drive an inner vitality (imagery associated with connection, integrity, and movement).
+If this drive toward vitality is lost, we are vulnerable to a psychic numbness or death-in-life (imagery associated with separation, disintegration, and stasis).
 In Lifton's own words, "Death does indeed bring about biological and psychic annihilation.
@@
 
-Lifton (1979) proposed five modes of experience or ways of achieving symbolic immortality: The biological (or biosocial) mode in which one lives on through their genetic and socio-cultural progeny, the creative mode in which one’s accomplishments and contribution outlast oneself, the natural mode in which one feels they are a part of the broader universe, the spiritual mode in which one seeks to transcend the physical realm to a higher spiritual realm beyond death, and the mode of experiential transcendence in which one experiences a phenomenological state of flow.
-The latter (experiential transcendence) must occur in the context of one of the other four to really be considered transcendent, but it is thought to have a great capacity to bring about personal change.
+Lifton (1979) proposed five modes of experience or ways of achieving symbolic immortality: The biological (or biosocial) mode in which one lives on through their genetic and sociocultural progeny, the creative mode in which one’s accomplishments and contribution outlast oneself, the natural mode in which one feels they are a part of the broader universe, the spiritual mode in which one seeks to transcend the physical realm to a higher spiritual realm beyond death, and the mode of experiential transcendence in which one experiences a phenomenological state of flow.
+The experiential mode must occur in the context of at least one of the other four to really be considered transcendent, but it is thought to have a great capacity to bring about personal change.
 
@@
 In the MS paradigm, experimentally priming a participant’s awareness of death (for example, by having participants write about death and then complete a distraction task) is thought to cause an increase in compensatory buffers.
-A meta-analysis of 277 experiments found mortality salience to have a robust, moderate overal effect size: *r*(276) = 0.35, *p* = .00 [@burke2010].
+A meta-analysis of 277 experiments found mortality salience to have a robust, moderate overall effect size: *r*(276) = 0.35, *p* = .00 [@burke2010].
 Altogether, these experiments provide convincing evidence for TMT and the MS hypothesis in particular.
@@
 The measure is inherently subjective, not only by the nature of self-report, but in that the scale seeks to measure what a person *believes* and how they *feel* about these subjects.
-The scale as a whole had a high internal consistency (alpha = .91) and test-retest reliability was r = .97.
+The scale as a whole had a high internal consistency (*\$\\alpha\$* = .91) and test-retest reliability was *r* = .97.
 Internal consistency of subscales for the five theoretical modes of immortality was mixed.
 Of the five, spiritual immortality was the most distinct from the scale as a whole and the other subscales.
-(Note that this seems relevant to what we found in our own scale development.
-For more in the Discussion later on.) Factor analysis showed three factors, mapping onto biosocial, creative, and spiritual.
-The transcendent and natural items may be related to biosocial.
+Factor analysis showed three factors, mapping onto biosocial, creative, and spiritual.
+The transcendent and natural items may be closely related to biosocial.
 
-Moving beyond the scale development itself (still Drolet 1990), SSI correlated negatively with death anxiety (Templer's Death Anxiety Scale) and had a strong (r = .84) positive relationship with purpose in life (Maholick's Purpose in Life Test).
+Moving beyond the scale development itself (still Drolet 1990), SSI correlated negatively with death anxiety (Templer's Death Anxiety Scale) and had a strong (*r* = .84) positive relationship with purpose in life (Maholick's Purpose in Life Test).
 In interpreting the very strong correlation, the author suggests that SSI is a broader construct than Purpose in Life and the scale itself may be less prone to social desirability effects than the PIL, although this had not been directly tested.
@@
 
-Mathews and Mister (1987) also developed a scale involving symbolic immortality, sensation seeking, and psychic numbness.
+Mathews and Mister (1987) also developed a scale pertaining to symbolic immortality, sensation seeking, and psychic numbness in a study including 400 adults.
+Experiential transcendence was operationalized as something like Zuckerman's (1979) sensation seeking, which may not fully capture the original intent (the experience of losing oneself).
+Items were mapped onto five factors, and the five factors largely aligned with Lifton's constructs.
+Although internal consistency was at least acceptable for each factor, goodness of fit statistics are not reported.
 Some studies have used a revised version of the scale by Mathews and Kling (1988), who adapted it for a study on prosocial behavior in the context of nonprofit volunteer motivation.
-Mathews and Mister's study included 400 adults.
-Experiential transcendence was operationalized as something like Zuckerman's (1979) sensation seeking, which may not fully capture the original intent (the experience of losing oneself).
-Items were forced into five factors, and the five factors largely aligned with Lifton's constructs.
-Although internal consistency was at least acceptable for each factor, goodness of fit statistics are not reported.
-Mathews and Kling's (1988) study reported similar results for their revised scale.
-The items themselves seem to have more face validity than the scale by Drolet, but some factors seem more behavioral and unnecessarily specific: pertaining to one's religiosity or biological children, whereas Lifton's theory allows for a broader interpretation of these dimensions.
+They reported similar results for their revised scale.
+The items on these scales seem to have more face validity than the scale by Drolet, but some factors seem more behavioral and unnecessarily specific: pertaining to one's religiosity or biological children, whereas Lifton's theory allows for a broader interpretation of these dimensions.
 The Nature and Creative factors seem most useful and theoretically aligned with Lifton.

### 2024-09-21 05_Manuscript/manuscript.Rmd
updating doc

@@
 shorttitle        : "Title"
-
 author: 
@@
       - "Supervision"
-
 affiliation:
@@
     institution   : "Konstanz Business School"
-
 authornote: |
   Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
   Enter author note here.
-
 abstract: |
@@
   <!-- https://tinyurl.com/ybremelq -->
-
 keywords          : "keywords"
 wordcount         : "X"
-
 floatsintext      : no
@@
 mask              : no
-
 figurelist        : no
@@
 footnotelist      : no
-
 classoption       : "man"
@@
 bibliography: references.bib
+editor_options: 
+  markdown: 
+    wrap: 72
 ---
@@
 
-Death is something each of us must learn to cope with, whether in healthy ways or less so.
-These issues may be at front of mind for many in light of the COVID-19 pandemic.
-Various existential philosophers and psychologists have proposed ways in which we deal with the awareness of death and the anxiety this awareness often causes.
-Psychoanalyst Erik Erikson (1950) proposed that during mid-life one becomes acutely aware of their oncoming death and is motivated to care for things which will outlast themselves.
-He called this act of caring generativity.
-In *The Denial of Death*, philosopher Ernest Becker (1973) posits that humans undertake immortality projects to curb their sense of vulnerability to death.
-Similarly, psychiatrist Robert Jay Lifton (1979), a mentee of Erikson, described the awareness of death as being ever present and motivating us to create symbols, thereby allowing us to imagine ourselves as symbolically immortalized.
-Existential psychiatrist Irvin Yalom (2008) notes that many of his clients experiencing anxiety about their death take comfort in “rippling,” the idea that one’s lasting effects on the world will ripple out and influence the world after they have died.
+Death is something each of us must learn to cope with, whether in
+healthy ways or less so. These issues may be at front of mind for many
+in light of the COVID-19 pandemic. Various existential philosophers and
+psychologists have proposed ways in which we deal with the awareness of
+death and the anxiety this awareness often causes. Psychoanalyst Erik
+Erikson (1950) proposed that during mid-life one becomes acutely aware
+of their oncoming death and is motivated to care for things which will
+outlast themselves. He called this act of caring generativity. In *The
+Denial of Death*, philosopher Ernest Becker (1973) posits that humans
+undertake immortality projects to curb their sense of vulnerability to
+death. Similarly, psychiatrist Robert Jay Lifton (1979), a mentee of
+Erikson, described the awareness of death as being ever present and
+motivating us to create symbols, thereby allowing us to imagine
+ourselves as symbolically immortalized. Existential psychiatrist Irvin
+Yalom (2008) notes that many of his clients experiencing anxiety about
+their death take comfort in “rippling,” the idea that one’s lasting
+effects on the world will ripple out and influence the world after they
+have died.
 
-Although these thinkers use different terminology, there are several common themes among their ideas.
-(1) Our physical death is an inevitability, and we often find our awareness of its inevitability to be aversive.
-This aversion may be referred to variously as angst, death-anxiety, despair, being-towards-death, terror, and so on.
-However, (2) we take comfort in the idea that other, non-physical parts of us continue to exist indefinitely after our biological death, through mechanisms such as the heroic archetype and symbolic self.
-(3) Finally, we can take action to promote these non-physical aspects of the self, such as through search for meaning, sense of immortality, care, generativity, and rippling.
+Although these thinkers use different terminology, there are several
+common themes among their ideas. (1) Our physical death is an
+inevitability, and we often find our awareness of its inevitability to
+be aversive. This aversion may be referred to variously as angst,
+death-anxiety, despair, being-towards-death, terror, and so on. However,
+(2) we take comfort in the idea that other, non-physical parts of us
+continue to exist indefinitely after our biological death, through
+mechanisms such as the heroic archetype and symbolic self. (3) Finally,
+we can take action to promote these non-physical aspects of the self,
+such as through search for meaning, sense of immortality, care,
+generativity, and rippling.
 
-One of these bodies of thought, called symbolic immortality, was originally theorized by Lifton (1979), who thought that awareness of death drives a fundamental human desire for a sense of continuity lasting beyond the lifespan.
-Essentially, humans are meaning-seeking creatures, and throughout our lives, this search for meaning involves an evolving psychological imagery of life and death.
-Death, or the transient nature of life, threatens our search for meaning.
-Lifton thought that if we could achieve what we believe to be some form of immortality, we could overcome this loss of meaning, and the awareness of death could instead drive an inner vitality (imagery associated with connection, integrity, and movement).
-If this drive toward vitality is lost, we are vulnerable to a psychic numbness or death-in-life (imagery associated with separation, disintegration, and stasis).
-In Lifton's own words, "Death does indeed bring about biological and psychic annihilation.
-But life includes symbolic perceptions of connections that precede and outlast that annihilation" (1979, p.
-18).
+One of these bodies of thought, called symbolic immortality, was
+originally theorized by Lifton (1979), who thought that awareness of
+death drives a fundamental human desire for a sense of continuity
+lasting beyond the lifespan. Essentially, humans are meaning-seeking
+creatures, and throughout our lives, this search for meaning involves an
+evolving psychological imagery of life and death. Death, or the
+transient nature of life, threatens our search for meaning. Lifton
+thought that if we could achieve what we believe to be some form of
+immortality, we could overcome this loss of meaning, and the awareness
+of death could instead drive an inner vitality (imagery associated with
+connection, integrity, and movement). If this drive toward vitality is
+lost, we are vulnerable to a psychic numbness or death-in-life (imagery
+associated with separation, disintegration, and stasis). In Lifton's own
+words, "Death does indeed bring about biological and psychic
+annihilation. But life includes symbolic perceptions of connections that
+precede and outlast that annihilation" (1979, p. 18).
 
-Lifton (1979) proposed five modes of experience or ways of achieving symbolic immortality: The biological (or biosocial) mode in which one lives on through their genetic and sociocultural progeny, the creative mode in which one’s accomplishments and contribution outlast oneself, the natural mode in which one feels they are a part of the broader universe, the spiritual mode in which one seeks to transcend the physical realm to a higher spiritual realm beyond death, and the mode of experiential transcendence in which one experiences a phenomenological state of flow.
-The experiential mode must occur in the context of at least one of the other four to really be considered transcendent, but it is thought to have a great capacity to bring about personal change.
+Lifton (1979) proposed five modes of experience or ways of achieving
+symbolic immortality: The biological (or biosocial) mode in which one
+lives on through their genetic and sociocultural progeny, the creative
+mode in which one’s accomplishments and contribution outlast oneself,
+the natural mode in which one feels they are a part of the broader
+universe, the spiritual mode in which one seeks to transcend the
+physical realm to a higher spiritual realm beyond death, and the mode of
+experiential transcendence in which one experiences a phenomenological
+state of flow. The experiential mode must occur in the context of at
+least one of the other four to really be considered transcendent, but it
+is thought to have a great capacity to bring about personal change.
 
-Claims of how we suppress death-anxiety have been investigated experimentally, primarily through the paradigm of Terror Management Theory (TMT).
-Based on the theories of Ernest Becker, TMT posits that human awareness of death is always present to some degree.
-This awareness of our inevitable death, coupled with a strong aversion to thoughts of death, causes terror and is pushed out of our consciousness by our creation of meaning systems [@greenberg1986].
-TMT proposes that self-esteem, interpersonal relationships, and cultural worldview work together to buffer against our anxiety about death.
-It is assumed that these buffers suppress thoughts of death by providing a sense of symbolic immortality, though little systematic research has been conducted on this construct.
-The results of this buffering process are not always positive.
-For example, experimentally priming mortality salience can lead to more positive attitudes toward in-group members but harsher negative attitudes toward out-group members [@greenberg1990].
+Claims of how we suppress death-anxiety have been investigated
+experimentally, primarily through the paradigm of Terror Management
+Theory (TMT). Based on the theories of Ernest Becker, TMT posits that
+human awareness of death is always present to some degree. This
+awareness of our inevitable death, coupled with a strong aversion to
+thoughts of death, causes terror and is pushed out of our consciousness
+by our creation of meaning systems [@greenberg1986]. TMT proposes that
+self-esteem, interpersonal relationships, and cultural worldview work
+together to buffer against our anxiety about death. It is assumed that
+these buffers suppress thoughts of death by providing a sense of
+symbolic immortality, though little systematic research has been
+conducted on this construct. The results of this buffering process are
+not always positive. For example, experimentally priming mortality
+salience can lead to more positive attitudes toward in-group members but
+harsher negative attitudes toward out-group members [@greenberg1990].
 
 TMT refers to a person's awareness of death as mortality salience (MS).
-The MS hypothesis of TMT posits than an increase in one's awareness of death causes an increase in compensatory behaviors to lower their death anxiety, either by distracting from the awareness of death or by the promotion of meaningful cultural worldviews.
-In the MS paradigm, experimentally priming a participant’s awareness of death (for example, by having participants write about death and then complete a distraction task) is thought to cause an increase in compensatory buffers.
-A meta-analysis of 277 experiments found mortality salience to have a robust, moderate overall effect size: *r*(276) = 0.35, *p* = .00 [@burke2010].
-Altogether, these experiments provide convincing evidence for TMT and the MS hypothesis in particular.
+The MS hypothesis of TMT posits than an increase in one's awareness of
+death causes an increase in compensatory behaviors to lower their death
+anxiety, either by distracting from the awareness of death or by the
+promotion of meaningful cultural worldviews. In the MS paradigm,
+experimentally priming a participant’s awareness of death (for example,
+by having participants write about death and then complete a distraction
+task) is thought to cause an increase in compensatory buffers. A
+meta-analysis of 277 experiments found mortality salience to have a
+robust, moderate overall effect size: *r*(276) = 0.35, *p* = .00
+[@burke2010]. Altogether, these experiments provide convincing evidence
+for TMT and the MS hypothesis in particular.
 
-Though some avoidance of (or buffering against) death anxiety is thought to be universal and has the potential to increase interpersonal conflict, awareness of death through symbolic immortality may also have potential as a positive force.
-In particular, it is thought to be an underlying motive for what Erikson referred to as generativity.
-Generativity is the seventh of eight proposed stages in Erikson's (1950) theory of psychosocial development, which he associated with midlife and described as "the concern in establishing and guiding the next generation" (Erikson, 1963, p.
-267).
-Little systematic research was conducted on this subject until the 1980's.
-Kotre (1984) expanded on the theory and proposed that the drive for generativity was related to a motive to expand the sense of self beyond the lifetime, especially in light of the fear of death.
+Though some avoidance of (or buffering against) death anxiety is thought
+to be universal and has the potential to increase interpersonal
+conflict, awareness of death through symbolic immortality may also have
+potential as a positive force. In particular, it is thought to be an
+underlying motive for what Erikson referred to as generativity.
+Generativity is the seventh of eight proposed stages in Erikson's (1950)
+theory of psychosocial development, which he associated with midlife and
+described as "the concern in establishing and guiding the next
+generation" (Erikson, 1963, p. 267). Little systematic research was
+conducted on this subject until the 1980's. Kotre (1984) expanded on the
+theory and proposed that the drive for generativity was related to a
+motive to expand the sense of self beyond the lifetime, especially in
+light of the fear of death.
 
-McAdams and de St.
-Aubin (1992) sought to formalize the study of generativity as a multidimensional construct.
-Their seven components of generativity include cultural demand, inner desire (for symbolic immortality and community), concern (for the next generation), belief (in the human species), commitment, action, and narration (of generativity within one's life story).
-In addition to a quantitative measure of generative concern (the Loyola Generativity Scale), they developed a system for content analysis of autobiographical episodes pertaining to generativity, and symbolic immortality is one of the five themes they found.
-Here they define symbolic immortality as "any reference to leaving a legacy, having an enduring influence, or leaving behind products that will outlive one's physical existence," a theme clearly related to both Lifton's and Erikson's theories (McAdams & de St.
-Aubin, 1992, p.
-1011).
+McAdams and de St. Aubin [-@mcadams1992] sought to formalize the study
+of generativity as a multidimensional construct. Their seven components
+of generativity include cultural demand, inner desire (for symbolic
+immortality and community), concern (for the next generation), belief
+(in the human species), commitment, action, and narration (of
+generativity within one's life story). In addition to a quantitative
+measure of generative concern (the Loyola Generativity Scale), they
+developed a system for content analysis of autobiographical episodes
+pertaining to generativity, and symbolic immortality is one of the five
+themes they found. Here they define symbolic immortality as "any
+reference to leaving a legacy, having an enduring influence, or leaving
+behind products that will outlive one's physical existence," a theme
+clearly related to both Lifton's and Erikson's theories [@mcadams1992,
+p. 1011].
 
-These research areas depend on the construct of symbolic immortality for their theoretical frameworks, but few researchers have attempted to systematically and quantitatively assess this construct.
-Two attempts have been made to develop such a measurement: Drolet's (1990) Sense of Symbolic Immortality Scale and Mathews and Kling (1988) measure of symbolic immortality, based on an original questionnaire by Mathews and Mister (1987).
+These research areas depend on the construct of symbolic immortality for
+their theoretical frameworks, but few researchers have attempted to
+systematically and quantitatively assess this construct. Two attempts
+have been made to develop such a measurement: Drolet's (1990) Sense of
+Symbolic Immortality Scale and Mathews and Kling (1988) measure of
+symbolic immortality, based on an original questionnaire by Mathews and
+Mister (1987).
 
-Drolet (1990) developed the Sense of Symbolic Immortality Scale based on Robert J.
-Lifton’s theory of symbolic immortality and its five modes of experience.
-Drolet studied 136 adults, ages 18-30 and 30-40, and hypothesized that those in their 30's (established adults) would have a greater sense of symbolic immortality than the young adults (18-30).
-The measure is inherently subjective, not only by the nature of self-report, but in that the scale seeks to measure what a person *believes* and how they *feel* about these subjects.
-The scale as a whole had a high internal consistency (*\$\\alpha\$* = .91) and test-retest reliability was *r* = .97.
-Internal consistency of subscales for the five theoretical modes of immortality was mixed.
-Of the five, spiritual immortality was the most distinct from the scale as a whole and the other subscales.
-Factor analysis showed three factors, mapping onto biosocial, creative, and spiritual.
-The transcendent and natural items may be closely related to biosocial.
+Drolet (1990) developed the Sense of Symbolic Immortality Scale based on
+Robert J. Lifton’s theory of symbolic immortality and its five modes of
+experience. Drolet studied 136 adults, ages 18-30 and 30-40, and
+hypothesized that those in their 30's (established adults) would have a
+greater sense of symbolic immortality than the young adults (18-30). The
+measure is inherently subjective, not only by the nature of self-report,
+but in that the scale seeks to measure what a person *believes* and how
+they *feel* about these subjects. The scale as a whole had a high
+internal consistency ($\alpha$ = .91) and test-retest reliability
+was *r* = .97. Internal consistency of subscales for the five
+theoretical modes of immortality was mixed. Of the five, spiritual
+immortality was the most distinct from the scale as a whole and the
+other subscales. Factor analysis showed three factors, mapping onto
+biosocial, creative, and spiritual. The transcendent and natural items
+may be closely related to biosocial.
 
-Moving beyond the scale development itself (still Drolet 1990), SSI correlated negatively with death anxiety (Templer's Death Anxiety Scale) and had a strong (*r* = .84) positive relationship with purpose in life (Maholick's Purpose in Life Test).
-In interpreting the very strong correlation, the author suggests that SSI is a broader construct than Purpose in Life and the scale itself may be less prone to social desirability effects than the PIL, although this had not been directly tested.
-Age group was also related, with established adults having a higher SSI, particularly in the biosocial and creative domains.
+Moving beyond the scale development itself (still Drolet 1990), SSI
+correlated negatively with death anxiety (Templer's Death Anxiety Scale)
+and had a strong (*r* = .84) positive relationship with purpose in life
+(Maholick's Purpose in Life Test). In interpreting the very strong
+correlation, the author suggests that SSI is a broader construct than
+Purpose in Life and the scale itself may be less prone to social
+desirability effects than the PIL, although this had not been directly
+tested. Age group was also related, with established adults having a
+higher SSI, particularly in the biosocial and creative domains.
 
-We see multiple issues with using the Symbolic Immortality Scale.
-First, the study was underpowered, conducting exploratory factor analysis of 67 items using a sample of 136.
-Second, the scale was developed in French, and we do not take for granted the psychometric properties of a translated version.
-Third and most fundamentally, the scale has poor face validity and appears to measure the constructs theorized to symbolically immortalize rather than a sense of symbolic immortality directly.
-For example, the scale includes items such as “My sex life contributes greatly to my well-being”, “Intimate relationships scare me”, and “I am sure of who I am." Although related to the constructs (such as interpersonal relationships and self-esteem) which theoretically help cope with death, it is unclear how these items represent the construct of symbolic immortality itself.
+We see multiple issues with using the Symbolic Immortality Scale. First,
+the study was underpowered, conducting exploratory factor analysis of 67
+items using a sample of 136. Second, the scale was developed in French,
+and we do not take for granted the psychometric properties of a
+translated version. Third and most fundamentally, the scale has poor
+face validity and appears to measure the constructs theorized to
+symbolically immortalize rather than a sense of symbolic immortality
+directly. For example, the scale includes items such as “My sex life
+contributes greatly to my well-being”, “Intimate relationships scare
+me”, and “I am sure of who I am." Although related to the constructs
+(such as interpersonal relationships and self-esteem) which
+theoretically help cope with death, it is unclear how these items
+represent the construct of symbolic immortality itself.
 
-Mathews and Mister (1987) also developed a scale pertaining to symbolic immortality, sensation seeking, and psychic numbness in a study including 400 adults.
-Experiential transcendence was operationalized as something like Zuckerman's (1979) sensation seeking, which may not fully capture the original intent (the experience of losing oneself).
-Items were mapped onto five factors, and the five factors largely aligned with Lifton's constructs.
-Although internal consistency was at least acceptable for each factor, goodness of fit statistics are not reported.
-Some studies have used a revised version of the scale by Mathews and Kling (1988), who adapted it for a study on prosocial behavior in the context of nonprofit volunteer motivation.
-They reported similar results for their revised scale.
-The items on these scales seem to have more face validity than the scale by Drolet, but some factors seem more behavioral and unnecessarily specific: pertaining to one's religiosity or biological children, whereas Lifton's theory allows for a broader interpretation of these dimensions.
-The Nature and Creative factors seem most useful and theoretically aligned with Lifton.
+Mathews and Mister (1987) also developed a scale pertaining to symbolic
+immortality, sensation seeking, and psychic numbness in a study
+including 400 adults. Experiential transcendence was operationalized as
+something like Zuckerman's (1979) sensation seeking, which may not fully
+capture the original intent (the experience of losing oneself). Items
+were mapped onto five factors, and the five factors largely aligned with
+Lifton's constructs. Although internal consistency was at least
+acceptable for each factor, goodness of fit statistics are not reported.
+Some studies have used a revised version of the scale by Mathews and
+Kling (1988), who adapted it for a study on prosocial behavior in the
+context of nonprofit volunteer motivation. They reported similar results
+for their revised scale. The items on these scales seem to have more
+face validity than the scale by Drolet, but some factors seem more
+behavioral and unnecessarily specific: pertaining to one's religiosity
+or biological children, whereas Lifton's theory allows for a broader
+interpretation of these dimensions. The Nature and Creative factors seem
+most useful and theoretically aligned with Lifton.
 
-Much more advanced factor analysis methods have been developed since the 1980s, but to our knowledge, these scales have not been tested with more robust tools.
-The goal of the present research is to develop an up-to-date symbolic immortality scale that more directly measures one’s sense of symbolic immortality and which contains items more generally applicable to broad groups of participants (e.g., regardless of a person's religious beliefs and parental status).
-We have attempted to use current best practices for scale development and analysis.
+Much more advanced factor analysis methods have been developed since the
+1980s, but to our knowledge, these scales have not been tested with more
+robust tools. The goal of the present research is to develop an
+up-to-date symbolic immortality scale that more directly measures one’s
+sense of symbolic immortality and which contains items more generally
+applicable to broad groups of participants (e.g., regardless of a
+person's religious beliefs and parental status). We have attempted to
+use current best practices for scale development and analysis.
 
@@
 
-```{r}
+```{r sona-outliers, eval = F}
+nolowqual <- import("../03_Data/sona_data_goodqual.csv")
 
-# Outliers ----------------------------------------------------------------
+mahal <- mahalanobis(nolowqual %>% select(Q2_1:Q5_20),
+                     colMeans(nolowqual %>% select(Q2_1:Q5_20), na.rm = TRUE),
+                     cov(nolowqual %>% select(Q2_1:Q5_20), use="pairwise.complete.obs"))
 
-mahal = mahalanobis(nolowqual[ , 37:97], 
-                    colMeans(nolowqual[ , 37:97], na.rm = TRUE),
-                    cov(nolowqual[ , 37:97], use="pairwise.complete.obs"))
-
-cutoff = qchisq(1 - .001,ncol(nolowqual[ , 37:97]))
-ncol(nolowqual[ , 37:97]) #df 61
+cutoff <- qchisq(1 - .001,
+                 ncol(nolowqual %>% select(Q2_1:Q5_20)))
+ncol(nolowqual %>% select(Q2_1:Q5_20)) #df 61
 cutoff #cutoff 100.8879
@@
 summary(mahal < cutoff)
-mahal[mahal > cutoff]
 
@@
 #42 participants excluded as outliers
+```
+
+-   try running with outliers as well --\> if differences: then talk
+    about what is going on with the outlier people
 
@@
 
-# Linearity #
-random = rchisq(nrow(noout[ , 37:97]), 7) 
-fake = lm(random~., data=noout[ , 37:97])
+# Linearity
 
-standardized = rstudent(fake)
-{qqnorm(standardized)
-  abline(0,1)}
-#seems okay
+random = rchisq(nrow(noout[ , 37:97]), 7) fake = lm(random\~.,
+data=noout[ , 37:97])
 
-# Normality #
-hist(standardized, breaks=15)
-#a little skewed but mostly centered on 0 and between -2 and 2 so okay
+standardized = rstudent(fake) {qqnorm(standardized) abline(0,1)} #seems
+okay
 
-# Homog/s #
-fitvalues = scale(fake$fitted.values)
-{plot(fitvalues, standardized) 
-  abline(0,0)
-  abline(v = 0)}
-#some homogeneity issues but we'll accept it
+# Normality
+
+hist(standardized, breaks=15) #a little skewed but mostly centered on 0
+and between -2 and 2 so okay
+
+# Homog/s
+
+fitvalues = scale(fake\$fitted.values) {plot(fitvalues, standardized)
+abline(0,0) abline(v = 0)} #some homogeneity issues but we'll accept it
 
 write.csv(noout, file = "sona_data_screened.csv", row.names = F)
-library(beepr)
-beep(sound = 5)
+library(beepr) beep(sound = 5)
 
-```
+\`\`\`
 

### 2024-09-21 05_Manuscript/manuscript.tex
updating doc

--- 2024-08-13 manuscript.tex
@@
 \makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
 % Set default figure placement to htbp
-\makeatletter
 \def\fps@figure{htbp}
@@
 % Make \paragraph and \subparagraph free-standing
+\makeatletter
 \ifx\paragraph\undefined\else
   \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
 \fi
@@
   \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
+\makeatother
 % definitions for citeproc citations
@@
 \def\languageshorthands#1{}
+\ifLuaTeX
+  \usepackage[english]{selnolig} % disable illegal ligatures
+\fi
 % Manuscript styling
@@
 \usepackage{csquotes}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
 \usepackage{bookmark}
@@
 Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
 Enter author note here.
@@
 
-Introduction
+Death is something each of us must learn to cope with, whether in
+healthy ways or less so. These issues may be at front of mind for many
+in light of the COVID-19 pandemic. Various existential philosophers and
+psychologists have proposed ways in which we deal with the awareness of
+death and the anxiety this awareness often causes. Psychoanalyst Erik
+Erikson (1950) proposed that during mid-life one becomes acutely aware
+of their oncoming death and is motivated to care for things which will
+outlast themselves. He called this act of caring generativity. In \emph{The
+Denial of Death}, philosopher Ernest Becker (1973) posits that humans
+undertake immortality projects to curb their sense of vulnerability to
+death. Similarly, psychiatrist Robert Jay Lifton (1979), a mentee of
+Erikson, described the awareness of death as being ever present and
+motivating us to create symbols, thereby allowing us to imagine
+ourselves as symbolically immortalized. Existential psychiatrist Irvin
+Yalom (2008) notes that many of his clients experiencing anxiety about
+their death take comfort in ``rippling,'' the idea that one's lasting
+effects on the world will ripple out and influence the world after they
+have died.
 
-(Wickham, François, Henry, Müller, \& Vaughan, 2023)
+Although these thinkers use different terminology, there are several
+common themes among their ideas. (1) Our physical death is an
+inevitability, and we often find our awareness of its inevitability to
+be aversive. This aversion may be referred to variously as angst,
+death-anxiety, despair, being-towards-death, terror, and so on. However,
+(2) we take comfort in the idea that other, non-physical parts of us
+continue to exist indefinitely after our biological death, through
+mechanisms such as the heroic archetype and symbolic self. (3) Finally,
+we can take action to promote these non-physical aspects of the self,
+such as through search for meaning, sense of immortality, care,
+generativity, and rippling.
 
-(Rosseel, 2012)
+One of these bodies of thought, called symbolic immortality, was
+originally theorized by Lifton (1979), who thought that awareness of
+death drives a fundamental human desire for a sense of continuity
+lasting beyond the lifespan. Essentially, humans are meaning-seeking
+creatures, and throughout our lives, this search for meaning involves an
+evolving psychological imagery of life and death. Death, or the
+transient nature of life, threatens our search for meaning. Lifton
+thought that if we could achieve what we believe to be some form of
+immortality, we could overcome this loss of meaning, and the awareness
+of death could instead drive an inner vitality (imagery associated with
+connection, integrity, and movement). If this drive toward vitality is
+lost, we are vulnerable to a psychic numbness or death-in-life (imagery
+associated with separation, disintegration, and stasis). In Lifton's own
+words, ``Death does indeed bring about biological and psychic
+annihilation. But life includes symbolic perceptions of connections that
+precede and outlast that annihilation'' (1979, p.~18).
 
-\section{Methods}\label{methods}
+Lifton (1979) proposed five modes of experience or ways of achieving
+symbolic immortality: The biological (or biosocial) mode in which one
+lives on through their genetic and sociocultural progeny, the creative
+mode in which one's accomplishments and contribution outlast oneself,
+the natural mode in which one feels they are a part of the broader
+universe, the spiritual mode in which one seeks to transcend the
+physical realm to a higher spiritual realm beyond death, and the mode of
+experiential transcendence in which one experiences a phenomenological
+state of flow. The experiential mode must occur in the context of at
+least one of the other four to really be considered transcendent, but it
+is thought to have a great capacity to bring about personal change.
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+Claims of how we suppress death-anxiety have been investigated
+experimentally, primarily through the paradigm of Terror Management
+Theory (TMT). Based on the theories of Ernest Becker, TMT posits that
+human awareness of death is always present to some degree. This
+awareness of our inevitable death, coupled with a strong aversion to
+thoughts of death, causes terror and is pushed out of our consciousness
+by our creation of meaning systems (Greenberg, Pyszczynski, \& Solomon, 1986). TMT proposes that
+self-esteem, interpersonal relationships, and cultural worldview work
+together to buffer against our anxiety about death. It is assumed that
+these buffers suppress thoughts of death by providing a sense of
+symbolic immortality, though little systematic research has been
+conducted on this construct. The results of this buffering process are
+not always positive. For example, experimentally priming mortality
+salience can lead to more positive attitudes toward in-group members but
+harsher negative attitudes toward out-group members (Greenberg et al., 1990).
+
+TMT refers to a person's awareness of death as mortality salience (MS).
+The MS hypothesis of TMT posits than an increase in one's awareness of
+death causes an increase in compensatory behaviors to lower their death
+anxiety, either by distracting from the awareness of death or by the
+promotion of meaningful cultural worldviews. In the MS paradigm,
+experimentally priming a participant's awareness of death (for example,
+by having participants write about death and then complete a distraction
+task) is thought to cause an increase in compensatory buffers. A
+meta-analysis of 277 experiments found mortality salience to have a
+robust, moderate overall effect size: \emph{r}(276) = 0.35, \emph{p} = .00
+(Burke, Martens, \& Faucher, 2010). Altogether, these experiments provide convincing evidence
+for TMT and the MS hypothesis in particular.
+
+Though some avoidance of (or buffering against) death anxiety is thought
+to be universal and has the potential to increase interpersonal
+conflict, awareness of death through symbolic immortality may also have
+potential as a positive force. In particular, it is thought to be an
+underlying motive for what Erikson referred to as generativity.
+Generativity is the seventh of eight proposed stages in Erikson's (1950)
+theory of psychosocial development, which he associated with midlife and
+described as ``the concern in establishing and guiding the next
+generation'' (Erikson, 1963, p.~267). Little systematic research was
+conducted on this subject until the 1980's. Kotre (1984) expanded on the
+theory and proposed that the drive for generativity was related to a
+motive to expand the sense of self beyond the lifetime, especially in
+light of the fear of death.
+
+McAdams and de St.~Aubin (1992) sought to formalize the study
+of generativity as a multidimensional construct. Their seven components
+of generativity include cultural demand, inner desire (for symbolic
+immortality and community), concern (for the next generation), belief
+(in the human species), commitment, action, and narration (of
+generativity within one's life story). In addition to a quantitative
+measure of generative concern (the Loyola Generativity Scale), they
+developed a system for content analysis of autobiographical episodes
+pertaining to generativity, and symbolic immortality is one of the five
+themes they found. Here they define symbolic immortality as ``any
+reference to leaving a legacy, having an enduring influence, or leaving
+behind products that will outlive one's physical existence,'' a theme
+clearly related to both Lifton's and Erikson's theories (Aust et al., 2022; McAdams \& St. Aubin, 1992, p. 1011).
+
+(Aust et al., 2022; Mathews \& Kling, 1988)
+
+(McAdams \& de St.~Aubin, 1992, p.~1011).
+
+These research areas depend on the construct of symbolic immortality for
+their theoretical frameworks, but few researchers have attempted to
+systematically and quantitatively assess this construct. Two attempts
+have been made to develop such a measurement: Drolet's (1990) Sense of
+Symbolic Immortality Scale and Mathews and Kling (1988) measure of
+symbolic immortality, based on an original questionnaire by Mathews and
+Mister (1987).
+
+Drolet (1990) developed the Sense of Symbolic Immortality Scale based on
+Robert J. Lifton's theory of symbolic immortality and its five modes of
+experience. Drolet studied 136 adults, ages 18-30 and 30-40, and
+hypothesized that those in their 30's (established adults) would have a
+greater sense of symbolic immortality than the young adults (18-30). The
+measure is inherently subjective, not only by the nature of self-report,
+but in that the scale seeks to measure what a person \emph{believes} and how
+they \emph{feel} about these subjects. The scale as a whole had a high
+internal consistency (\emph{\$\textbackslash alpha\$} = .91) and test-retest reliability
+was \emph{r} = .97. Internal consistency of subscales for the five
+theoretical modes of immortality was mixed. Of the five, spiritual
+immortality was the most distinct from the scale as a whole and the
+other subscales. Factor analysis showed three factors, mapping onto
+biosocial, creative, and spiritual. The transcendent and natural items
+may be closely related to biosocial.
+
+Moving beyond the scale development itself (still Drolet 1990), SSI
+correlated negatively with death anxiety (Templer's Death Anxiety Scale)
+and had a strong (\emph{r} = .84) positive relationship with purpose in life
+(Maholick's Purpose in Life Test). In interpreting the very strong
+correlation, the author suggests that SSI is a broader construct than
+Purpose in Life and the scale itself may be less prone to social
+desirability effects than the PIL, although this had not been directly
+tested. Age group was also related, with established adults having a
+higher SSI, particularly in the biosocial and creative domains.
+
+We see multiple issues with using the Symbolic Immortality Scale. First,
+the study was underpowered, conducting exploratory factor analysis of 67
+items using a sample of 136. Second, the scale was developed in French,
+and we do not take for granted the psychometric properties of a
+translated version. Third and most fundamentally, the scale has poor
+face validity and appears to measure the constructs theorized to
+symbolically immortalize rather than a sense of symbolic immortality
+directly. For example, the scale includes items such as ``My sex life
+contributes greatly to my well-being'', ``Intimate relationships scare
+me'', and ``I am sure of who I am.'' Although related to the constructs
+(such as interpersonal relationships and self-esteem) which
+theoretically help cope with death, it is unclear how these items
+represent the construct of symbolic immortality itself.
+
+Mathews and Mister (1987) also developed a scale pertaining to symbolic
+immortality, sensation seeking, and psychic numbness in a study
+including 400 adults. Experiential transcendence was operationalized as
+something like Zuckerman's (1979) sensation seeking, which may not fully
+capture the original intent (the experience of losing oneself). Items
+were mapped onto five factors, and the five factors largely aligned with
+Lifton's constructs. Although internal consistency was at least
+acceptable for each factor, goodness of fit statistics are not reported.
+Some studies have used a revised version of the scale by Mathews and
+Kling (1988), who adapted it for a study on prosocial behavior in the
+context of nonprofit volunteer motivation. They reported similar results
+for their revised scale. The items on these scales seem to have more
+face validity than the scale by Drolet, but some factors seem more
+behavioral and unnecessarily specific: pertaining to one's religiosity
+or biological children, whereas Lifton's theory allows for a broader
+interpretation of these dimensions. The Nature and Creative factors seem
+most useful and theoretically aligned with Lifton.
+
+Much more advanced factor analysis methods have been developed since the
+1980s, but to our knowledge, these scales have not been tested with more
+robust tools. The goal of the present research is to develop an
+up-to-date symbolic immortality scale that more directly measures one's
+sense of symbolic immortality and which contains items more generally
+applicable to broad groups of participants (e.g., regardless of a
+person's religious beliefs and parental status). We have attempted to
+use current best practices for scale development and analysis.
+
+\section{Method}\label{method}
 
@@
 
-We used R (Version 4.4.1; \textbf{R-base?}) and the R-packages \emph{papaja} (Version 0.1.2; \textbf{R-papaja?}), and \emph{tinylabels} (Version 0.2.4; \textbf{R-tinylabels?}) for all our analyses.
+\section{Results}\label{results}
 
-\section{Results}\label{results}
+\subsection{Data Screening}\label{data-screening}
+
+\begin{itemize}
+\tightlist
+\item
+  try running with outliers as well --\textgreater{} if differences: then talk
+  about what is going on with the outlier people
+\end{itemize}
+
+\section{Assumptions -------------------------------------------------------------}\label{assumptions--}
+
+\section{Linearity}\label{linearity}
+
+random = rchisq(nrow(noout{[} , 37:97{]}), 7) fake = lm(random\textasciitilde.,
+data=noout{[} , 37:97{]})
+
+standardized = rstudent(fake) \{qqnorm(standardized) abline(0,1)\} \#seems
+okay
+
+\section{Normality}\label{normality}
+
+hist(standardized, breaks=15) \#a little skewed but mostly centered on 0
+and between -2 and 2 so okay
+
+\section{Homog/s}\label{homogs}
+
+fitvalues = scale(fake\$fitted.values) \{plot(fitvalues, standardized)
+abline(0,0) abline(v = 0)\} \#some homogeneity issues but we'll accept it
+
+write.csv(noout, file = ``sona\_data\_screened.csv'', row.names = F)
+library(beepr) beep(sound = 5)
+
+```
 
@@
 \begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-rosseel2012}
-Rosseel, Y. (2012). Lavaan: An r package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(1), 1--36. \url{https://doi.org/10.18637/jss.v048.i02}
+\bibitem[\citeproctext]{ref-aust2022}
+Aust, F., Barth, M., Diedenhofen, B., Stahl, C., Casillas, J.
+V., \& Siegel, R.
+(2022).
+\emph{Papaja: Prepare american psychological association journal articles with r markdown}.
+Retrieved from \url{https://CRAN.R-project.org/package=papaja}
 
-\bibitem[\citeproctext]{ref-dplyr}
-Wickham, H., François, R., Henry, L., Müller, K., \& Vaughan, D. (2023). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+\bibitem[\citeproctext]{ref-burke2010}
+Burke, B.
+L., Martens, A., \& Faucher, E.
+H.
+(2010).
+Two Decades of Terror Management Theory: A Meta-Analysis of Mortality Salience Research.
+\emph{Personality and Social Psychology Review}, \emph{14}(2), 155--195.
+\url{https://doi.org/10.1177/1088868309352321}
+
+\bibitem[\citeproctext]{ref-greenberg1986}
+Greenberg, J., Pyszczynski, T., \& Solomon, S. (1986). \emph{The Causes and Consequences of a Need for Self-Esteem: A Terror Management Theory}. New York: Springer-Verlag.
+
+\bibitem[\citeproctext]{ref-greenberg1990}
+Greenberg, J., Solomon, S., Veeder, M., Pyszczynski, T., Rosenblatt, A., Kirkland, S., \& Lyon, D.
+(1990).
+Evidence for Terror Management Theory II: The Effects of Mortality Salience on Reactions to Those Who Threaten or Bolster the Cultural Worldview.
+\emph{Journal of Personality and Social Psychology}, \emph{58}(2), 308--318.
+
+\bibitem[\citeproctext]{ref-mathews1988}
+Mathews, R.
+C., \& Kling, K.
+J.
+(1988).
+Self-Transcendence, Time Perspective, and Prosocial Behavior.
+\emph{Journal of Voluntary Action Research}, \emph{17}(2), 4--24.
+\url{https://doi.org/10.1177/089976408801700202}
+
+\bibitem[\citeproctext]{ref-mcadams1992}
+McAdams, D.
+P., \& St.
+Aubin, E.
+de.
+(1992).
+A theory of generativity and its assessment through self-report, behavioral acts, and narrative themes in autobiography.
+\emph{Journal of Personality and Social Psychology}, \emph{62}(6), 1003--1015.
 

### 2024-10-04 05_Manuscript/manuscript.Rmd
updating data screening and efa

@@
 they *feel* about these subjects. The scale as a whole had a high
-internal consistency ($\alpha$ = .91) and test-retest reliability
-was *r* = .97. Internal consistency of subscales for the five
-theoretical modes of immortality was mixed. Of the five, spiritual
-immortality was the most distinct from the scale as a whole and the
-other subscales. Factor analysis showed three factors, mapping onto
-biosocial, creative, and spiritual. The transcendent and natural items
-may be closely related to biosocial.
+internal consistency ($\alpha$ = .91) and test-retest reliability was
+*r* = .97. Internal consistency of subscales for the five theoretical
+modes of immortality was mixed. Of the five, spiritual immortality was
+the most distinct from the scale as a whole and the other subscales.
+Factor analysis showed three factors, mapping onto biosocial, creative,
+and spiritual. The transcendent and natural items may be closely related
+to biosocial.
 
@@
 library(mice)
+library(psych)
 
@@
   mutate(where = "sona")
+sona_replaced <- import("../03_Data/sona_data_replaced.csv")
+sona_page1 <- import("../03_Data/sona_page1_sad.csv")
+sona_page2 <- import("../03_Data/sona_page2_sad.csv")
+sona_page3 <- import("../03_Data/sona_page3_sad.csv")
+sona_good <- import("../03_Data/sona_data_goodqual.csv")
+sona_noout <- import("../03_Data/sona_data_noout.csv")
+
 mturk <- import("../03_Data/mturk_data_deidentify.csv") %>% 
   mutate(where = "mturk")
+mturk_replaced <- import("../03_Data/mturk_data_replaced.csv")
+mturk_page1 <- import("../03_Data/mturk_page1_sad.csv")
+mturk_page2 <- import("../03_Data/mturk_page2_sad.csv")
+mturk_page3 <- import("../03_Data/mturk_page3_sad.csv")
+mturk_good <- import("../03_Data/mturk_data_goodqual.csv")
+mturk_noout <- import("../03_Data/mturk_data_noout.csv")
+
 ```
@@
           select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20))
-# everything is within the expected range
-
 apply(sona %>% 
@@
       2, sd, na.rm = TRUE)
-#
+# everything is within the expected range
 
@@
 
-noout = subset(nolowqual, mahal < cutoff)
-#42 participants excluded as outliers
+noout <- subset(nolowqual, mahal < cutoff)
+write.csv(noout, "../03_Data/sona_data_noout.csv", row.names = F)
 ```
 
--   try running with outliers as well --\> if differences: then talk
-    about what is going on with the outlier people
+```{r sona-assumptions, eval = F} 
+random <- rchisq(nrow(sona_good), 7) 
+fake <- lm(random ~ ., data = sona_good %>% 
+             select(Q2_1:Q5_20)  %>% 
+             select(-Q2_21, -Q4_20, -Q5_16))
+standardized <- rstudent(fake)
+fitvalues <- scale(fake$fitted.values)
 
-# Assumptions -------------------------------------------------------------
+# Linearity ----
+{
+  qqnorm(standardized)
+  abline(0,1)
+}
 
-# Linearity
+# Normality -----
+hist(standardized, breaks=15)
 
-random = rchisq(nrow(noout[ , 37:97]), 7) fake = lm(random\~.,
-data=noout[ , 37:97])
+# Homoscedasticity -----
+{
+  plot(fitvalues, standardized)
+  abline(0,0) 
+  abline(v = 0)
+}
 
-standardized = rstudent(fake) {qqnorm(standardized) abline(0,1)} #seems
-okay
+random <- rchisq(nrow(sona_noout), 7) 
+fake <- lm(random ~ ., data = sona_noout %>% 
+             select(Q2_1:Q5_20)  %>% 
+             select(-Q2_21, -Q4_20, -Q5_16))
+standardized <- rstudent(fake)
+fitvalues <- scale(fake$fitted.values)
 
-# Normality
+# Linearity -----
+{
+  qqnorm(standardized)
+  abline(0,1)
+}
 
-hist(standardized, breaks=15) #a little skewed but mostly centered on 0
-and between -2 and 2 so okay
+# Normality -----
+hist(standardized, breaks=15)
 
-# Homog/s
+# Homoscedasticity -----
+{
+  plot(fitvalues, standardized)
+  abline(0,0) 
+  abline(v = 0)
+} 
+```
 
-fitvalues = scale(fake\$fitted.values) {plot(fitvalues, standardized)
-abline(0,0) abline(v = 0)} #some homogeneity issues but we'll accept it
+```{r screen-mturk-accuracy-out, eval = F}
+# Accuracy ----
+summary(mturk %>% 
+          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20))
+apply(mturk %>% 
+          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
+      2, mean, na.rm = TRUE)
+apply(mturk %>% 
+          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
+      2, sd, na.rm = TRUE)
+# everything is within the expected range
 
-write.csv(noout, file = "sona_data_screened.csv", row.names = F)
-library(beepr) beep(sound = 5)
+# Missing ----
 
-\`\`\`
+# rows
+missing <- apply(mturk %>% 
+          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
+          1, 
+          percentmiss) 
+table(missing)
+replacepeople <- subset(mturk, missing <= 5)
+dontpeople <- subset(mturk, missing > 5)
+
+# columns
+missingcol <- apply(replacepeople %>% 
+                      select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
+                    2, 
+                    percentmiss)
+table(missingcol) # all replaceable
+
+replacecolumn <- replacepeople %>% 
+  select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20)
+dontcolumn <- replacepeople %>% 
+  select(-c(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20))
+
+# replacing those with <= 5% missing by multiple imputation
+tempnomiss <- mice(replacecolumn)
+nomiss <- complete(tempnomiss, 1)
+summary(nomiss)
+
+# putting data back together
+# excluding participants with > 5% missing (7 total)
+allcolumns <- cbind(dontcolumn, nomiss)
+summary(allcolumns)
+write.csv(allcolumns, "../03_Data/mturk_data_replaced.csv", row.names = F)
+```
+
+```{r screen-mturk-SAD, eval = F}
+# SAD 
+nomissing <- import("../03_Data/mturk_data_replaced.csv")
+
+# Block 1
+page1 <- SAD(dat = nomissing %>% 
+               select(Q2_1:Q2_21),
+    rt = nomissing$`Q10_Page Submit`,
+    min = 1, 
+    max = 5, 
+    partno = nomissing$ResponseId, 
+    click = nomissing$`Q10_Click Count`, 
+    manvec = nomissing$Q2_21, 
+    mancor = 1, 
+    char = 1626)
+write.csv(page1, "../03_Data/mturk_page1_sad.csv", row.names = F)
+
+# Block 2
+page2 <- SAD(dat = nomissing %>% 
+               select(Q4_1:Q4_20), 
+            rt = nomissing$`Q11_Page Submit`,
+            min = 1, 
+            max = 5, 
+            partno = nomissing$ResponseId, 
+            click = nomissing$`Q11_Click Count`, 
+            manvec = nomissing$Q4_20, 
+            mancor = 4, 
+            char = 1491)
+write.csv(page2, "../03_Data/mturk_page2_sad.csv", row.names = F)
+
+# Block 3
+page3 <- SAD(dat = nomissing %>% 
+               select(Q5_1:Q5_20), 
+            rt = nomissing$`Q12_Page Submit`,
+            min = 1, 
+            max = 5, 
+            partno = nomissing$ResponseId, 
+            click = nomissing$`Q12_Click Count`, 
+            manvec = nomissing$Q5_16, 
+            mancor = 3, 
+            char = 1496)
+write.csv(page3, "../03_Data/mturk_page3_sad.csv", row.names = F)
+
+# Total
+nomissing$totalbad <- page1$badTotal + page2$badTotal + page3$badTotal
+table(nomissing$totalbad) 
+sum(nomissing$totalbad < 15*.4) 
+nrow(nomissing)
+
+nomissing$totalbadUP <- 
+  page1$badChar + page1$badClick + page1$badMC + 
+  page2$badChar + page2$badClick + page2$badMC + 
+  page3$badChar + page3$badClick + page3$badMC
+table(nomissing$totalbadUP)
+sum(nomissing$totalbadUP < 9*.4) 
+# B&S say 2/5 which is 40%, so 40% of the 9 total is 3.6 or 4 or more
+
+nolowqual <- subset(nomissing, totalbadUP < 4)
+write.csv(nolowqual, "../03_Data/mturk_data_goodqual.csv", row.names = F)
+```
+
+```{r mturk-outliers, eval = F}
+nolowqual <- import("../03_Data/mturk_data_goodqual.csv")
+
+mahal <- mahalanobis(nolowqual %>% select(Q2_1:Q5_20),
+                     colMeans(nolowqual %>% select(Q2_1:Q5_20), na.rm = TRUE),
+                     cov(nolowqual %>% select(Q2_1:Q5_20), use="pairwise.complete.obs"))
+
+cutoff <- qchisq(1 - .001,
+                 ncol(nolowqual %>% select(Q2_1:Q5_20)))
+ncol(nolowqual %>% select(Q2_1:Q5_20)) #df 61
+cutoff #cutoff 100.8879
+
+summary(mahal < cutoff)
+
+noout <- subset(nolowqual, mahal < cutoff)
+write.csv(noout, "../03_Data/mturk_data_noout.csv", row.names = F)
+```
+
+```{r mturk-assumptions, eval = F} 
+random <- rchisq(nrow(mturk_good), 7) 
+fake <- lm(random ~ ., data = mturk_good %>% 
+             select(Q2_1:Q5_20)  %>% 
+             select(-Q2_21, -Q4_20, -Q5_16))
+standardized <- rstudent(fake)
+fitvalues <- scale(fake$fitted.values)
+
+# Linearity ----
+{
+  qqnorm(standardized)
+  abline(0,1)
+}
+
+# Normality -----
+hist(standardized, breaks=15)
+
+# Homoscedasticity -----
+{
+  plot(fitvalues, standardized)
+  abline(0,0) 
+  abline(v = 0)
+}
+
+random <- rchisq(nrow(mturk_noout), 7) 
+fake <- lm(random ~ ., data = mturk_noout %>% 
+             select(Q2_1:Q5_20)  %>% 
+             select(-Q2_21, -Q4_20, -Q5_16))
+standardized <- rstudent(fake)
+fitvalues <- scale(fake$fitted.values)
+
+# Linearity -----
+{
+  qqnorm(standardized)
+  abline(0,1)
+}
+
+# Normality -----
+hist(standardized, breaks=15)
+
+# Homoscedasticity -----
+{
+  plot(fitvalues, standardized)
+  abline(0,0) 
+  abline(v = 0)
+} 
+```
+
+```{r data-combine-split}
+combo <- bind_rows(sona_good, mturk_good)
+combo_noout <- bind_rows(sona_noout, mturk_noout)
+
+random_split <- c(
+  sample(sona_good$ResponseId, nrow(sona_good)/2),
+  sample(mturk_good$ResponseId, round(nrow(mturk_good)/2))
+)
+
+efaDF <- combo %>% 
+  filter(ResponseId %in% random_split) %>% 
+  select(Q2_1:Q5_20)  %>% 
+  select(-Q2_21, -Q4_20, -Q5_16)
+cfaDF <- combo %>% 
+  filter(!(ResponseId %in% random_split)) %>% 
+  select(Q2_1:Q5_20)  %>% 
+  select(-Q2_21, -Q4_20, -Q5_16)
+
+nrow(efaDF)
+nrow(cfaDF)
+
+efaDF_noout <- combo_noout %>% 
+  filter(ResponseId %in% random_split) %>% 
+  select(Q2_1:Q5_20)  %>% 
+  select(-Q2_21, -Q4_20, -Q5_16)
+cfaDF_noout <- combo_noout %>% 
+  filter(!(ResponseId %in% random_split)) %>% 
+  select(Q2_1:Q5_20)  %>% 
+  select(-Q2_21, -Q4_20, -Q5_16)
+
+nrow(efaDF_noout)
+nrow(cfaDF_noout)
+```
+
+## EFA
+
+### Number of Factors
+
+```{r}
+number_items <- fa.parallel(efaDF, #data frame
+                            fm="ml", #math
+                            fa="fa") #only efa
+sum(number_items$fa.values > 1)
+sum(number_items$fa.values > .7)
+```
+
+### Simple Structure
+
+```{r}
+EFA_fit <- fa(efaDF, #data
+              nfactors = 2, #number of factors
+              rotate = "oblimin", #rotation
+              fm = "ml") #math
+
+EFA_fit
+
+efa_loadings <- as.data.frame(unclass(EFA_fit$loadings)) %>% 
+  mutate(keep = ifelse(
+    ML1 >= .30, "yes", ifelse(
+      ML2 >= .30, "yes", ifelse(
+        ML1 >= .30 & ML2 >= .30, "no", "no"
+      )
+    )
+  )) %>% 
+  mutate(question = rownames(.))
+
+EFA_fit_2 <- fa(efaDF %>% 
+                  select(efa_loadings %>% 
+                           filter(keep == "yes") %>% 
+                           pull(question)), #data
+              nfactors = 2, #number of factors
+              rotate = "oblimin", #rotation
+              fm = "ml") #math
+
+EFA_fit_2
+
+efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
+  mutate(keep = ifelse(
+    ML1 >= .30, "yes", ifelse(
+      ML2 >= .30, "yes", ifelse(
+        ML1 >= .30 & ML2 >= .30, "no", "no"
+      )
+    )
+  )) %>% 
+  mutate(question = rownames(.))
+```
+
+```{r}
+EFA_fit <- fa(efaDF, #data
+              nfactors = 3, #number of factors
+              rotate = "oblimin", #rotation
+              fm = "ml") #math
+
+EFA_fit
+
+efa_loadings <- as.data.frame(unclass(EFA_fit$loadings)) %>% 
+  mutate(keep = ifelse(
+    ML1 >= .30, "yes", ifelse(
+      ML2 >= .30, "yes", ifelse(
+        ML3 >= .30, "yes", "no"
+        )
+      )
+    )
+  ) %>% 
+  mutate(question = rownames(.)) %>% 
+  mutate(
+    keep = ifelse(
+          (ML1 >= .30 & ML2 >= .30) | 
+            (ML1 >= .30 & ML3 >= .30) |
+            (ML3 >= .30 & ML2 >= .30), "no", keep
+          )
+  )
+
+EFA_fit_2 <- fa(efaDF %>% 
+                  select(efa_loadings %>% 
+                           filter(keep == "yes") %>% 
+                           pull(question)), #data
+              nfactors = 3, #number of factors
+              rotate = "oblimin", #rotation
+              fm = "ml") #math
+
+EFA_fit_2
+
+efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
+  mutate(keep = ifelse(
+    ML1 >= .30, "yes", ifelse(
+      ML2 >= .30, "yes", ifelse(
+        ML3 >= .30, "yes", "no"
+        )
+      )
+    )
+  ) %>% 
+  mutate(question = rownames(.)) %>% 
+  mutate(
+    keep = ifelse(
+          (ML1 >= .30 & ML2 >= .30) | 
+            (ML1 >= .30 & ML3 >= .30) |
+            (ML3 >= .30 & ML2 >= .30), "no", keep
+          )
+  )
+```
 

### 2024-10-04 05_Manuscript/manuscript.Rmd
adding trackdown

@@
 
+```{r trackdown, eval = F}
+library(trackdown)
+# upload_file(
+#   file = "manuscript.Rmd",
+#   gfile = "gen_scale_manuscript_trackdown",
+#   gpath = "gen_scale/",
+#   hide_code = TRUE
+# )
+
+# pull to me 
+download_file(
+  file = "manuscript.Rmd",
+  gfile = "gen_scale_manuscript_trackdown",
+  gpath = "gen_scale/",
+  hide_code = TRUE
+)
+
+# push to google
+update_file(
+  file = "manuscript.Rmd",
+  gfile = "gen_scale_manuscript_trackdown",
+  gpath = "gen_scale/",
+  hide_code = TRUE
+)
+```
+
 Death is something each of us must learn to cope with, whether in
@@
 
+also do five
+
 ```{r}
@@
 
+# remember you gotta fix this because of the order of operations 
 efa_loadings <- as.data.frame(unclass(EFA_fit$loadings)) %>% 
@@
 
+```{r}
+EFA_fit <- fa(efaDF, #data
+              nfactors = 5, #number of factors
+              rotate = "oblimin", #rotation
+              fm = "ml") #math
+
+EFA_fit
+
+efa_loadings <- as.data.frame(unclass(EFA_fit$loadings)) %>% 
+  mutate(question = rownames(.)) %>% 
+  rowwise() %>%
+  mutate(keep = sum(c_across(-question) >= .30)) %>% 
+  ungroup()
+
+EFA_fit_2 <- fa(efaDF %>% 
+                  select(efa_loadings %>% 
+                           filter(keep == 1) %>% 
+                           pull(question)), #data
+              nfactors = 5, #number of factors
+              rotate = "oblimin", #rotation
+              fm = "ml") #math
+
+EFA_fit_2
+
+efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
+  mutate(question = rownames(.)) %>% 
+  rowwise() %>%
+  mutate(keep = sum(c_across(-question) >= .30)) %>% 
+  ungroup()
+
+EFA_fit_3 <- fa(efaDF %>% 
+                  select(efa_loadings_2 %>% 
+                           filter(keep == 1) %>% 
+                           pull(question)), #data
+              nfactors = 5, #number of factors
+              rotate = "oblimin", #rotation
+              fm = "ml") #math
+
+EFA_fit_3
+
+efa_loadings_3 <- as.data.frame(unclass(EFA_fit_3$loadings)) %>% 
+  mutate(question = rownames(.)) %>% 
+  rowwise() %>%
+  mutate(keep = sum(c_across(-question) >= .30)) %>% 
+  ungroup()
+
+```
+
+- take the final version of each "best model" 
+- get down to 5 items each or whatever is left (best loading and theoretical)
+- look at the fit indices to tell which may be best
+
 # Discussion

### 2024-10-06 05_Manuscript/manuscript.Rmd
fixed citations (some errors?)

@@
 death and the anxiety this awareness often causes. Psychoanalyst Erik
-Erikson (1950) proposed that during mid-life one becomes acutely aware
-of their oncoming death and is motivated to care for things which will
-outlast themselves. He called this act of caring generativity. In *The
-Denial of Death*, philosopher Ernest Becker (1973) posits that humans
-undertake immortality projects to curb their sense of vulnerability to
-death. Similarly, psychiatrist Robert Jay Lifton (1979), a mentee of
-Erikson, described the awareness of death as being ever present and
-motivating us to create symbols, thereby allowing us to imagine
-ourselves as symbolically immortalized. Existential psychiatrist Irvin
-Yalom (2008) notes that many of his clients experiencing anxiety about
-their death take comfort in “rippling,” the idea that one’s lasting
-effects on the world will ripple out and influence the world after they
-have died.
+Erikson [-@erikson1950] proposed that during mid-life one becomes
+acutely aware of their oncoming death and is motivated to care for
+things which will outlast themselves. He called this act of caring
+generativity. In *The Denial of Death*, philosopher Ernest Becker
+[-@becker1973] posits that humans undertake immortality projects to curb
+their sense of vulnerability to death. Similarly, psychiatrist Robert
+Jay Lifton [-@lifton1979], a mentee of Erikson, described the awareness
+of death as being ever present and motivating us to create symbols,
+thereby allowing us to imagine ourselves as symbolically immortalized.
+Existential psychiatrist Irvin Yalom [-@yalom2008] notes that many of
+his clients experiencing anxiety about their death take comfort in
+“rippling,” the idea that one’s lasting effects on the world will ripple
+out and influence the world after they have died.
 
@@
 One of these bodies of thought, called symbolic immortality, was
-originally theorized by Lifton (1979), who thought that awareness of
-death drives a fundamental human desire for a sense of continuity
-lasting beyond the lifespan. Essentially, humans are meaning-seeking
-creatures, and throughout our lives, this search for meaning involves an
-evolving psychological imagery of life and death. Death, or the
-transient nature of life, threatens our search for meaning. Lifton
-thought that if we could achieve what we believe to be some form of
-immortality, we could overcome this loss of meaning, and the awareness
-of death could instead drive an inner vitality (imagery associated with
-connection, integrity, and movement). If this drive toward vitality is
-lost, we are vulnerable to a psychic numbness or death-in-life (imagery
-associated with separation, disintegration, and stasis). In Lifton's own
-words, "Death does indeed bring about biological and psychic
-annihilation. But life includes symbolic perceptions of connections that
-precede and outlast that annihilation" (1979, p. 18).
-
-Lifton (1979) proposed five modes of experience or ways of achieving
-symbolic immortality: The biological (or biosocial) mode in which one
-lives on through their genetic and sociocultural progeny, the creative
-mode in which one’s accomplishments and contribution outlast oneself,
-the natural mode in which one feels they are a part of the broader
-universe, the spiritual mode in which one seeks to transcend the
+originally theorized by Lifton [-@lifton1979], who thought that
+awareness of death drives a fundamental human desire for a sense of
+continuity lasting beyond the lifespan. Essentially, humans are
+meaning-seeking creatures, and throughout our lives, this search for
+meaning involves an evolving psychological imagery of life and death.
+Death, or the transient nature of life, threatens our search for
+meaning. Lifton thought that if we could achieve what we believe to be
+some form of immortality, we could overcome this loss of meaning, and
+the awareness of death could instead drive an inner vitality (imagery
+associated with connection, integrity, and movement). If this drive
+toward vitality is lost, we are vulnerable to a psychic numbness or
+death-in-life (imagery associated with separation, disintegration, and
+stasis). In Lifton's own words, "Death does indeed bring about
+biological and psychic annihilation. But life includes symbolic
+perceptions of connections that precede and outlast that annihilation"
+[-@lifton1979, p. 18].
+
+Lifton [-@lifton1979] proposed five modes of experience or ways of
+achieving symbolic immortality: The biological (or biosocial) mode in
+which one lives on through their genetic and sociocultural progeny, the
+creative mode in which one’s accomplishments and contribution outlast
+oneself, the natural mode in which one feels they are a part of the
+broader universe, the spiritual mode in which one seeks to transcend the
 physical realm to a higher spiritual realm beyond death, and the mode of
@@
 underlying motive for what Erikson referred to as generativity.
-Generativity is the seventh of eight proposed stages in Erikson's (1950)
-theory of psychosocial development, which he associated with midlife and
-described as "the concern in establishing and guiding the next
-generation" (Erikson, 1963, p. 267). Little systematic research was
-conducted on this subject until the 1980's. Kotre (1984) expanded on the
-theory and proposed that the drive for generativity was related to a
-motive to expand the sense of self beyond the lifetime, especially in
-light of the fear of death.
+Generativity is the seventh of eight proposed stages in Erikson's
+[-@erikson1950] theory of psychosocial development, which he associated
+with midlife and described as "the concern in establishing and guiding
+the next generation" [@erikson1963, p. 267]. Little systematic research
+was conducted on this subject until the 1980's. Kotre [-@kotre1984]
+expanded on the theory and proposed that the drive for generativity was
+related to a motive to expand the sense of self beyond the lifetime,
+especially in light of the fear of death.
 
@@
 systematically and quantitatively assess this construct. Two attempts
-have been made to develop such a measurement: Drolet's (1990) Sense of
-Symbolic Immortality Scale and Mathews and Kling (1988) measure of
-symbolic immortality, based on an original questionnaire by Mathews and
-Mister (1987).
-
-Drolet (1990) developed the Sense of Symbolic Immortality Scale based on
-Robert J. Lifton’s theory of symbolic immortality and its five modes of
-experience. Drolet studied 136 adults, ages 18-30 and 30-40, and
-hypothesized that those in their 30's (established adults) would have a
-greater sense of symbolic immortality than the young adults (18-30). The
-measure is inherently subjective, not only by the nature of self-report,
-but in that the scale seeks to measure what a person *believes* and how
-they *feel* about these subjects. The scale as a whole had a high
-internal consistency ($\alpha$ = .91) and test-retest reliability was
-*r* = .97. Internal consistency of subscales for the five theoretical
-modes of immortality was mixed. Of the five, spiritual immortality was
-the most distinct from the scale as a whole and the other subscales.
-Factor analysis showed three factors, mapping onto biosocial, creative,
-and spiritual. The transcendent and natural items may be closely related
-to biosocial.
-
-Moving beyond the scale development itself (still Drolet 1990), SSI
-correlated negatively with death anxiety (Templer's Death Anxiety Scale)
-and had a strong (*r* = .84) positive relationship with purpose in life
-(Maholick's Purpose in Life Test). In interpreting the very strong
-correlation, the author suggests that SSI is a broader construct than
-Purpose in Life and the scale itself may be less prone to social
-desirability effects than the PIL, although this had not been directly
-tested. Age group was also related, with established adults having a
-higher SSI, particularly in the biosocial and creative domains.
+have been made to develop such a measurement: Drolet's [-@drolet1990]
+Sense of Symbolic Immortality Scale and Mathews and Kling's
+[-@mathews1988] measure of symbolic immortality, based on an original
+questionnaire by Mathews and Mister [-@mathews1987].
+
+Drolet [-@drolet1990] developed the Sense of Symbolic Immortality Scale
+based on Robert J. Lifton’s theory of symbolic immortality and its five
+modes of experience. Drolet studied 136 adults, ages 18-30 and 30-40,
+and hypothesized that those in their 30's (established adults) would
+have a greater sense of symbolic immortality than the young adults
+(18-30). The measure is inherently subjective, not only by the nature of
+self-report, but in that the scale seeks to measure what a person
+*believes* and how they *feel* about these subjects. The scale as a
+whole had a high internal consistency ($\alpha$ = .91) and test-retest
+reliability was *r* = .97. Internal consistency of subscales for the
+five theoretical modes of immortality was mixed. Of the five, spiritual
+immortality was the most distinct from the scale as a whole and the
+other subscales. Factor analysis showed three factors, mapping onto
+biosocial, creative, and spiritual. The transcendent and natural items
+may be closely related to biosocial.
+
+Moving beyond the scale development itself, SSI correlated negatively
+with Templer's Death Anxiety Scale and had a strong (*r* = .84) positive
+relationship with Maholick's Purpose in Life Test [@drolet1990]. In
+interpreting the very strong correlation, the author suggests that SSI
+is a broader construct than Purpose in Life and the scale itself may be
+less prone to social desirability effects than the PIL, although this
+had not been directly tested. Age group was also related, with
+established adults having a higher SSI, particularly in the biosocial
+and creative domains.
 
@@
 
-Mathews and Mister (1987) also developed a scale pertaining to symbolic
-immortality, sensation seeking, and psychic numbness in a study
+Mathews and Mister [-@mathews1987] also developed a scale pertaining to
+symbolic immortality, sensation seeking, and psychic numbness in a study
 including 400 adults. Experiential transcendence was operationalized as
-something like Zuckerman's (1979) sensation seeking, which may not fully
-capture the original intent (the experience of losing oneself). Items
-were mapped onto five factors, and the five factors largely aligned with
-Lifton's constructs. Although internal consistency was at least
-acceptable for each factor, goodness of fit statistics are not reported.
-Some studies have used a revised version of the scale by Mathews and
-Kling (1988), who adapted it for a study on prosocial behavior in the
-context of nonprofit volunteer motivation. They reported similar results
-for their revised scale. The items on these scales seem to have more
-face validity than the scale by Drolet, but some factors seem more
-behavioral and unnecessarily specific: pertaining to one's religiosity
-or biological children, whereas Lifton's theory allows for a broader
-interpretation of these dimensions. The Nature and Creative factors seem
-most useful and theoretically aligned with Lifton.
+similar to Zuckerman's [-@zuckerman1979] sensation seeking, which may
+not fully capture the original intent (the experience of losing
+oneself). Items were mapped onto five factors, and the five factors
+largely aligned with Lifton's constructs. Although internal consistency
+was at least acceptable for each factor, goodness of fit statistics are
+not reported. Some studies have used a revised version of the scale by
+Mathews and Kling [-@mathews1988], who adapted it for a study on
+prosocial behavior in the context of nonprofit volunteer motivation.
+They reported similar results for their revised scale. The items on
+these scales seem to have more face validity than the scale by Drolet,
+but some factors seem more behavioral and unnecessarily specific:
+pertaining to one's religiosity or biological children, whereas Lifton's
+theory allows for a broader interpretation of these dimensions. The
+Nature and Creative factors seem most useful and theoretically aligned
+with Lifton.
 
@@
 -   take the final version of each "best model"
-- get down to 5 items each or whatever is left (best loading and theoretical)
+-   get down to 5 items each or whatever is left (best loading and
+    theoretical)
 -   look at the fit indices to tell which may be best

### 2024-10-06 05_Manuscript/manuscript.tex
fixed citations (some errors?)

@@
 \makeatletter
-\newsavebox\pandoc@box
-\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
-  \sbox\pandoc@box{#1}%
-  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
-  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
-  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
-  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
-  \else\usebox{\pandoc@box}%
-  \fi%
-}
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 % Set default figure placement to htbp
+\makeatletter
 \def\fps@figure{htbp}
@@
 \def\languageshorthands#1{}
-\ifLuaTeX
-  \usepackage[english]{selnolig} % disable illegal ligatures
-\fi
 % Manuscript styling
@@
 \usepackage{csquotes}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 \usepackage{bookmark}
@@
 death and the anxiety this awareness often causes. Psychoanalyst Erik
-Erikson (1950) proposed that during mid-life one becomes acutely aware
-of their oncoming death and is motivated to care for things which will
-outlast themselves. He called this act of caring generativity. In \emph{The
-Denial of Death}, philosopher Ernest Becker (1973) posits that humans
-undertake immortality projects to curb their sense of vulnerability to
-death. Similarly, psychiatrist Robert Jay Lifton (1979), a mentee of
-Erikson, described the awareness of death as being ever present and
-motivating us to create symbols, thereby allowing us to imagine
-ourselves as symbolically immortalized. Existential psychiatrist Irvin
-Yalom (2008) notes that many of his clients experiencing anxiety about
-their death take comfort in ``rippling,'' the idea that one's lasting
-effects on the world will ripple out and influence the world after they
-have died.
+Erikson (1950) proposed that during mid-life one becomes
+acutely aware of their oncoming death and is motivated to care for
+things which will outlast themselves. He called this act of caring
+generativity. In \emph{The Denial of Death}, philosopher Ernest Becker
+(\textbf{becker1973?}) posits that humans undertake immortality projects to curb
+their sense of vulnerability to death. Similarly, psychiatrist Robert
+Jay Lifton (\textbf{lifton1979?}), a mentee of Erikson, described the awareness
+of death as being ever present and motivating us to create symbols,
+thereby allowing us to imagine ourselves as symbolically immortalized.
+Existential psychiatrist Irvin Yalom (\textbf{yalom2008?}) notes that many of
+his clients experiencing anxiety about their death take comfort in
+``rippling,'' the idea that one's lasting effects on the world will ripple
+out and influence the world after they have died.
 
@@
 One of these bodies of thought, called symbolic immortality, was
-originally theorized by Lifton (1979), who thought that awareness of
-death drives a fundamental human desire for a sense of continuity
-lasting beyond the lifespan. Essentially, humans are meaning-seeking
-creatures, and throughout our lives, this search for meaning involves an
-evolving psychological imagery of life and death. Death, or the
-transient nature of life, threatens our search for meaning. Lifton
-thought that if we could achieve what we believe to be some form of
-immortality, we could overcome this loss of meaning, and the awareness
-of death could instead drive an inner vitality (imagery associated with
-connection, integrity, and movement). If this drive toward vitality is
-lost, we are vulnerable to a psychic numbness or death-in-life (imagery
-associated with separation, disintegration, and stasis). In Lifton's own
-words, ``Death does indeed bring about biological and psychic
-annihilation. But life includes symbolic perceptions of connections that
-precede and outlast that annihilation'' (1979, p.~18).
+originally theorized by Lifton (\textbf{lifton1979?}), who thought that
+awareness of death drives a fundamental human desire for a sense of
+continuity lasting beyond the lifespan. Essentially, humans are
+meaning-seeking creatures, and throughout our lives, this search for
+meaning involves an evolving psychological imagery of life and death.
+Death, or the transient nature of life, threatens our search for
+meaning. Lifton thought that if we could achieve what we believe to be
+some form of immortality, we could overcome this loss of meaning, and
+the awareness of death could instead drive an inner vitality (imagery
+associated with connection, integrity, and movement). If this drive
+toward vitality is lost, we are vulnerable to a psychic numbness or
+death-in-life (imagery associated with separation, disintegration, and
+stasis). In Lifton's own words, ``Death does indeed bring about
+biological and psychic annihilation. But life includes symbolic
+perceptions of connections that precede and outlast that annihilation''
+(\textbf{lifton1979?}).
 
-Lifton (1979) proposed five modes of experience or ways of achieving
-symbolic immortality: The biological (or biosocial) mode in which one
-lives on through their genetic and sociocultural progeny, the creative
-mode in which one's accomplishments and contribution outlast oneself,
-the natural mode in which one feels they are a part of the broader
-universe, the spiritual mode in which one seeks to transcend the
+Lifton (\textbf{lifton1979?}) proposed five modes of experience or ways of
+achieving symbolic immortality: The biological (or biosocial) mode in
+which one lives on through their genetic and sociocultural progeny, the
+creative mode in which one's accomplishments and contribution outlast
+oneself, the natural mode in which one feels they are a part of the
+broader universe, the spiritual mode in which one seeks to transcend the
 physical realm to a higher spiritual realm beyond death, and the mode of
@@
 underlying motive for what Erikson referred to as generativity.
-Generativity is the seventh of eight proposed stages in Erikson's (1950)
-theory of psychosocial development, which he associated with midlife and
-described as ``the concern in establishing and guiding the next
-generation'' (Erikson, 1963, p.~267). Little systematic research was
-conducted on this subject until the 1980's. Kotre (1984) expanded on the
-theory and proposed that the drive for generativity was related to a
-motive to expand the sense of self beyond the lifetime, especially in
-light of the fear of death.
+Generativity is the seventh of eight proposed stages in Erikson's
+(1950) theory of psychosocial development, which he associated
+with midlife and described as ``the concern in establishing and guiding
+the next generation'' (E. H. Erikson, 1963, p. 267). Little systematic research
+was conducted on this subject until the 1980's. Kotre (1984)
+expanded on the theory and proposed that the drive for generativity was
+related to a motive to expand the sense of self beyond the lifetime,
+especially in light of the fear of death.
 
@@
 behind products that will outlive one's physical existence,'' a theme
-clearly related to both Lifton's and Erikson's theories (Aust et al., 2022; McAdams \& St. Aubin, 1992, p. 1011).
-
-(Aust et al., 2022; Mathews \& Kling, 1988)
-
-(McAdams \& de St.~Aubin, 1992, p.~1011).
+clearly related to both Lifton's and Erikson's theories (McAdams \& St. Aubin, 1992, p. 1011).
 
@@
 systematically and quantitatively assess this construct. Two attempts
-have been made to develop such a measurement: Drolet's (1990) Sense of
-Symbolic Immortality Scale and Mathews and Kling (1988) measure of
-symbolic immortality, based on an original questionnaire by Mathews and
-Mister (1987).
+have been made to develop such a measurement: Drolet's (1990)
+Sense of Symbolic Immortality Scale and Mathews and Kling's
+(1988) measure of symbolic immortality, based on an original
+questionnaire by Mathews and Mister (1987).
 
-Drolet (1990) developed the Sense of Symbolic Immortality Scale based on
-Robert J. Lifton's theory of symbolic immortality and its five modes of
-experience. Drolet studied 136 adults, ages 18-30 and 30-40, and
-hypothesized that those in their 30's (established adults) would have a
-greater sense of symbolic immortality than the young adults (18-30). The
-measure is inherently subjective, not only by the nature of self-report,
-but in that the scale seeks to measure what a person \emph{believes} and how
-they \emph{feel} about these subjects. The scale as a whole had a high
-internal consistency (\emph{\$\textbackslash alpha\$} = .91) and test-retest reliability
-was \emph{r} = .97. Internal consistency of subscales for the five
-theoretical modes of immortality was mixed. Of the five, spiritual
+Drolet (1990) developed the Sense of Symbolic Immortality Scale
+based on Robert J. Lifton's theory of symbolic immortality and its five
+modes of experience. Drolet studied 136 adults, ages 18-30 and 30-40,
+and hypothesized that those in their 30's (established adults) would
+have a greater sense of symbolic immortality than the young adults
+(18-30). The measure is inherently subjective, not only by the nature of
+self-report, but in that the scale seeks to measure what a person
+\emph{believes} and how they \emph{feel} about these subjects. The scale as a
+whole had a high internal consistency (\(\alpha\) = .91) and test-retest
+reliability was \emph{r} = .97. Internal consistency of subscales for the
+five theoretical modes of immortality was mixed. Of the five, spiritual
 immortality was the most distinct from the scale as a whole and the
@@
 
-Moving beyond the scale development itself (still Drolet 1990), SSI
-correlated negatively with death anxiety (Templer's Death Anxiety Scale)
-and had a strong (\emph{r} = .84) positive relationship with purpose in life
-(Maholick's Purpose in Life Test). In interpreting the very strong
-correlation, the author suggests that SSI is a broader construct than
-Purpose in Life and the scale itself may be less prone to social
-desirability effects than the PIL, although this had not been directly
-tested. Age group was also related, with established adults having a
-higher SSI, particularly in the biosocial and creative domains.
+Moving beyond the scale development itself, SSI correlated negatively
+with Templer's Death Anxiety Scale and had a strong (\emph{r} = .84) positive
+relationship with Maholick's Purpose in Life Test (Drolet, 1990). In
+interpreting the very strong correlation, the author suggests that SSI
+is a broader construct than Purpose in Life and the scale itself may be
+less prone to social desirability effects than the PIL, although this
+had not been directly tested. Age group was also related, with
+established adults having a higher SSI, particularly in the biosocial
+and creative domains.
 
@@
 
-Mathews and Mister (1987) also developed a scale pertaining to symbolic
-immortality, sensation seeking, and psychic numbness in a study
+Mathews and Mister (1987) also developed a scale pertaining to
+symbolic immortality, sensation seeking, and psychic numbness in a study
 including 400 adults. Experiential transcendence was operationalized as
-something like Zuckerman's (1979) sensation seeking, which may not fully
-capture the original intent (the experience of losing oneself). Items
-were mapped onto five factors, and the five factors largely aligned with
-Lifton's constructs. Although internal consistency was at least
-acceptable for each factor, goodness of fit statistics are not reported.
-Some studies have used a revised version of the scale by Mathews and
-Kling (1988), who adapted it for a study on prosocial behavior in the
-context of nonprofit volunteer motivation. They reported similar results
-for their revised scale. The items on these scales seem to have more
-face validity than the scale by Drolet, but some factors seem more
-behavioral and unnecessarily specific: pertaining to one's religiosity
-or biological children, whereas Lifton's theory allows for a broader
-interpretation of these dimensions. The Nature and Creative factors seem
-most useful and theoretically aligned with Lifton.
+similar to Zuckerman's (1979) sensation seeking, which may
+not fully capture the original intent (the experience of losing
+oneself). Items were mapped onto five factors, and the five factors
+largely aligned with Lifton's constructs. Although internal consistency
+was at least acceptable for each factor, goodness of fit statistics are
+not reported. Some studies have used a revised version of the scale by
+Mathews and Kling (1988), who adapted it for a study on
+prosocial behavior in the context of nonprofit volunteer motivation.
+They reported similar results for their revised scale. The items on
+these scales seem to have more face validity than the scale by Drolet,
+but some factors seem more behavioral and unnecessarily specific:
+pertaining to one's religiosity or biological children, whereas Lifton's
+theory allows for a broader interpretation of these dimensions. The
+Nature and Creative factors seem most useful and theoretically aligned
+with Lifton.
 
@@
 
+\begin{verbatim}
+## [1] 352
+\end{verbatim}
+
+\begin{verbatim}
+## [1] 353
+\end{verbatim}
+
+\begin{verbatim}
+## [1] 326
+\end{verbatim}
+
+\begin{verbatim}
+## [1] 326
+\end{verbatim}
+
+\subsection{EFA}\label{efa}
+
+\subsubsection{Number of Factors}\label{number-of-factors}
+
+also do five
+
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-1-1.pdf}
+
+\begin{verbatim}
+## Parallel analysis suggests that the number of factors =  7  and the number of components =  NA
+\end{verbatim}
+
+\begin{verbatim}
+## [1] 5
+\end{verbatim}
+
+\begin{verbatim}
+## [1] 7
+\end{verbatim}
+
+\subsubsection{Simple Structure}\label{simple-structure}
+
+\begin{verbatim}
+## Factor Analysis using method =  ml
+## Call: fa(r = efaDF, nfactors = 2, rotate = "oblimin", fm = "ml")
+## Standardized loadings (pattern matrix) based upon correlation matrix
+##         ML1   ML2    h2   u2 com
+## Q2_1   0.57  0.15 0.436 0.56 1.1
+## Q2_2   0.77 -0.05 0.552 0.45 1.0
+## Q2_3   0.76 -0.08 0.528 0.47 1.0
+## Q2_4   0.70  0.05 0.523 0.48 1.0
+## Q2_5   0.73 -0.10 0.466 0.53 1.0
+## Q2_6   0.72  0.06 0.561 0.44 1.0
+## Q2_7   0.47  0.07 0.259 0.74 1.0
+## Q2_8   0.65 -0.03 0.408 0.59 1.0
+## Q2_9   0.63  0.01 0.405 0.60 1.0
+## Q2_10  0.58 -0.05 0.308 0.69 1.0
+## Q2_11  0.18  0.64 0.546 0.45 1.2
+## Q2_12 -0.05  0.92 0.805 0.19 1.0
+## Q2_13  0.11  0.18 0.066 0.93 1.6
+## Q2_14  0.66  0.06 0.480 0.52 1.0
+## Q2_15  0.68 -0.08 0.421 0.58 1.0
+## Q2_16  0.79 -0.08 0.571 0.43 1.0
+## Q2_17 -0.01  0.92 0.836 0.16 1.0
+## Q2_18  0.14  0.75 0.686 0.31 1.1
+## Q2_19  0.46  0.12 0.286 0.71 1.1
+## Q2_20  0.64 -0.11 0.354 0.65 1.1
+## Q4_1   0.71 -0.06 0.468 0.53 1.0
+## Q4_2   0.60 -0.05 0.328 0.67 1.0
+## Q4_3   0.60 -0.06 0.335 0.66 1.0
+## Q4_4   0.52  0.13 0.351 0.65 1.1
+## Q4_5   0.67 -0.06 0.410 0.59 1.0
+## Q4_6   0.52  0.19 0.411 0.59 1.3
+## Q4_7   0.31 -0.13 0.073 0.93 1.3
+## Q4_8   0.34  0.07 0.148 0.85 1.1
+## Q4_9   0.65  0.15 0.533 0.47 1.1
+## Q4_10  0.68  0.03 0.481 0.52 1.0
+## Q4_11  0.09  0.14 0.042 0.96 1.7
+## Q4_12  0.40 -0.04 0.146 0.85 1.0
+## Q4_13  0.23  0.38 0.286 0.71 1.7
+## Q4_14  0.17  0.46 0.317 0.68 1.3
+## Q4_15  0.63  0.04 0.421 0.58 1.0
+## Q4_16  0.55  0.01 0.312 0.69 1.0
+## Q4_17  0.12  0.51 0.336 0.66 1.1
+## Q4_18  0.10  0.19 0.064 0.94 1.5
+## Q4_19 -0.07  0.95 0.834 0.17 1.0
+## Q5_1   0.07  0.78 0.670 0.33 1.0
+## Q5_2   0.02  0.85 0.740 0.26 1.0
+## Q5_3   0.09  0.50 0.305 0.70 1.1
+## Q5_4   0.51  0.25 0.446 0.55 1.5
+## Q5_5   0.14  0.00 0.021 0.98 1.0
+## Q5_6   0.44  0.16 0.290 0.71 1.3
+## Q5_7   0.59 -0.01 0.338 0.66 1.0
+## Q5_8   0.68  0.04 0.491 0.51 1.0
+## Q5_9   0.75 -0.03 0.547 0.45 1.0
+## Q5_10 -0.06  0.85 0.669 0.33 1.0
+## Q5_11 -0.02  0.15 0.020 0.98 1.0
+## Q5_12  0.05  0.30 0.107 0.89 1.1
+## Q5_13  0.74  0.04 0.574 0.43 1.0
+## Q5_14  0.31 -0.04 0.085 0.91 1.0
+## Q5_15  0.57  0.09 0.387 0.61 1.1
+## Q5_17  0.49  0.15 0.334 0.67 1.2
+## Q5_18  0.35  0.20 0.232 0.77 1.6
+## Q5_19  0.52  0.25 0.466 0.53 1.4
+## Q5_20  0.19 -0.06 0.029 0.97 1.2
+## 
+##                         ML1  ML2
+## SS loadings           14.91 7.63
+## Proportion Var         0.26 0.13
+## Cumulative Var         0.26 0.39
+## Proportion Explained   0.66 0.34
+## Cumulative Proportion  0.66 1.00
+## 
+##  With factor correlations of 
+##      ML1  ML2
+## ML1 1.00 0.49
+## ML2 0.49 1.00
+## 
+## Mean item complexity =  1.1
+## Test of the hypothesis that 2 factors are sufficient.
+## 
+## df null model =  1653  with the objective function =  38.9 with Chi Square =  12870.73
+## df of  the model are 1538  and the objective function was  12.63 
+## 
+## The root mean square of the residuals (RMSR) is  0.07 
+## The df corrected root mean square of the residuals is  0.07 
+## 
+## The harmonic n.obs is  352 with the empirical chi square  5082.08  with prob <  0 
+## The total n.obs was  352  with Likelihood Chi Square =  4161.82  with prob <  4.3e-240 
+## 
+## Tucker Lewis Index of factoring reliability =  0.747
+## RMSEA index =  0.07  and the 90 % confidence intervals are  0.067 0.072
+## BIC =  -4856.44
+## Fit based upon off diagonal values = 0.96
+## Measures of factor score adequacy             
+##                                                    ML1  ML2
+## Correlation of (regression) scores with factors   0.98 0.98
+## Multiple R square of scores with factors          0.96 0.96
+## Minimum correlation of possible factor scores     0.93 0.93
+\end{verbatim}
+
+\begin{verbatim}
+## Factor Analysis using method =  ml
+## Call: fa(r = efaDF %>% select(efa_loadings %>% filter(keep == "yes") %>% 
+##     pull(question)), nfactors = 2, rotate = "oblimin", fm = "ml")
+## Standardized loadings (pattern matrix) based upon correlation matrix
+##         ML1   ML2    h2   u2 com
+## Q2_1   0.57  0.15 0.435 0.56 1.1
+## Q2_2   0.77 -0.06 0.551 0.45 1.0
+## Q2_3   0.76 -0.08 0.529 0.47 1.0
+## Q2_4   0.69  0.06 0.525 0.47 1.0
+## Q2_5   0.73 -0.10 0.467 0.53 1.0
+## Q2_6   0.72  0.06 0.561 0.44 1.0
+## Q2_7   0.47  0.07 0.260 0.74 1.0
+## Q2_8   0.65 -0.02 0.408 0.59 1.0
+## Q2_9   0.63  0.01 0.406 0.59 1.0
+## Q2_10  0.58 -0.05 0.306 0.69 1.0
+## Q2_11  0.18  0.64 0.545 0.45 1.2
+## Q2_12 -0.05  0.92 0.805 0.20 1.0
+## Q2_14  0.66  0.05 0.477 0.52 1.0
+## Q2_15  0.68 -0.08 0.422 0.58 1.0
+## Q2_16  0.79 -0.08 0.572 0.43 1.0
+## Q2_17 -0.01  0.92 0.837 0.16 1.0
+## Q2_18  0.14  0.75 0.686 0.31 1.1
+## Q2_19  0.46  0.13 0.287 0.71 1.1
+## Q2_20  0.64 -0.10 0.353 0.65 1.0
+## Q4_1   0.71 -0.06 0.469 0.53 1.0
+## Q4_2   0.60 -0.06 0.329 0.67 1.0
+## Q4_3   0.60 -0.05 0.335 0.67 1.0
+## Q4_4   0.52  0.13 0.349 0.65 1.1
+## Q4_5   0.67 -0.06 0.410 0.59 1.0
+## Q4_6   0.52  0.20 0.413 0.59 1.3
+## Q4_7   0.31 -0.13 0.072 0.93 1.4
+## Q4_8   0.34  0.07 0.146 0.85 1.1
+## Q4_9   0.65  0.14 0.533 0.47 1.1
+## Q4_10  0.68  0.02 0.481 0.52 1.0
+## Q4_12  0.40 -0.04 0.145 0.86 1.0
+## Q4_13  0.23  0.38 0.285 0.72 1.7
+## Q4_14  0.16  0.47 0.321 0.68 1.2
+## Q4_15  0.63  0.04 0.423 0.58 1.0
+## Q4_16  0.55  0.01 0.309 0.69 1.0
+## Q4_17  0.12  0.51 0.329 0.67 1.1
+## Q4_19 -0.07  0.95 0.835 0.16 1.0
+## Q5_1   0.07  0.78 0.672 0.33 1.0
+## Q5_2   0.02  0.85 0.742 0.26 1.0
+## Q5_3   0.08  0.51 0.306 0.69 1.1
+## Q5_4   0.51  0.25 0.446 0.55 1.5
+## Q5_6   0.44  0.16 0.288 0.71 1.2
+## Q5_7   0.59 -0.02 0.337 0.66 1.0
+## Q5_8   0.68  0.04 0.489 0.51 1.0
+## Q5_9   0.75 -0.02 0.549 0.45 1.0
+## Q5_10 -0.06  0.85 0.666 0.33 1.0
+## Q5_13  0.74  0.04 0.574 0.43 1.0
+## Q5_14  0.31 -0.04 0.085 0.91 1.0
+## Q5_15  0.57  0.09 0.388 0.61 1.1
+## Q5_17  0.49  0.15 0.334 0.67 1.2
+## Q5_18  0.35  0.20 0.230 0.77 1.6
+## Q5_19  0.52  0.25 0.466 0.53 1.4
+## 
+##                         ML1  ML2
+## SS loadings           14.80 7.39
+## Proportion Var         0.29 0.14
+## Cumulative Var         0.29 0.44
+## Proportion Explained   0.67 0.33
+## Cumulative Proportion  0.67 1.00
+## 
+##  With factor correlations of 
+##      ML1  ML2
+## ML1 1.00 0.49
+## ML2 0.49 1.00
+## 
+## Mean item complexity =  1.1
+## Test of the hypothesis that 2 factors are sufficient.
+## 
+## df null model =  1275  with the objective function =  35.47 with Chi Square =  11817.61
+## df of  the model are 1174  and the objective function was  9.54 
+## 
+## The root mean square of the residuals (RMSR) is  0.06 
+## The df corrected root mean square of the residuals is  0.06 
+## 
+## The harmonic n.obs is  352 with the empirical chi square  2962.25  with prob <  4.6e-155 
+## The total n.obs was  352  with Likelihood Chi Square =  3164.31  with prob <  3.7e-182 
+## 
+## Tucker Lewis Index of factoring reliability =  0.794
+## RMSEA index =  0.069  and the 90 % confidence intervals are  0.067 0.072
+## BIC =  -3719.59
+## Fit based upon off diagonal values = 0.98
+## Measures of factor score adequacy             
+##                                                    ML1  ML2
+## Correlation of (regression) scores with factors   0.98 0.98
+## Multiple R square of scores with factors          0.96 0.96
+## Minimum correlation of possible factor scores     0.93 0.93
+\end{verbatim}
+
+\begin{verbatim}
+## Factor Analysis using method =  ml
+## Call: fa(r = efaDF, nfactors = 3, rotate = "oblimin", fm = "ml")
+## Standardized loadings (pattern matrix) based upon correlation matrix
+##         ML1   ML2   ML3    h2   u2 com
+## Q2_1   0.47  0.17  0.20 0.445 0.56 1.6
+## Q2_2   0.63 -0.03  0.28 0.572 0.43 1.4
+## Q2_3   0.72 -0.05  0.08 0.528 0.47 1.0
+## Q2_4   0.71  0.09 -0.04 0.548 0.45 1.0
+## Q2_5   0.74 -0.07 -0.04 0.495 0.51 1.0
+## Q2_6   0.64  0.09  0.16 0.560 0.44 1.2
+## Q2_7   0.59  0.10 -0.26 0.371 0.63 1.4
+## Q2_8   0.74  0.01 -0.18 0.500 0.50 1.1
+## Q2_9   0.72  0.04 -0.18 0.492 0.51 1.1
+## Q2_10  0.39 -0.04  0.40 0.395 0.61 2.0
+## Q2_11  0.14  0.64  0.06 0.546 0.45 1.1
+## Q2_12 -0.06  0.92  0.02 0.804 0.20 1.0
+## Q2_13 -0.06  0.18  0.37 0.179 0.82 1.5
+## Q2_14  0.45  0.07  0.45 0.588 0.41 2.0
+## Q2_15  0.62 -0.05  0.11 0.418 0.58 1.1
+## Q2_16  0.75 -0.04  0.07 0.573 0.43 1.0
+## Q2_17  0.00  0.92 -0.02 0.837 0.16 1.0
+## Q2_18  0.13  0.76  0.02 0.686 0.31 1.1
+## Q2_19  0.53  0.15 -0.15 0.338 0.66 1.3
+## Q2_20  0.71 -0.07 -0.14 0.420 0.58 1.1
+## Q4_1   0.75 -0.02 -0.09 0.517 0.48 1.0
+## Q4_2   0.60 -0.03  0.00 0.340 0.66 1.0
+## Q4_3   0.64 -0.03 -0.07 0.367 0.63 1.0
+## Q4_4   0.40  0.15  0.23 0.371 0.63 1.9
+## Q4_5   0.54 -0.04  0.25 0.425 0.57 1.4
+## Q4_6   0.58  0.22 -0.13 0.459 0.54 1.4
+## Q4_7   0.07 -0.13  0.51 0.270 0.73 1.2
+## Q4_8   0.19  0.08  0.32 0.208 0.79 1.8
+## Q4_9   0.54  0.17  0.21 0.539 0.46 1.5
+## Q4_10  0.52  0.05  0.33 0.522 0.48 1.7
+## Q4_11 -0.12  0.13  0.45 0.212 0.79 1.3
+## Q4_12  0.42 -0.01 -0.06 0.161 0.84 1.0
+## Q4_13  0.20  0.39  0.07 0.287 0.71 1.6
+## Q4_14  0.23  0.48 -0.14 0.346 0.65 1.6
+## Q4_15  0.66  0.07 -0.07 0.451 0.55 1.0
+## Q4_16  0.30  0.01  0.54 0.497 0.50 1.6
+## Q4_17  0.00  0.51  0.25 0.381 0.62 1.4
+## Q4_18 -0.17  0.18  0.55 0.326 0.67 1.4
+## Q4_19 -0.05  0.95 -0.06 0.837 0.16 1.0
+## Q5_1   0.07  0.78  0.00 0.670 0.33 1.0
+## Q5_2   0.04  0.85 -0.04 0.744 0.26 1.0
+## Q5_3   0.09  0.51  0.00 0.305 0.69 1.1
+## Q5_4   0.50  0.28  0.00 0.453 0.55 1.6
+## Q5_5   0.13  0.01  0.03 0.021 0.98 1.1
+## Q5_6   0.33  0.17  0.24 0.313 0.69 2.4
+## Q5_7   0.46  0.01  0.25 0.356 0.64 1.5
+## Q5_8   0.49  0.06  0.41 0.568 0.43 2.0
+## Q5_9   0.70  0.01  0.08 0.544 0.46 1.0
+## Q5_10 -0.09  0.84  0.05 0.671 0.33 1.0
+## Q5_11 -0.09  0.15  0.15 0.042 0.96 2.7
+## Q5_12 -0.17  0.29  0.46 0.294 0.71 2.0
+## Q5_13  0.61  0.07  0.25 0.583 0.42 1.4
+## Q5_14  0.21 -0.03  0.21 0.107 0.89 2.0
+## Q5_15  0.62  0.12 -0.10 0.431 0.57 1.1
+## Q5_17  0.46  0.17  0.04 0.335 0.66 1.3
+## Q5_18  0.29  0.21  0.12 0.233 0.77 2.2
+## Q5_19  0.44  0.27  0.17 0.468 0.53 2.0
+## Q5_20  0.20 -0.06 -0.02 0.032 0.97 1.2
+## 
+##                         ML1  ML2  ML3
+## SS loadings           13.39 7.95 3.65
+## Proportion Var         0.23 0.14 0.06
+## Cumulative Var         0.23 0.37 0.43
+## Proportion Explained   0.54 0.32 0.15
+## Cumulative Proportion  0.54 0.85 1.00
+## 
+##  With factor correlations of 
+##      ML1  ML2  ML3
+## ML1 1.00 0.45 0.32
+## ML2 0.45 1.00 0.23
+## ML3 0.32 0.23 1.00
+## 
+## Mean item complexity =  1.4
+## Test of the hypothesis that 3 factors are sufficient.
+## 
+## df null model =  1653  with the objective function =  38.9 with Chi Square =  12870.73
+## df of  the model are 1482  and the objective function was  10.58 
+## 
+## The root mean square of the residuals (RMSR) is  0.05 
+## The df corrected root mean square of the residuals is  0.05 
+## 
+## The harmonic n.obs is  352 with the empirical chi square  3147.43  with prob <  7.2e-122 
+## The total n.obs was  352  with Likelihood Chi Square =  3478.38  with prob <  1.2e-161 
+## 
+## Tucker Lewis Index of factoring reliability =  0.8
+## RMSEA index =  0.062  and the 90 % confidence intervals are  0.059 0.065
+## BIC =  -5211.52
+## Fit based upon off diagonal values = 0.98
+## Measures of factor score adequacy             
+##                                                    ML1  ML2  ML3
+## Correlation of (regression) scores with factors   0.98 0.98 0.92
+## Multiple R square of scores with factors          0.96 0.96 0.84
+## Minimum correlation of possible factor scores     0.92 0.93 0.68
+\end{verbatim}
+
+\begin{verbatim}
+## Factor Analysis using method =  ml
+## Call: fa(r = efaDF %>% select(efa_loadings %>% filter(keep == "yes") %>% 
+##     pull(question)), nfactors = 3, rotate = "oblimin", fm = "ml")
+## Standardized loadings (pattern matrix) based upon correlation matrix
+##         ML2   ML1   ML3   h2   u2 com
+## Q2_1   0.53  0.13  0.18 0.45 0.55 1.4
+## Q2_2   0.70 -0.06  0.18 0.54 0.46 1.1
+## Q2_3   0.75 -0.05 -0.02 0.53 0.47 1.0
+## Q2_4   0.71  0.10 -0.11 0.56 0.44 1.1
+## Q2_5   0.75 -0.06 -0.11 0.50 0.50 1.1
+## Q2_6   0.69  0.06  0.09 0.55 0.45 1.0
+## Q2_7   0.53  0.11 -0.18 0.33 0.67 1.3
+## Q2_8   0.69  0.01 -0.12 0.46 0.54 1.1
+## Q2_9   0.68  0.03 -0.11 0.46 0.54 1.1
+## Q2_11  0.16  0.62  0.09 0.55 0.45 1.2
+## Q2_12 -0.05  0.92  0.00 0.81 0.19 1.0
+## Q2_13  0.02  0.10  0.42 0.21 0.79 1.1
+## Q2_15  0.66 -0.05  0.00 0.41 0.59 1.0
+## Q2_16  0.78 -0.04 -0.05 0.57 0.43 1.0
+## Q2_17  0.00  0.92 -0.01 0.84 0.16 1.0
+## Q2_18  0.14  0.74  0.05 0.69 0.31 1.1
+## Q2_19  0.50  0.14 -0.09 0.32 0.68 1.2
+## Q2_20  0.67 -0.07 -0.11 0.40 0.60 1.1
+## Q4_1   0.73 -0.03 -0.07 0.50 0.50 1.0
+## Q4_2   0.61 -0.05  0.01 0.35 0.65 1.0
+## Q4_3   0.63 -0.03 -0.08 0.37 0.63 1.0
+## Q4_4   0.46  0.11  0.20 0.36 0.64 1.5
+## Q4_5   0.61 -0.09  0.22 0.42 0.58 1.3
+## Q4_6   0.56  0.23 -0.12 0.45 0.55 1.4
+## Q4_7   0.19 -0.20  0.43 0.21 0.79 1.8
+## Q4_8   0.27  0.01  0.34 0.23 0.77 1.9
+## Q4_9   0.60  0.13  0.18 0.54 0.46 1.3
+## Q4_11 -0.01  0.04  0.50 0.26 0.74 1.0
+## Q4_12  0.41 -0.03 -0.02 0.16 0.84 1.0
+## Q4_13  0.22  0.35  0.14 0.30 0.70 2.1
+## Q4_14  0.20  0.49 -0.11 0.34 0.66 1.5
+## Q4_15  0.65  0.08 -0.09 0.45 0.55 1.1
+## Q4_17  0.06  0.44  0.34 0.42 0.58 1.9
+## Q4_18 -0.05  0.05  0.68 0.48 0.52 1.0
+## Q4_19 -0.06  0.96 -0.05 0.84 0.16 1.0
+## Q5_1   0.08  0.78  0.00 0.67 0.33 1.0
+## Q5_2   0.03  0.85 -0.02 0.74 0.26 1.0
+## Q5_3   0.08  0.51  0.00 0.31 0.69 1.1
+## Q5_4   0.51  0.25  0.05 0.45 0.55 1.5
+## Q5_6   0.39  0.13  0.22 0.31 0.69 1.8
+## Q5_7   0.53 -0.04  0.23 0.36 0.64 1.4
+## Q5_9   0.74 -0.01  0.03 0.55 0.45 1.0
+## Q5_10 -0.07  0.82  0.09 0.67 0.33 1.0
+## Q5_12 -0.06  0.18  0.57 0.39 0.61 1.2
+## Q5_13  0.68  0.01  0.25 0.60 0.40 1.3
+## Q5_15  0.60  0.10 -0.02 0.42 0.58 1.1
+## Q5_17  0.48  0.13  0.09 0.34 0.66 1.2
+## Q5_19  0.49  0.24  0.12 0.46 0.54 1.6
+## 
+##                         ML2  ML1  ML3
+## SS loadings           12.36 7.36 2.42
+## Proportion Var         0.26 0.15 0.05
+## Cumulative Var         0.26 0.41 0.46
+## Proportion Explained   0.56 0.33 0.11
+## Cumulative Proportion  0.56 0.89 1.00
+## 
+##  With factor correlations of 
+##      ML2  ML1  ML3
+## ML2 1.00 0.46 0.20
+## ML1 0.46 1.00 0.28
+## ML3 0.20 0.28 1.00
+## 
+## Mean item complexity =  1.2
+## Test of the hypothesis that 3 factors are sufficient.
+## 
+## df null model =  1128  with the objective function =  31.98 with Chi Square =  10685.83
+## df of  the model are 987  and the objective function was  7.17 
+## 
+## The root mean square of the residuals (RMSR) is  0.05 
+## The df corrected root mean square of the residuals is  0.05 
+## 
+## The harmonic n.obs is  352 with the empirical chi square  1731.72  with prob <  1.4e-43 
+## The total n.obs was  352  with Likelihood Chi Square =  2381.61  with prob <  1.1e-116 
+## 
+## Tucker Lewis Index of factoring reliability =  0.832
+## RMSEA index =  0.063  and the 90 % confidence intervals are  0.06 0.067
+## BIC =  -3405.79
+## Fit based upon off diagonal values = 0.98
+## Measures of factor score adequacy             
+##                                                    ML2  ML1  ML3
+## Correlation of (regression) scores with factors   0.98 0.98 0.89
+## Multiple R square of scores with factors          0.96 0.96 0.79
+## Minimum correlation of possible factor scores     0.92 0.93 0.58
+\end{verbatim}
+
+\begin{verbatim}
+## Factor Analysis using method =  ml
+## Call: fa(r = efaDF, nfactors = 5, rotate = "oblimin", fm = "ml")
+## Standardized loadings (pattern matrix) based upon correlation matrix
+##         ML2   ML5   ML1   ML3   ML4   h2   u2 com
+## Q2_1   0.13  0.40  0.13  0.27 -0.05 0.48 0.52 2.3
+## Q2_2  -0.01  0.20  0.49  0.25  0.04 0.57 0.43 1.9
+## Q2_3   0.04  0.02  0.81 -0.06  0.00 0.67 0.33 1.0
+## Q2_4   0.14  0.24  0.52 -0.09  0.10 0.58 0.42 1.7
+## Q2_5  -0.03  0.33  0.45 -0.04  0.05 0.48 0.52 1.9
+## Q2_6   0.09  0.32  0.34  0.18  0.11 0.56 0.44 2.9
+## Q2_7   0.11  0.48  0.13 -0.18  0.05 0.36 0.64 1.6
+## Q2_8  -0.04  0.77  0.05 -0.08  0.01 0.59 0.41 1.0
+## Q2_9  -0.02  0.79  0.02 -0.07 -0.04 0.61 0.39 1.0
+## Q2_10 -0.03  0.03  0.39  0.36  0.06 0.39 0.61 2.1
+## Q2_11  0.64  0.06  0.10  0.06  0.01 0.55 0.45 1.1
+## Q2_12  0.92 -0.07  0.04  0.01 -0.06 0.81 0.19 1.0
+## Q2_13  0.11  0.05 -0.07  0.41 -0.13 0.22 0.78 1.4
+## Q2_14  0.08  0.01  0.49  0.39  0.06 0.59 0.41 2.0
+## Q2_15  0.04 -0.05  0.79 -0.04 -0.04 0.57 0.43 1.0
+## Q2_16  0.05  0.04  0.82 -0.08  0.01 0.72 0.28 1.0
+## Q2_17  0.92  0.00  0.03 -0.03 -0.07 0.84 0.16 1.0
+## Q2_18  0.77  0.01  0.11  0.01  0.05 0.69 0.31 1.1
+## Q2_19  0.11  0.61 -0.06 -0.02  0.04 0.39 0.61 1.1
+## Q2_20 -0.09  0.59  0.13 -0.06  0.15 0.45 0.55 1.3
+## Q4_1  -0.03  0.57  0.25 -0.03  0.01 0.53 0.47 1.4
+## Q4_2  -0.01  0.33  0.30  0.03  0.02 0.33 0.67 2.0
+## Q4_3   0.00  0.35  0.29 -0.03  0.09 0.35 0.65 2.1
+## Q4_4   0.15  0.17  0.26  0.24  0.05 0.37 0.63 3.4
+## Q4_5  -0.05  0.28  0.32  0.27  0.02 0.43 0.57 3.0
+## Q4_6   0.23  0.41  0.21 -0.07 -0.02 0.45 0.55 2.2
+## Q4_7  -0.16 -0.09  0.12  0.53  0.16 0.31 0.69 1.6
+## Q4_8   0.00  0.29 -0.07  0.41 -0.02 0.27 0.73 1.9
+## Q4_9   0.15  0.34  0.26  0.24  0.00 0.54 0.46 3.2
+## Q4_10  0.07  0.09  0.51  0.27 -0.04 0.53 0.47 1.7
+## Q4_11  0.05  0.04 -0.07  0.50 -0.26 0.31 0.69 1.6
+## Q4_12 -0.01  0.27  0.13 -0.01  0.13 0.16 0.84 2.0
+## Q4_13  0.36  0.19  0.00  0.12  0.08 0.30 0.70 1.9
+## Q4_14  0.49  0.13  0.07 -0.12  0.12 0.35 0.65 1.4
+## Q4_15  0.10  0.33  0.38 -0.06  0.00 0.45 0.55 2.2
+## Q4_16  0.02 -0.07  0.40  0.49  0.07 0.50 0.50 2.0
+## Q4_17  0.49 -0.02  0.01  0.26  0.10 0.39 0.61 1.6
+## Q4_18  0.10 -0.04 -0.16  0.63  0.06 0.40 0.60 1.2
+## Q4_19  0.94  0.03 -0.07 -0.04 -0.04 0.84 0.16 1.0
+## Q5_1   0.79  0.00  0.05  0.00  0.07 0.68 0.32 1.0
+## Q5_2   0.85  0.03 -0.01 -0.03  0.07 0.75 0.25 1.0
+## Q5_3   0.52  0.01 -0.04  0.02  0.40 0.47 0.53 1.9
+## Q5_4   0.24  0.46  0.05  0.09  0.12 0.49 0.51 1.8
+## Q5_5   0.01  0.04 -0.11  0.08  0.65 0.42 0.58 1.1
+## Q5_6   0.15  0.17  0.16  0.27  0.08 0.32 0.68 3.4
+## Q5_7  -0.01  0.23  0.27  0.26  0.05 0.36 0.64 3.0
+## Q5_8   0.07  0.10  0.45  0.37  0.01 0.57 0.43 2.1
+## Q5_9   0.06  0.21  0.56  0.04  0.02 0.57 0.43 1.3
+## Q5_10  0.82  0.00 -0.07  0.06 -0.06 0.67 0.33 1.0
+## Q5_11  0.10  0.09 -0.02  0.18 -0.54 0.33 0.67 1.4
+## Q5_12  0.22 -0.06 -0.09  0.50 -0.05 0.32 0.68 1.5
+## Q5_13  0.05  0.36  0.30  0.29  0.00 0.59 0.41 2.9
+## Q5_14 -0.03  0.04  0.21  0.20 -0.05 0.11 0.89 2.2
+## Q5_15  0.05  0.76 -0.07  0.04 -0.03 0.56 0.44 1.0
+## Q5_17  0.10  0.60 -0.09  0.19 -0.05 0.44 0.56 1.3
+## Q5_18  0.14  0.44 -0.14  0.25  0.04 0.32 0.68 2.1
+## Q5_19  0.30  0.11  0.34  0.15  0.10 0.48 0.52 2.8
+## Q5_20 -0.02 -0.02 -0.01 -0.01  0.79 0.61 0.39 1.0
+## 
+##                        ML2  ML5  ML1  ML3  ML4
+## SS loadings           7.83 7.27 7.06 3.91 1.94
+## Proportion Var        0.14 0.13 0.12 0.07 0.03
+## Cumulative Var        0.14 0.26 0.38 0.45 0.48
+## Proportion Explained  0.28 0.26 0.25 0.14 0.07
+## Cumulative Proportion 0.28 0.54 0.79 0.93 1.00
+## 
+##  With factor correlations of 
+##      ML2  ML5  ML1  ML3  ML4
+## ML2 1.00 0.43 0.33 0.31 0.10
+## ML5 0.43 1.00 0.62 0.25 0.17
+## ML1 0.33 0.62 1.00 0.30 0.20
+## ML3 0.31 0.25 0.30 1.00 0.06
+## ML4 0.10 0.17 0.20 0.06 1.00
+## 
+## Mean item complexity =  1.7
+## Test of the hypothesis that 5 factors are sufficient.
+## 
+## df null model =  1653  with the objective function =  38.9 with Chi Square =  12870.73
+## df of  the model are 1373  and the objective function was  8.33 
+## 
+## The root mean square of the residuals (RMSR) is  0.04 
+## The df corrected root mean square of the residuals is  0.04 
+## 
+## The harmonic n.obs is  352 with the empirical chi square  1829.65  with prob <  1.3e-15 
+## The total n.obs was  352  with Likelihood Chi Square =  2727.58  with prob <  4.9e-92 
+## 
+## Tucker Lewis Index of factoring reliability =  0.853
+## RMSEA index =  0.053  and the 90 % confidence intervals are  0.05 0.056
+## BIC =  -5323.18
+## Fit based upon off diagonal values = 0.99
+## Measures of factor score adequacy             
+##                                                    ML2  ML5  ML1  ML3  ML4
+## Correlation of (regression) scores with factors   0.98 0.96 0.96 0.92 0.89
+## Multiple R square of scores with factors          0.97 0.92 0.93 0.84 0.79
+## Minimum correlation of possible factor scores     0.93 0.84 0.85 0.69 0.57
+\end{verbatim}
+
+\begin{verbatim}
+## Factor Analysis using method =  ml
+## Call: fa(r = efaDF %>% select(efa_loadings %>% filter(keep == 1) %>% 
+##     pull(question)), nfactors = 5, rotate = "oblimin", fm = "ml")
+## Standardized loadings (pattern matrix) based upon correlation matrix
+##         ML1   ML2   ML3   ML5   ML4    h2   u2 com
+## Q2_1   0.16  0.16  0.15  0.35  0.15 0.450 0.55 2.8
+## Q2_2  -0.02  0.50  0.08  0.24  0.17 0.545 0.45 1.8
+## Q2_3   0.01  0.84  0.02 -0.04 -0.01 0.699 0.30 1.0
+## Q2_4   0.15  0.54  0.13  0.16 -0.14 0.583 0.42 1.6
+## Q2_7   0.12  0.17  0.27  0.19 -0.14 0.324 0.68 3.8
+## Q2_8  -0.03  0.03  0.94 -0.08  0.03 0.846 0.15 1.0
+## Q2_9   0.01  0.01  0.85  0.01  0.01 0.747 0.25 1.0
+## Q2_11  0.63  0.13  0.05 -0.01  0.08 0.555 0.45 1.1
+## Q2_12  0.92  0.00 -0.06  0.00  0.00 0.809 0.19 1.0
+## Q2_13  0.08 -0.04  0.12 -0.04  0.47 0.252 0.75 1.2
+## Q2_15  0.00  0.83  0.03 -0.15  0.02 0.635 0.37 1.1
+## Q2_16  0.03  0.84  0.07 -0.07 -0.05 0.742 0.26 1.0
+## Q2_17  0.93  0.00  0.02 -0.05  0.00 0.844 0.16 1.0
+## Q2_18  0.76  0.14  0.00  0.00  0.05 0.695 0.31 1.1
+## Q2_19  0.15 -0.04  0.25  0.47 -0.11 0.437 0.56 1.9
+## Q2_20 -0.06  0.18  0.43  0.25 -0.08 0.447 0.55 2.1
+## Q4_1  -0.01  0.27  0.45  0.16 -0.01 0.522 0.48 1.9
+## Q4_2  -0.02  0.33  0.14  0.25  0.03 0.341 0.66 2.3
+## Q4_3   0.00  0.31  0.11  0.32 -0.05 0.353 0.65 2.3
+## Q4_5  -0.06  0.38  0.06  0.33  0.19 0.454 0.55 2.6
+## Q4_6   0.25  0.24  0.15  0.27 -0.10 0.445 0.56 3.9
+## Q4_7  -0.19  0.17 -0.20  0.30  0.37 0.260 0.74 3.6
+## Q4_8   0.00  0.01  0.06  0.37  0.28 0.281 0.72 1.9
+## Q4_9   0.16  0.31  0.15  0.28  0.15 0.532 0.47 3.6
+## Q4_10  0.05  0.50  0.04  0.16  0.20 0.500 0.50 1.6
+## Q4_11  0.00 -0.04  0.11 -0.06  0.58 0.331 0.67 1.1
+## Q4_13  0.36  0.08  0.04  0.17  0.10 0.300 0.70 1.8
+## Q4_14  0.50  0.09  0.06  0.08 -0.12 0.341 0.66 1.3
+## Q4_17  0.44  0.10  0.05 -0.08  0.35 0.438 0.56 2.1
+## Q4_18  0.01 -0.04 -0.02  0.04  0.74 0.549 0.45 1.0
+## Q4_19  0.95 -0.10  0.02  0.01 -0.03 0.838 0.16 1.0
+## Q5_1   0.79  0.05 -0.05  0.08 -0.02 0.672 0.33 1.0
+## Q5_2   0.85 -0.01  0.03  0.01 -0.01 0.742 0.26 1.0
+## Q5_4   0.26  0.13  0.23  0.29  0.02 0.476 0.52 3.3
+## Q5_5  -0.02  0.04  0.03  0.11  0.05 0.027 0.97 2.2
+## Q5_9   0.05  0.59  0.01  0.24 -0.02 0.576 0.42 1.3
+## Q5_10  0.82 -0.06 -0.01 -0.02  0.08 0.674 0.33 1.0
+## Q5_12  0.16 -0.01  0.00 -0.06  0.61 0.434 0.57 1.2
+## Q5_15  0.09 -0.01  0.55  0.26  0.02 0.544 0.46 1.5
+## Q5_17  0.14 -0.05  0.25  0.47  0.04 0.452 0.55 1.8
+## Q5_18  0.17 -0.09  0.11  0.47  0.10 0.357 0.64 1.6
+## Q5_19  0.30  0.37 -0.08  0.28  0.02 0.483 0.52 3.0
+## Q5_20 -0.05  0.14 -0.03  0.14 -0.05 0.041 0.96 2.6
+## 
+##                        ML1  ML2  ML3  ML5  ML4
+## SS loadings           7.26 5.24 3.67 3.14 2.26
+## Proportion Var        0.17 0.12 0.09 0.07 0.05
+## Cumulative Var        0.17 0.29 0.38 0.45 0.50
+## Proportion Explained  0.34 0.24 0.17 0.15 0.10
+## Cumulative Proportion 0.34 0.58 0.75 0.90 1.00
+## 
+##  With factor correlations of 
+##      ML1  ML2  ML3  ML5  ML4
+## ML1 1.00 0.36 0.35 0.34 0.29
+## ML2 0.36 1.00 0.56 0.44 0.15
+## ML3 0.35 0.56 1.00 0.44 0.08
+## ML5 0.34 0.44 0.44 1.00 0.18
+## ML4 0.29 0.15 0.08 0.18 1.00
+## 
+## Mean item complexity =  1.8
+## Test of the hypothesis that 5 factors are sufficient.
+## 
+## df null model =  903  with the objective function =  27.79 with Chi Square =  9333.35
+## df of  the model are 698  and the objective function was  4.52 
+## 
+## The root mean square of the residuals (RMSR) is  0.04 
+## The df corrected root mean square of the residuals is  0.05 
+## 
+## The harmonic n.obs is  352 with the empirical chi square  1021.68  with prob <  1.3e-14 
+## The total n.obs was  352  with Likelihood Chi Square =  1504.09  with prob <  3.9e-61 
+## 
+## Tucker Lewis Index of factoring reliability =  0.875
+## RMSEA index =  0.057  and the 90 % confidence intervals are  0.053 0.061
+## BIC =  -2588.72
+## Fit based upon off diagonal values = 0.99
+## Measures of factor score adequacy             
+##                                                    ML1  ML2  ML3  ML5  ML4
+## Correlation of (regression) scores with factors   0.98 0.96 0.96 0.89 0.89
+## Multiple R square of scores with factors          0.96 0.92 0.92 0.80 0.79
+## Minimum correlation of possible factor scores     0.93 0.84 0.84 0.59 0.58
+\end{verbatim}
+
+\begin{verbatim}
+## Factor Analysis using method =  ml
+## Call: fa(r = efaDF %>% select(efa_loadings_2 %>% filter(keep == 1) %>% 
+##     pull(question)), nfactors = 5, rotate = "oblimin", fm = "ml")
+## Standardized loadings (pattern matrix) based upon correlation matrix
+##         ML1   ML3   ML2   ML5   ML4   h2   u2 com
+## Q2_1   0.12  0.23  0.12  0.31  0.15 0.44 0.56 3.1
+## Q2_2  -0.03  0.56  0.07  0.17  0.16 0.53 0.47 1.4
+## Q2_3   0.00  0.86 -0.01 -0.04 -0.01 0.70 0.30 1.0
+## Q2_4   0.14  0.56  0.11  0.15 -0.15 0.58 0.42 1.5
+## Q2_8   0.00 -0.01  0.95 -0.06  0.02 0.85 0.15 1.0
+## Q2_9   0.02 -0.01  0.84  0.04  0.00 0.74 0.26 1.0
+## Q2_11  0.65  0.13  0.08 -0.06  0.07 0.55 0.45 1.2
+## Q2_12  0.92  0.00 -0.07  0.02  0.00 0.82 0.18 1.0
+## Q2_13  0.06 -0.03  0.10 -0.01  0.48 0.26 0.74 1.1
+## Q2_15 -0.01  0.82  0.00 -0.10  0.02 0.61 0.39 1.0
+## Q2_16  0.02  0.84  0.05 -0.05 -0.04 0.74 0.26 1.0
+## Q2_17  0.92 -0.01  0.03 -0.04  0.00 0.84 0.16 1.0
+## Q2_18  0.76  0.15  0.02 -0.05  0.06 0.69 0.31 1.1
+## Q2_19  0.10  0.03  0.20  0.46 -0.09 0.40 0.60 1.6
+## Q2_20 -0.06  0.20  0.43  0.18 -0.09 0.43 0.57 2.0
+## Q4_1   0.00  0.29  0.45  0.09  0.01 0.51 0.49 1.8
+## Q4_2  -0.01  0.37  0.16  0.11  0.05 0.30 0.70 1.6
+## Q4_8  -0.04  0.08 -0.01  0.42  0.21 0.27 0.73 1.6
+## Q4_9   0.13  0.35  0.12  0.26  0.13 0.52 0.48 2.8
+## Q4_10  0.06  0.54  0.06  0.06  0.19 0.48 0.52 1.3
+## Q4_11 -0.02 -0.03  0.08 -0.01  0.60 0.35 0.65 1.0
+## Q4_13  0.34  0.11  0.01  0.18  0.07 0.29 0.71 1.9
+## Q4_14  0.53  0.09  0.11 -0.03 -0.12 0.34 0.66 1.3
+## Q4_18 -0.02  0.00 -0.04  0.04  0.75 0.57 0.43 1.0
+## Q4_19  0.94 -0.10  0.02  0.02 -0.02 0.84 0.16 1.0
+## Q5_1   0.78  0.07 -0.06  0.10 -0.02 0.68 0.32 1.1
+## Q5_2   0.85 -0.01  0.03  0.02 -0.01 0.74 0.26 1.0
+## Q5_9   0.02  0.65 -0.03  0.23 -0.02 0.57 0.43 1.3
+## Q5_10  0.82 -0.06 -0.01  0.00  0.07 0.67 0.33 1.0
+## Q5_12  0.13  0.01 -0.02 -0.03  0.63 0.45 0.55 1.1
+## Q5_15  0.07  0.02  0.50  0.29 -0.01 0.54 0.46 1.7
+## Q5_17  0.03  0.01  0.10  0.70  0.01 0.60 0.40 1.0
+## Q5_18  0.07 -0.02 -0.04  0.67  0.05 0.48 0.52 1.0
+## 
+##                        ML1  ML3  ML2  ML5  ML4
+## SS loadings           6.42 4.68 3.00 2.41 1.88
+## Proportion Var        0.19 0.14 0.09 0.07 0.06
+## Cumulative Var        0.19 0.34 0.43 0.50 0.56
+## Proportion Explained  0.35 0.25 0.16 0.13 0.10
+## Cumulative Proportion 0.35 0.60 0.77 0.90 1.00
+## 
+##  With factor correlations of 
+##      ML1  ML3  ML2  ML5  ML4
+## ML1 1.00 0.37 0.33 0.43 0.30
+## ML3 0.37 1.00 0.59 0.42 0.13
+## ML2 0.33 0.59 1.00 0.50 0.08
+## ML5 0.43 0.42 0.50 1.00 0.22
+## ML4 0.30 0.13 0.08 0.22 1.00
+## 
+## Mean item complexity =  1.3
+## Test of the hypothesis that 5 factors are sufficient.
+## 
+## df null model =  528  with the objective function =  21.69 with Chi Square =  7357.73
+## df of  the model are 373  and the objective function was  2.17 
+## 
+## The root mean square of the residuals (RMSR) is  0.03 
+## The df corrected root mean square of the residuals is  0.03 
+## 
+## The harmonic n.obs is  352 with the empirical chi square  300.78  with prob <  1 
+## The total n.obs was  352  with Likelihood Chi Square =  727.35  with prob <  4.3e-25 
+## 
+## Tucker Lewis Index of factoring reliability =  0.926
+## RMSEA index =  0.052  and the 90 % confidence intervals are  0.046 0.058
+## BIC =  -1459.79
+## Fit based upon off diagonal values = 0.99
+## Measures of factor score adequacy             
+##                                                    ML1  ML3  ML2  ML5  ML4
+## Correlation of (regression) scores with factors   0.98 0.96 0.96 0.90 0.88
+## Multiple R square of scores with factors          0.96 0.92 0.92 0.81 0.77
+## Minimum correlation of possible factor scores     0.93 0.84 0.83 0.61 0.55
+\end{verbatim}
+
 \begin{itemize}
@@
 \item
-  try running with outliers as well --\textgreater{} if differences: then talk
-  about what is going on with the outlier people
+  take the final version of each ``best model''
+\item
+  get down to 5 items each or whatever is left (best loading and
+  theoretical)
+\item
+  look at the fit indices to tell which may be best
 \end{itemize}
-
-\section{Assumptions -------------------------------------------------------------}\label{assumptions--}
-
-\section{Linearity}\label{linearity}
-
-random = rchisq(nrow(noout{[} , 37:97{]}), 7) fake = lm(random\textasciitilde.,
-data=noout{[} , 37:97{]})
-
-standardized = rstudent(fake) \{qqnorm(standardized) abline(0,1)\} \#seems
-okay
-
-\section{Normality}\label{normality}
-
-hist(standardized, breaks=15) \#a little skewed but mostly centered on 0
-and between -2 and 2 so okay
-
-\section{Homog/s}\label{homogs}
-
-fitvalues = scale(fake\$fitted.values) \{plot(fitvalues, standardized)
-abline(0,0) abline(v = 0)\} \#some homogeneity issues but we'll accept it
-
-write.csv(noout, file = ``sona\_data\_screened.csv'', row.names = F)
-library(beepr) beep(sound = 5)
-
-```
 
@@
 \begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-aust2022}
-Aust, F., Barth, M., Diedenhofen, B., Stahl, C., Casillas, J.
-V., \& Siegel, R.
-(2022).
-\emph{Papaja: Prepare american psychological association journal articles with r markdown}.
-Retrieved from \url{https://CRAN.R-project.org/package=papaja}
-
 \bibitem[\citeproctext]{ref-burke2010}
@@
 \url{https://doi.org/10.1177/1088868309352321}
+
+\bibitem[\citeproctext]{ref-drolet1990}
+Drolet, J.-L. (1990). Transcending death during early adulthood: Symbolic immortality, death anxiety, and purpose in life. \emph{Journal of Clinical Psychology}, \emph{46}(2), 148--160.
+
+\bibitem[\citeproctext]{ref-erikson1950}
+Erikson, Erik H. (1950). \emph{Childhood and society}. New York: Norton.
+
+\bibitem[\citeproctext]{ref-erikson1963}
+Erikson, E. H. (1963). \emph{Childhood and society} (2nd ed.). New York: Norton.
 
@@
 
+\bibitem[\citeproctext]{ref-kotre1984}
+Kotre, J. (1984). \emph{Outliving the self: How we live on in future generations}. New York: W. W. Norton \& Company, Inc.
+
 \bibitem[\citeproctext]{ref-mathews1988}
@@
 \url{https://doi.org/10.1177/089976408801700202}
+
+\bibitem[\citeproctext]{ref-mathews1987}
+Mathews, R.
+C., \& Mister, R.
+D.
+(1987).
+Measuring an Individual's Investment in the Future: Symbolic Immortality, Sensation Seeking, and Psychic Numbness.
+\emph{OMEGA - Journal of Death and Dying}, \emph{18}(3), 161--173.
+\url{https://doi.org/10.2190/NL7H-YY22-DN6Q-5XEB}
 
@@
 
+\bibitem[\citeproctext]{ref-zuckerman1979}
+Zuckerman, M., \& Neeb, M. (1979). Sensation seeking and psychopathology. \emph{Psychiatry Research}, \emph{1}(3), 255--264. \url{https://doi.org/10.1016/0165-1781(79)90007-6}
+
 \end{CSLReferences}

### 2024-10-15 05_Manuscript/manuscript.Rmd
added item text to factor loadings output

@@
 nrow(cfaDF_noout)
+
+write.csv(efaDF, "../03_Data/efaDF.csv", row.names = F)
+write.csv(cfaDF, "../03_Data/cfaDF.csv", row.names = F)
 ```
@@
 ```{r}
+#efaDF <- read.csv("../03_Data/efaDF.csv")
+
 number_items <- fa.parallel(efaDF, #data frame
@@
 ```{r}
+item_text <- read.csv("../03_Data/item_text.csv")
+
 EFA_fit <- fa(efaDF, #data
@@
   mutate(question = rownames(.))
+
+## Make a dataframe with loadings and item text
+model1_loadings <- efa_loadings_2
+model1_loadings$ItemNum <- row.names(model1_loadings)
+model1_withtext <- merge(item_text, model1_loadings, by = 'ItemNum')
+
 ```
@@
 ```{r}
+
 EFA_fit <- fa(efaDF, #data
@@
   )
+
+model2_loadings <- efa_loadings_2
+model2_loadings$ItemNum <- row.names(model2_loadings)
+model2_withtext <- merge(item_text, model2_loadings, by = 'ItemNum')
 ```
@@
 
+model3_loadings <- efa_loadings_3
+model3_loadings$ItemNum <- model3_loadings$question
+model3_withtext <- merge(item_text, model3_loadings, by = 'ItemNum')
+
 ```
@@
 
+**Model 1: Two-Factor**
+
+These are all the items with loading \> 0.7
+
+-   Factor One: Sense of Contribution
+
+    -   Q2_16: I have taken part in activities or events which will
+        impact the future.
+
+    -   Q2_2: I have contributed to the world in a unique way.
+
+    -   Q2_3: I have contributed to causes that will impact the future.
+
+    -   Q5_9: I have contributed to things which will be meaningful.
+
+    -   Q5_13: I will leave a lasting legacy.
+
+    -   Q2_5: I am proud of my accomplishments.
+
+    -   Q2_6: I am confident in the legacy I will leave when I die.
+
+    -   Q4_1: Others would say I have impacted their lives.
+
+<!-- -->
+
+-   Factor Two: Spiritual Immortality
+
+    -   Q4_19: I believe in an afterlife.
+
+    -   Q2_17: My spirit or soul will live on after I physically die.
+
+    -   Q2_12: I believe I will live on in the afterlife.
+
+    -   Q5_2: Death is not the end.
+
+    -   Q5_10: I believe in an immaterial soul or spirit.
+
+    -   Q5_1: I am comforted by the thought of an afterlife.
+
+    -   Q2_18: Death will not be the end of me.
+
+**Model 2: Three-Factor**
+
+-   Factor One:
+
+    -   Q2_16: I have taken part in activities or events which will
+        impact the future.
+
+    -   Q2_3: I have contributed to causes that will impact the future.
+
+    -   Q2_5: I am proud of my accomplishments.
+
+    -   Q5_9: I have contributed to things which will be meaningful.
+
+    -   Q4_1: Others would say I have impacted their lives.
+
+    -   Q2_4: I feel I have taken part in something bigger than myself.
+
+    -   Q2_2: I have contributed to the world in a unique way.
+
+<!-- -->
+
+-   Factor Two:
+
+    -   Q
+
+<!-- -->
+
+-   Factor Three:
+
+    -   Q
+
+**Model 3: Five-Factor**
+
 # Discussion

### 2024-10-18 05_Manuscript/manuscript.Rmd
updating efa analyses

--- 2024-10-06 05_Manuscript/manuscript.Rmd
@@
 
+questions <- import("../03_Data/questions.xlsx")
 ```
@@
 
-also do five
-
 ```{r}
@@
   )) %>% 
-  mutate(question = rownames(.))
+  mutate(question = rownames(.)) %>% 
+  left_join(questions,
+            by = c("question" = "Question_Number")) %>% 
+  arrange(desc(ML1)) %>% 
+  export(., "results/2_factor.xlsx", row.names = F)
 ```
@@
           )
-  )
+  ) %>% 
+  left_join(questions,
+            by = c("question" = "Question_Number")) %>% 
+  arrange(desc(ML1)) %>% 
+  export(., "results/3_factor.xlsx", row.names = F)
 ```
@@
   mutate(keep = sum(c_across(-question) >= .30)) %>% 
-  ungroup()
+  ungroup() %>% 
+  left_join(questions,
+            by = c("question" = "Question_Number")) %>% 
+  arrange(desc(ML1)) %>% 
+  export(., "results/5_factor.xlsx", row.names = F)
 

### 2024-10-22 05_Manuscript/manuscript.Rmd
updating efa results

--- 2024-10-15 05_Manuscript/manuscript.Rmd
@@
   )) %>% 
-  mutate(question = rownames(.))
-
-## Make a dataframe with loadings and item text
-model1_loadings <- efa_loadings_2
-model1_loadings$ItemNum <- row.names(model1_loadings)
-model1_withtext <- merge(item_text, model1_loadings, by = 'ItemNum')
-
+  mutate(question = rownames(.)) %>% 
+  left_join(questions,
+            by = c("question" = "Question_Number")) %>% 
+  arrange(desc(ML1)) %>% 
+  export(., "results/2_factor.xlsx", row.names = F)
 ```
@@
           )
-  )
-
-model2_loadings <- efa_loadings_2
-model2_loadings$ItemNum <- row.names(model2_loadings)
-model2_withtext <- merge(item_text, model2_loadings, by = 'ItemNum')
+  ) %>% 
+  left_join(questions,
+            by = c("question" = "Question_Number")) %>% 
+  arrange(desc(ML1)) %>% 
+  export(., "results/3_factor.xlsx", row.names = F)
 ```
@@
   mutate(keep = sum(c_across(-question) >= .30)) %>% 
-  ungroup()
-
-model3_loadings <- efa_loadings_3
-model3_loadings$ItemNum <- model3_loadings$question
-model3_withtext <- merge(item_text, model3_loadings, by = 'ItemNum')
-
-```
-
--   take the final version of each "best model"
--   get down to 5 items each or whatever is left (best loading and
-    theoretical)
--   look at the fit indices to tell which may be best
+  ungroup() %>% 
+  left_join(questions,
+            by = c("question" = "Question_Number")) %>% 
+  arrange(desc(ML1)) %>% 
+  export(., "results/5_factor.xlsx", row.names = F)
+```
+
+- import the edited files and test those models for fit 
+- theory is 5, so if the fit is similar, then go with five
+
+--- 
+test cfa 
+test MGCFA --> use new package to include information 
+---
 

### 2024-12-10 05_Manuscript/manuscript.Rmd
updating with trackdown

@@
 library(trackdown)
+source("~/GitHub/files/google_creds.R")
 # upload_file(
@@
 
-# Method
-
-## Participants
-
-## Material
-
-## Procedure
-
-## Data analysis
-
-# Results
-
 ```{r libraries}
@@
 library(psych)
+library(visualizemi)
+library(lavaan)
 
@@
 
+# Method
+
+## Participants
+
+```{r get-age}
+sona <- sona %>% 
+  mutate(Q13 = gsub("[a-z]", "", Q13)) %>% 
+  mutate(Q13 = ifelse(
+    Q13 == 1991, 2018-1991, Q13)
+  ) %>% 
+  mutate(Q13 = as.numeric(Q13))
+
+mturk <- mturk %>% 
+  mutate(Q14 = as.numeric(Q14))
+```
+
+Participants were recruited from two data sources. `r nrow(sona)`
+undergraduate students taking introduction to psychology were recruited
+for course credit at a large midwestern university. Undergraduate
+participants were *M* = `r apa_num(mean(sona$Q13, na.rm = T))` (*SD* =
+`r apa_num(sd(sona$Q13, na.rm = T))`) years old at the time of the
+study. `r nrow(mturk)` participants were recruited from Amazon's
+Mechanical Turk, and these participants were *M* =
+`r apa_num(mean(mturk$Q14, na.rm = T))` (*SD* =
+`r apa_num(sd(mturk$Q14, na.rm = T))`) years old. No other demographic
+information was collected in the study.
+
+## Material and Procedure
+
+`r nrow(questions)-3` items were developed using previous scale
+development on generativity [@drolet1990], along with theoretical factor
+alignment to XXCITEXX. These items aligned with areas of biological,
+physical, social, spiritual, and personal immortality. The survey was
+implemented in Qualtrics. First, participants entered their age in years
+for basic demographic information. The immortality items were separated
+into three blocks of 20-21 questions. These three blocks of questions
+were randomized across participants, and the items within each block
+were also randomized. In each block, one attention check item was shown
+(e.g., "Answer this question as somewhat agree."). At the end of the
+study, participants were directed back to either SONA for undergraduate
+course credit or Mechanical Turk for monetary
+compensation[\^Unfortunately, the exact amount we paid participants is
+lost to time. Given our ethics application, we believe it was 1-2 USD,
+and the survey was completed in *M* =
+`r apa_num(mean(mturk_good[, "Duration (in seconds)"])/60)` (*SD* =
+`r apa_num(sd(mturk_good[, "Duration (in seconds)"])/60)` minutes.].
+
+## Data analysis
+
+This study was not pre-registered. We conducted data analysis in two
+phases. The data were first screened for inattentive and outlier
+responses. The data were then randomly split into an exploratory and
+confirmatory dataset. We developed the XX scale by using exploratory
+factor analysis (EFA) with maximum likelihood estimation and an oblique
+(i.e., oblimin) rotation [@preacher2003]. Analyses were performed with
+the *psych* package [@revelle2020]. We used scree plots, parallel
+analysis, and theory to determine the number of factors and compared
+models based on fit indices to select the best model. We use the
+following fit indices: Root Mean Squared Error of Approximation [RMSEA;
+@steiger2016], Root Mean Squared Residual [RMSR; @jöreskog1996],
+Comparative Fit Index [CFI; @bentler1990], and the Tucker-Lewis Index
+[TLI; @tucker1973]. Values close to one are expected for goodness of fit
+statistics [CFI, TLI; @bentler1990; @hu1999], while lower values close
+to zero are considered better models for residual statistics [RMSEA,
+RMSR; @steiger2016].
+
+We then analyzed the best model from the exploratory stage using
+confirmatory factor analysis (CFA) and multigroup CFA [@kline2016;
+@brown2015] on the second confirmatory dataset. The models were analyzed
+with *lavaan* [@rosseel2012] and *visualizemi* [@buchanan2024] *R*
+packages. Multigroup CFA can be used to determine if the scale structure
+can be generalized to subsamples within the data, and thus, allowing for
+the same interpretation of total or subscale scores calculated from the
+scale. First, we modeled the overall structure from the EFA results to
+determine fit in a new sample. The RMSEA, CFI, and TLI were used to
+determine model fit along with the Standardized Root Mean Squared
+Residual [SRMR; @bentler1995]. The same interpretations were included
+from the exploratory stage: high fit indices close to one for goodness
+of fit statistics, and low fit indices close to zero for residual fit
+statistics. If the overall model fit well, we then modeled the
+subsamples of student populations and Mechanical Turk populations
+separately. While fit is expected to potentially degrade due to smaller
+sample sizes, we expect these models to converge to demonstrate that it
+is appropriate to combine models for multigroup testing.
+
+For the multigroup CFA, we used @brown2015's suggested terminology and
+steps for analysis. The *configural* model includes both subsamples
+combined together into one model controlling for group structure. This
+model supports the "configuration" or structure of the scale is at least
+similar within each group, but does not force each group to show similar
+patterns of parameter estimates. Each subsequent step constrains a set
+of parameters to be equal across groups to demonstrate invariance (i.e.,
+equivalence). The configural model is then compared to the *metric*
+model, which sets the factor loadings for each measured item to be equal
+across groups. This model supports that each item is related to the
+underlying latent variable the same way for each group. If this
+assumption holds, the metric model is then compared to a *scalar* model,
+which sets the item intercepts (i.e., item means) to be equal across
+groups. Scalar model invariance suggests that each subsample shows the
+same item means and factor loadings across groups. Finally, we compared
+the scalar model to the *strict* model, which constrains item residuals
+(i.e., errors, variance) to be the same across groups. Invariance in
+model residuals suggests that the items have the same answer
+range/spread across groups.
+
+To assess if models are invariant, we used $\Delta$ CFI \<= .01
+criterion to indicate that models were equivalent [@cheung2002]. If
+models were not considered invariant, we investigated for the source of
+the invariance by using partial invariance testing [@byrne1989;
+@cheung1999]. Each parameter estimate is individually relaxed to
+determine if that particular estimate leads to misfit in the model. For
+example, if the model fails scalar invariance, each item mean would be
+allowed to freely vary between groups (one at a time) to find the items
+that show group differences. If only a few items show group differences,
+then the model is considered "partially" invariant, and the impact on
+total scores can be assessed. Partially invariant models indicate areas
+for further investigation into group differences and ways that the final
+scores of the model must be carefully interpreted. Previously, @nye2011
+and @nye2019 proposed an effect size $d_{MACS}$ to help quantify the
+size of the difference between groups in partially invariant models.
+However, $d_{MACS}$ can generally only be used to understand the item
+means and loadings together (due to the mathematical calculation),
+regardless of the tyep of non-invariance. Therefore, we applied a new
+technique proposed by @buchanan2024 to assess several potential effect
+size components of the model: 1) overall model replication likelihood,
+2) individual parameter replication likelihood, and 3) effect size for
+individual parameters showing non-invariance.
+
+We will use the $h_{nmi}$ effect size as the likelihood of replication
+statistic for both the overall model and individual parameters. First,
+the data is bootstrapped with replacement *n* times to create similar
+samples to the original data. The grouping variable is then randomized
+to create a comparison model. The proportion of times that invariance
+(or non-invariance) is met is calculated for the bootstrapped and
+randomized group labels. $h_{nmi}$ is Cohen's $h$ , which is the
+standardized difference between two proportions for non-invariance (no
+measurement invariance, but the statistic can also be calculated as
+$h_{mi}$ for the difference in proportions for when the model showed
+measurement invariance). We suggest $h_{nmi}$ because the interpretation
+is a bit simpler: effect sizes close to zero indicate that the
+bootstrapped data and randomized groups data show the same number of
+non-measurement invariance findings, indicating that they are likely the
+same result. The logic here is that if groups are truly equal in their
+measurement on a scale, then the grouping variable should not affect the
+results, thus, randomizing the grouping variable label does not affect
+the results. As $h_{nmi}$ increases, we expect to find non-measurement
+invariance between groups, as the bootstrapped data is consistently
+different than randomized group labels. $h$ can be interpreted much like
+$d$, but $d$ does not technically have upper or lower limits (i.e., they
+are $\infty$), while $h$'s range is limited to $\pi$. Therefore, we will
+report $h_{nmi_p}$ which is scaled to range from -1 to +1 for easier
+interpretation. In addition to this effect size, we can calculate $d$
+for the differences in parameters for bootstrapped versus random group
+labels, thus, providing an estimate for the size of group differences on
+partially invariant parameter estimates.
+
+# Results
+
 ## Data Screening
+
+### Undergraduate Data
+
+Data were screened for accuracy, missing data, outliers, and multivariate parametric assumptions.
+
+`r nrow(sona)`
+`r nrow(sona_replaced)`
+`r nrow(sona_good)`
+`r nrow(sona_noout)`
 
@@
 
+### Mechanical Turk Data
+
+`r nrow(mturk)`
+`r nrow(mturk_replaced)`
+`r nrow(mturk_good)`
+`r nrow(mturk_noout)`
+
 ```{r screen-mturk-accuracy-out, eval = F}
@@
 ```{r data-combine-split}
-combo <- bind_rows(sona_good, mturk_good)
-combo_noout <- bind_rows(sona_noout, mturk_noout)
+combo <- bind_rows(sona_good %>% 
+                     mutate(where = "Undergraduate"), 
+                   mturk_good %>% 
+                     mutate(where = "Mechanical Turk"))
+combo_noout <- bind_rows(sona_noout %>% 
+                     mutate(where = "Undergraduate"), 
+                     mturk_noout %>% 
+                     mutate(where = "Mechanical Turk"))
 
@@
   filter(!(ResponseId %in% random_split)) %>% 
-  select(Q2_1:Q5_20)  %>% 
+  select(Q2_1:Q5_20, where)  %>% 
   select(-Q2_21, -Q4_20, -Q5_16)
@@
 
-```{r}
+```{r number-factors}
 #efaDF <- read.csv("../03_Data/efaDF.csv")
@@
 
-```{r}
+```{r two-factor}
 item_text <- read.csv("../03_Data/item_text.csv")
@@
 
-```{r}
+```{r three-factor}
 
@@
 
-```{r}
+```{r five-factor}
 EFA_fit <- fa(efaDF, #data
@@
 
-- import the edited files and test those models for fit 
-- theory is 5, so if the fit is similar, then go with five
-
---- 
-test cfa 
-test MGCFA --> use new package to include information 
----
-
-**Model 1: Two-Factor**
-
-These are all the items with loading \> 0.7
-
--   Factor One: Sense of Contribution
-
-    -   Q2_16: I have taken part in activities or events which will
-        impact the future.
-
-    -   Q2_2: I have contributed to the world in a unique way.
-
-    -   Q2_3: I have contributed to causes that will impact the future.
-
-    -   Q5_9: I have contributed to things which will be meaningful.
-
-    -   Q5_13: I will leave a lasting legacy.
-
-    -   Q2_5: I am proud of my accomplishments.
-
-    -   Q2_6: I am confident in the legacy I will leave when I die.
-
-    -   Q4_1: Others would say I have impacted their lives.
-
-<!-- -->
-
--   Factor Two: Spiritual Immortality
-
-    -   Q4_19: I believe in an afterlife.
-
-    -   Q2_17: My spirit or soul will live on after I physically die.
-
-    -   Q2_12: I believe I will live on in the afterlife.
-
-    -   Q5_2: Death is not the end.
-
-    -   Q5_10: I believe in an immaterial soul or spirit.
-
-    -   Q5_1: I am comforted by the thought of an afterlife.
-
-    -   Q2_18: Death will not be the end of me.
-
-**Model 2: Three-Factor**
-
--   Factor One:
-
-    -   Q2_16: I have taken part in activities or events which will
-        impact the future.
-
-    -   Q2_3: I have contributed to causes that will impact the future.
-
-    -   Q2_5: I am proud of my accomplishments.
-
-    -   Q5_9: I have contributed to things which will be meaningful.
-
-    -   Q4_1: Others would say I have impacted their lives.
-
-    -   Q2_4: I feel I have taken part in something bigger than myself.
-
-    -   Q2_2: I have contributed to the world in a unique way.
-
-<!-- -->
-
--   Factor Two:
-
-    -   Q
-
-<!-- -->
-
--   Factor Three:
-
-    -   Q
-
-**Model 3: Five-Factor**
+```{r comparison-models}
+efa_results <- import("results/final_questions.xlsx")
+EFA_2factor <- fa(efaDF %>% 
+                    select(efa_results %>% 
+                           filter(!is.na(factor2)) %>% 
+                           pull(question)),
+                  nfactors = 2,
+                  rotate = "oblimin", #rotation
+                  fm = "ml") #math
+
+EFA_3factor <- fa(efaDF %>% 
+                    select(efa_results %>% 
+                           filter(!is.na(factor3)) %>% 
+                           pull(question)),
+                  nfactors = 3,
+                  rotate = "oblimin", #rotation
+                  fm = "ml") #math
+
+EFA_5factor <- fa(efaDF %>% 
+                    select(efa_results %>% 
+                           filter(!is.na(factor5)) %>% 
+                           pull(question)),
+                  nfactors = 5,
+                  rotate = "oblimin", #rotation
+                  fm = "ml") #math
+
+EFA_2factor
+EFA_3factor
+EFA_5factor
+
+new_5_columns <- as.data.frame(unclass(EFA_5factor$loadings)) %>% 
+  mutate(question = rownames(.)) %>% 
+  rowwise() %>%
+  mutate(keep = sum(c_across(-question) >= .30)) %>% 
+  ungroup() %>% 
+  arrange(desc(keep)) %>% 
+  filter(keep == 1) %>% 
+  pull(question)
+
+EFA_5factor <- fa(efaDF %>% 
+                    select(all_of(new_5_columns)),
+                  nfactors = 5,
+                  rotate = "oblimin", #rotation
+                  fm = "ml") #math
+
+EFA_5factor
+
+new_5_columns <- as.data.frame(unclass(EFA_5factor$loadings)) %>% 
+  mutate(question = rownames(.)) %>% 
+  rowwise() %>%
+  mutate(keep = sum(c_across(-question) >= .30)) %>% 
+  ungroup() %>% 
+  arrange(desc(keep)) %>% 
+  filter(keep == 1) %>% 
+  pull(question)
+
+EFA_5factor <- fa(efaDF %>% 
+                    select(all_of(new_5_columns)),
+                  nfactors = 5,
+                  rotate = "oblimin", #rotation
+                  fm = "ml") #math
+
+EFA_5factor
+
+# as.data.frame(unclass(EFA_5factor$loadings)) %>% 
+#   mutate(question = rownames(.)) %>% 
+#   rowwise() %>%
+#   mutate(keep = sum(c_across(-question) >= .30)) %>% 
+#   ungroup() %>% 
+#   left_join(questions,
+#             by = c("question" = "Question_Number")) %>% 
+#   arrange(desc(ML1)) %>% 
+#   export(., "results/5_factor_reduced.xlsx", row.names = F)
+```
+
+```{r}
+# test if q2_1 changing to a different place changes results 
+five_reduced <- import('results/5_factor_reduced.xlsx')
+five.model <- ""
+
+for (factor in unique(five_reduced$Factor)){
+  questions <- five_reduced %>% 
+    filter(Factor == factor) %>% 
+    pull(question)
+
+  five.model <- 
+    paste0(five.model, "\n",
+        factor, " =~ ", 
+        paste(questions, collapse = " + "))
+}
+
+#cat(five.model)
+
+model.results <- mgcfa(
+  model = five.model,
+  data = cfaDF,
+  group = "where", 
+  group.equal = c("loadings", "intercepts", "residuals"),
+  meanstructure = TRUE
+)
+
+summary(model.results$model_overall, 
+        standardized = T,
+        fit.measures = T, 
+        rsquare = T)
+
+summary(model.results$group_models$model.Undergraduate, 
+        standardized = T,
+        fit.measures = T, 
+        rsquare = T)
+
+modificationindices(model.results$group_models$model.Undergraduate,
+                    sort. = T)
+
+summary(model.results$group_models$`model.Mechanical Turk`, 
+        standardized = T,
+        fit.measures = T, 
+        rsquare = T)
+
+modificationindices(model.results$group_models$`model.Mechanical Turk`, 
+                    sort. = T)
+
+summary(model.results$model_configural, 
+        standardized = T,
+        fit.measures = T, 
+        rsquare = T)
+
+model.results$model_fit
+
+model.partial <- partial_mi(
+  saved_model = model.results$invariance_models$model.intercepts,
+  data = cfaDF,
+  model = five.model,
+  group = "where",
+  group.equal = c("loadings", "intercepts"),
+  partial_step = "intercepts")
+
+model.partial$fit_table
+```
+
+```{r}
+# distribution of each latent variable as a plot
+
+saved_mi_plots <- plot_mi(data_coef = model.results.partial$model_coef,
+                          # which model do you want to plot from model column
+                          model_step = "intercepts", 
+                          # name of observed item
+                          item_name = "Q4_8", 
+                          # LV limits to graph
+                          x_limits = c(-2,2), 
+                          # Y min and max in data
+                          y_limits = c(min(cfaDF$Q4_8),
+                                       max(cfaDF$Q4_8)), 
+                          # what ci do you want
+                          conf.level = .95, 
+                          # what model results do you want
+                          model_results = model.results.partial$invariance_models$model.intercepts, 
+                          # which latent is the observed variable on
+                          # important for cross-loaded variables
+                          lv_name = "biological", 
+                          # if you have more than two groups, which two do you want
+                          plot_groups = NULL)
+
+saved_mi_plots$complete
+
+saved_mi_plots <- plot_mi(data_coef = model.results.partial$model_coef,
+                          # which model do you want to plot from model column
+                          model_step = "intercepts", 
+                          # name of observed item
+                          item_name = "Q2_4", 
+                          # LV limits to graph
+                          x_limits = c(-1,1), 
+                          # Y min and max in data
+                          y_limits = c(min(cfaDF$Q2_4),
+                                       max(cfaDF$Q2_4)), 
+                          # what ci do you want
+                          conf.level = .95, 
+                          # what model results do you want
+                          model_results = model.results.partial$invariance_models$model.intercepts, 
+                          # which latent is the observed variable on
+                          # important for cross-loaded variables
+                          lv_name = "social", 
+                          # if you have more than two groups, which two do you want
+                          plot_groups = NULL)
+
+model.results.partial <- mgcfa(
+  model = five.model,
+  data = cfaDF,
+  group = "where", 
+  group.equal = c("loadings", "intercepts", "residuals"),
+  meanstructure = TRUE,
+  group.partial = "Q4_8 ~1"
+)
+
+# figure out how to update this 
+# so that it will take the group.partial correctly 
+model.partial.partial <- partial_mi(
+  saved_model = model.results.partial$invariance_models$model.residuals,
+  data = cfaDF,
+  model = five.model,
+  group = "where",
+  group.equal = c("loadings", "intercepts", "residuals"),
+  partial_step = "residuals")
+
+model.partial.partial$fit_table
+```
+
+```{r boot-model, eval = F}
+saved_boot_model <- bootstrap_model(
+  # saved configural model to start at
+  saved_configural = model.results$model_configural,
+  # dataset for the analysis
+  data = cfaDF,
+  # model lavaan syntax
+  model = five.model,
+  # group variable in the dataset
+  group = "where", 
+  # number of bootstraps
+  # this is set to a low number to compile quickly for cran
+  nboot = 1000,
+  # name of the fit measure you want to use, make sure it's lavaan
+  invariance_index = "cfi",
+  # rule for the difference in fit indices
+  invariance_rule = .01,
+  # what order of steps do you want to test? 
+  group.equal = c("loadings", "intercepts", "residuals")
+)
+
+saveRDS(saved_boot_model, "../03_Data/saved_boot_model.rds")
+```
+
+```{r boot-partial, eval = F}
+saved_boot_partial <- bootstrap_partial(
+  # the model you want to test 
+  # use the model before your invariant one 
+  # similar set up to partial_mi
+  saved_model = model.results$invariance_models$model.loadings,
+  # the dataframe
+  data = cfaDF,
+  # the original model syntax
+  model = five.model,
+  # the grouping variable column
+  group = "where",
+  # run more, but this package vignette needs to knit fast
+  nboot = 1000,
+  # what index are you using for invariance?
+  # match this to lavaan's name under fitmeasures()
+  invariance_index = "cfi",
+  # what rule are you using?
+  invariance_rule = .01,
+  # what are we comparing against? 
+  invariance_compare = unname(fitmeasures(model.results$invariance_models$model.loadings, "cfi")),
+  # which step you want to estimate effect size for
+  partial_step = c("intercepts"), 
+  # which parameters you want to hold constrained
+  group.equal = c("loadings", "intercepts")
+  )
+saveRDS(saved_boot_partial, "../03_Data/saved_boot_partial.rds")
+```
 
